---
title: "assignment01"
author: "Jeff Nguyen 6524885309"
date: "20/08/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**
</font>
Assignment 01  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  
&nbsp;

# **Question 1**
## a. Solve $x^2 +2x -8 =0$

Solving polynomial equations in R using polyroot. The quadratic equation is expected to have 2 roots in the form of $x= \frac{-b \pm \sqrt{b^2-4ac}}{2a}$

```{r}
polyroot(c(-8, 2, 1))
```
&nbsp;  

## b. Solve $x^2 -9 =0$

Solving polynomial equations in R using polyroot. The quadratic equation is expected to have 2 roots in the form of $x= \frac{-b \pm \sqrt{b^2-4ac}}{2a}$

```{r}
polyroot(c(-9, 0, 1))
```
&nbsp;

## c. Solve $x^3 -x^2 +4x -4 =0$

Solving polynomial equations in R using polyroot. The cubic equation is expected to have three roots.

```{r}
polyroot(c(-4, 4, -1, 1))
```
&nbsp;

## d. Solve $x^5 +3x^2 -8 =0$

Solving polynomial equations in R using polyroot. The equation is expected to have 5 roots.

```{r}
polyroot(c(-8, 0, 3, 0, 0, 1))
```
&nbsp;

# **Question 2**

For discrete compounding (presented in a,b,c,d), we use the formula $S = A(1+\frac{r}{n})^{nt}$ ,substitute $A=100$, $r= 6\%$, $t=5$ and use the correct value for n based on the number compounding period per year. Then we use the below custom function in R to solve it.

```{r definition-fv}
# Discrete Compounding Function
# Compounding a=100 at an interest rate r=6% incurring with frequency n a year, for 5 years.
fv_discrete <- function(n) {
  100*(1+0.06/n)^(n*5)
}
```

###### a. Compound annually
```{r}
# compounded annually, so n=1
fv_discrete(1)
```

###### b. Compound quarterly
```{r}
# compounded quarterly, so n=4
fv_discrete(4)
```

###### c. Compound monthly
```{r}
# compounded monthly, so n=12
fv_discrete(12)
```

###### d. Compound daily
```{r}
# compounded daily, so n=365
fv_discrete(365)
```


For continuous compounding, we use the formula $S = Ae^{rt}$ ,substitute $A=100$, $r= 6\%$, $t=5$. Thus:

```{r}
fv_continuous <- 100*exp(0.06*5)
fv_continuous
```
&nbsp;

# **Question 3**
Using the two formulas:&nbsp;
Present value of cash flow (future returns): $PV_{CF} = \frac{R_1}{(1+r)^1} + \frac{R_2}{(1+r)^2} + \frac{R_3}{(1+r)^3} + ... + \frac{R_n}{(1+r)^n}$

Present value of the investment $PV_{investment} = PV_{CF} + \frac{MV}{(1+r)^n}$  
with $R_1$, $R_2$, $R_3$, ..., and $R_n$ be the return each year and $MV$ the market value at the end of the final year.  
Establishing the r functions
```{r definition-pv}
# Present value of cash flow (future returns)
pv_cf <- function(R,r) {
  sum(R/((1+r)^(1:length(R))))
}

pv_investment <- function(R,r,MV) {
  pv_cf(R,r) + MV/((1+r)^length(R))
}
```

Substituting the given value of future returns:  
$R_1 = 22000$, $R_2 = 28500$, $R_3 = 32000$, $R_4 = 18000$, $R_5 = 12000$ and the final year market value $MV = 52000$, we have:

Present value of future returns:
```{r}
R <- c(22000, 28500, 32000, 18000, 12000) # Future returns
r <- 0.06 # interest rate

pv_cf(R,r) # PV of future returns
```

Present value of investment:
```{r}
R <- c(22000, 28500, 32000, 18000, 12000) # Future returns
r <- 0.06 # interest rate
MV <- 52000 # market value of investment in the final year

pv_investment(R,r,MV) #PV of investment
```
&nbsp;

# **Question 4**
Calculate NPV using this function $NPV = PV_{Investment} - Initial\:Investment$

Using the method and parameters in **Question 3** to calculate $PV_{Investment}$ and the initial investment valued at $120,000, we have:

```{r}
R <- c(22000, 28500, 32000, 18000, 12000) # Future returns
r <- 0.06 # interest rate
MV <- 52000 # market value of investment in the final year
init_investment <- 120000 # initial investment

npv <- pv_investment(R,r,MV) - init_investment #NPV
npv
```
&nbsp;

# **Question 5**
Calculate PV of the perpetuity using the formula  $PV_{CF} = \frac{R_1}{(1+r)^1} + \frac{R_2}{(1+r)^2} + \frac{R_3}{(1+r)^3} + ... + \frac{R_n}{(1+r)^n} = \frac{R}{r}$ with $R_1 = R_2 = R_3 = ... = R_n$ and $n = \infty$

Subtituing the parameters $R=1$ and $r=5\%$, we have
```{r}
perpetuity <- function(R,r) {
  R/r
}

R <- 1
r <- .05

perpetuity(1,.05)
```
&nbsp;

# **Question 6**
## a. Find IRR of question 4

IRR is the break-even root of the equation $I_0 = \frac{R_1}{(1+r)^1} + \frac{R_2}{(1+r)^2} + \frac{R_3}{(1+r)^3} + ... + \frac{R_n}{(1+r)^n}$  
Thus the problem turns into finding the non-complex root of the polynomial equation in the form of $I_0 - \frac{R_1}{(1+r)^1} - \frac{R_2}{(1+r)^2} - \frac{R_3}{(1+r)^3} - ... - \frac{R_n}{(1+r)^n} = 0$  
Note that the root will be in the form $\frac{1}{1+r}$

Using the parameters in **Question 4**
```{r}
R <- c(22000, 28500, 32000, 18000, 12000 + 52000) # Future returns, adding the scrap value to the final year

init_investment <- 120000 # initial investment
R_combine <- c(init_investment, R*(-1)) # rearrange the polynomial equation
r <- polyroot(R_combine) # find roots of the polynomial equation, the return will be 1+r

(1/(Re(r)[abs(Im(r)) < 1e-6])) - 1 # find only the non-complex root of said equation and subtract 1
```  
## b. Find the rate of return on a $24,000 investment with an annual return of $4,500 for five years and a scrap value of $2,500 at the end of the fifth year.

In this case $I_0 = 24000$, $R_1 = R_2 = R_3 = R_4 = R_5 = 4500$, and $MV = 2500$
Using similar method in a. with the new parameters
```{r}
R <- c(4500, 4500, 4500, 4500, 4500 + 2500) # Future returns, adding the scrap value to the final year

init_investment <- 24000 # initial investment
R_combine <- c(init_investment, R*(-1)) # rearrange the polynomial equation
r <- polyroot(R_combine) # find roots of the polynomial equation, the return will be 1+r

(1/(Re(r)[abs(Im(r)) < 1e-6])) - 1 # find only the non-complex root of said equation and subtract 1

```
