---
title: "assignment03"
author: "Jeff Nguyen"
date: "03/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 03  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**

For continuous functions defined by $y= f(x)$, the point $(x_0,f(x_0))$ is a maxima or minima if $x_0$ is in the domain of the function and $f'(x) = 0$. Thus, for the below, we find and test extrema values $x_0$ for which $f'(x_0) = 0$.


## a. $y = x^2 - 6x + 5$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    2x - 6 & = 0 \\
    x & = 3
  \end{aligned}
\end{equation}

**Thus we have the extrema $x_0 = 3$**  

**Graph of the function:**
```{r}
curve(x^2 - 6*x + 5, -100,100)
```

Testing for min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0-1) & = f'(2)  \qquad &    f'(x_0+1) & = f'(4) \\
    f'(x_0-1) & = 2(2) - 6     &    f'(x_0+1) & = 2(4) - 6 \\
    f'(x_0-1) & = -2 < 0       &    f'(x_0+1) & = 2 > 0
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation}
  \begin{aligned}
    f(3) & = 3^2 - 6(3) + 5 \\
    f(3) & = -4
  \end{aligned}
\end{equation}

**We see that the function is decreasing on $(-\infty,3)$, and increasing on $(3,\infty)$
Thus, the absolute minima of the function is at $(3,-4)$**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    2 & = 0 \text{ (not possible)}
  \end{aligned}
\end{equation}

**Thus the inflection point does not exist for this function.**
  




## b. $y = -x^2 + 6x - 5$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    -2x + 6 & = 0
    x & = 3
  \end{aligned}
\end{equation}

**Thus we have the extrema $x_0 = 3$** 

**Graph of the function:**
```{r}
curve(-x^2 + 6*x - 5, -100,100)
```

Testing for min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0 - 1) & = f'(2)  \qquad &    f'(x_0 + 1) & = f'(4) \\
    f'(x_0 - 1) & = -2(2) + 6    &    f'(x_0 + 1) & = -2(4) + 6 \\
    f'(x_0 - 1) & = 4 > 0        &    f'(x_0 + 1) & = -2 < 0
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation}
  \begin{aligned}
    f(3) & = -3^2 + 6(3) - 5 \\
    f(3) & = 4
  \end{aligned}
\end{equation}

**We see that the function is increasing on $(-\infty,3)$, and decreasing on $(3,\infty)$
Thus, the absolute maxima of the function is at $(3,4)$**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    -2 & = 0 \text{ (not possible)}
  \end{aligned}
\end{equation}

**Thus the inflection point does not exist for this function.**
  






## c. $y = 2x^3 - 15x^2 + 36x + 10$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    6x^2 - 30x + 36 & = 0 \\
    x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
    x & = \frac{-(-30) \pm \sqrt{(-30)^2 - 4(6)(36)}}{2(6)} \\
    x & = \frac{30 \pm \sqrt{36}}{12} \\
    x & = 
      \left\{
        \begin{array} {11}
          3 \\
          2
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Thus we have the potential extremas $x_0 = 3$ and $x_0 = 2$  

**Graph of the function:**
```{r}
curve(2*x^3 - 15*x^2 + 36*x + 10, -100,100)
```

Testing min, max with $x_0 = 3$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(\frac{11}{4})                    \qquad  &   f'(x_0 + 1) & = f'(4) \\
    f'(x_0 - \frac{1}{4}) & = 6(\frac{11}{4})^2 - 30(\frac{11}{4}) + 36   &   f'(x_0 + 1) & = 6(4)^2 - 30(4) + 36 \\
    f'(x_0 - \frac{1}{4}) & = -\frac{9}{8} < 0                            &   f'(x_0 + 1) & = 12 > 0 \\
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation} 
  \begin{aligned}
    f(3) & = 2(3)^3 - 15(3)^2 + 36(3) + 10 \\
    f(3) & = 37
  \end{aligned}
\end{equation}


**From the above, we gather the function is decreasing just before $(3,37)$ and increasing right after $(3,37)$
Thus, the function has a local minima at $(3,37)$**

Testing min, max with $x_0 = 2$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(\frac{7}{4})                    \qquad  &   f'(x_0 + \frac{1}{4}) & = f'(\frac{9}{4}) \\
    f'(x_0 - \frac{1}{4}) & = 6(\frac{7}{4})^2 - 30(\frac{7}{4}) + 36    &   f'(x_0 + \frac{1}{4}) & = 6(\frac{9}{4})^2 - 30(\frac{9}{4}) + 36 \\
    f'(x_0 - \frac{1}{4}) & = \frac{15}{8} > 0                          &   f'(x_0 + \frac{1}{4}) & = -\frac{9}{8} < 0 \\
  \end{aligned}
\end{equation}

Finding $f(2)$:
\begin{equation} 
  \begin{aligned}
    f(2) & = 2(2)^3 - 15(2)^2 + 36(2) + 10 \\
    f(2) & = 38
  \end{aligned}
\end{equation}

**From the above, we gather the function is increasing just before $(2,38)$ and decreasing right after $(2,38)$**
**Thus, the function has a local minima at $(3,37)$**

**The function does not have absolute minima nor maxima.**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    12x - 30 & = 0 \\
    x & = \frac{5}{2}
  \end{aligned}
\end{equation}

Testing the potential inflection point $(\frac{5}{2},f(\frac{5}{2}))$ :
\begin{equation} 
  \begin{aligned}
    f''(x_0 - \frac{1}{2}) & = f''(2)   \qquad  &   f''(x_0 + \frac{1}{2}) & = f''(3) \\
    f''(x_0 - \frac{1}{2}) & = 12(2) - 30       &   f''(x_0 + \frac{1}{2}) & = 12(3) - 30 \\
    f''(x_0 - \frac{1}{2}) & = -6 < 0           &   f''(x_0 + \frac{1}{2}) & = 6 > 0 \\
  \end{aligned}
\end{equation}

Finding $f(\frac{5}{2})$:
\begin{equation} 
  \begin{aligned}
    f(\frac{5}{2}) & = 2(\frac{5}{2})^3 - 15(\frac{5}{2})^2 + 36(\frac{5}{2}) + 10 \\
    f(\frac{5}{2}) & = \frac{75}{2}
  \end{aligned}
\end{equation}

**Thus $(3, \frac{75}{2})$ is an inflection point and is where the function curvature changes from concave to convex.**
  



## d. $y = x^3 -3x^2 +3x$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    3x^2 -6x + 3 & = 0 \\
    x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
    x & = \frac{-(-6) \pm \sqrt{(-6)^2 - 4(3)(3)}}{2(3)} \\
    x & = \frac{6 \pm \sqrt{0}}{6} \\
    x & = 1
       
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = 1$
  
Graph of the function:
```{r}
curve(x^3 -3*x^2 +3*x, -100,100)
```


Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(0)       \qquad  &   f'(x_0 + 1) & = f'(2) \\
    f'(x_0 - 1) & = 3(0)^2 - 6(0) + 3   &   f'(x_0 + 1) & = 3(2)^2 - 6(2) + 3 \\
    f'(x_0 - 1) & = 3 > 0               &   f'(x_0 + 1) & = 3 > 0
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = 1^3 - 3(1)^2 + 3(1) \\
    f(1) & = 1
  \end{aligned}
\end{equation}

**From the above, we know the function increasing past $(1,1)$ and there is no local or absolute minima or maxima.**
  

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    6x - 6 & = 0 \\
    x & = 1
  \end{aligned}
\end{equation}

Testing the potential inflection point at $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(0)   \qquad  &   f''(x_0 + 1) & = f''(2) \\
    f''(x_0 - 1) & = 6(0) - 6         &   f''(x_0 + 1) & = 6(2) - 6 \\
    f''(x_0 - 1) & = -6 < 0           &   f''(x_0 + 1) & = 6 > 0
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(1,1)$, thus $(1,1)$ is an inflection point.**
  
## e. $y = (x-1)^3$

This is a polynomial function, thus, it is continuous everywhere.
Expanding:

\begin{equation}
  \begin{aligned}
    f(x) & = (x-1) ^3 \\
         & = (x-1)(x^2 - 2x + 1) \\
         & = x^3 - 2x^2 + x - x^2 + 2x - 1 \\
         & = x^3 - 3x^2 + 3x - 1 \\
  \end{aligned}
\end{equation}

Finding min, max:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    3x^2 - 6x + 3 & = 0 \\
    x^2 - 2x + 1 & = 0 \\
    (x-1)^2 & = 0 \\
    x & = 1
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = 1$
  
Graph of the function:
```{r}
curve(x^3 - 3*x^2 + 3*x - 1, -100,100)
```


Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(0)   \qquad  &   f'(x_0 + 1) & = f'(2) \\
    f'(x_0 - 1) & = (0-1)^2         &   f'(x_0 + 1) & = (2-1)^2 \\
    f'(x_0 - 1) & = 1 > 0           &   f'(x_0 + 1) & = 1 > 0
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (1-1)^3 \\
    f(1) & = 0
  \end{aligned}
\end{equation}

**From the above, we know the function increasing past $(1,0)$ and there is no local or absolute minima or maxima.**
  

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    2x - 2 & = 0 \\
    x & = 1
  \end{aligned}
\end{equation}

Testing the potential inflection point at $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(0)   \qquad  &   f''(x_0 + 1) & = f''(2) \\
    f''(x_0 - 1) & = 2(0) - 2         &   f''(x_0 + 1) & = 2(2) - 2 \\
    f''(x_0 - 1) & = -2 < 0            &   f''(x_0 + 1) & = 2 > 0
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(1,0)$, thus $(1,0)$ is an inflection point.**
  





## f. $y = (x^2 - 1)^2$

This is a polynomial function, thus, it is continuous everywhere.
Expanding:

\begin{equation}
  \begin{aligned}
    f(x) & = (x^2 - 1)^2 \\
         & = x^4 - 2x^2 + 1
  \end{aligned}
\end{equation}

Finding min, max:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    4x^3 - 4x & = 0 \\
    4x(x^2 - 1) & = 0 \\
    4x(x - 1)(x + 1) & = 0 \\
    x & =
      \left\{
        \begin{array} {11}
          0 \\
          1 \\
          -1
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = -1$, $x_0 = 0$ and $x_0 = 1$
  
Graph of the function:
```{r}
curve(x^4 - 2*x^2 + 1, -2,2)
```


Testing min, max with $x_0 = -1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(-2)   \qquad  &   f'(x_0 + \frac{1}{4}) & = f'(-3/4) \\
    f'(x_0 - 1) & = 4(-2)^3 - 4(-2)  &   f'(x_0 + \frac{1}{4}) & = 4(-3/4)^3 - 4(-3/4) \\
    f'(x_0 - 1) & = -24 < 0          &   f'(x_0 + \frac{1}{4}) & = 21/16 > 0
  \end{aligned}
\end{equation}

Finding $f(-1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (-1)^4 - 2(-1)^2 + 1 \\
    f(1) & = 0
  \end{aligned}
\end{equation}

**From the above, we know the function has a local min at $(-1,0)$.**
  
  
Testing min, max with $x_0 = 0$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(-\frac{1}{4})               \qquad  &   f'(x_0 + \frac{1}{4}) & = f'(1/4) \\
    f'(x_0 - \frac{1}{4}) & = 4(-\frac{1}{4})^3 - 4(-\frac{1}{4})   &   f'(x_0 + \frac{1}{4}) & = 4(1/4)^3 - 4(1/4) \\
    f'(x_0 - \frac{1}{4}) & = \frac{15}{16} > 0                     &   f'(x_0 + \frac{1}{4}) & = -15/16 < 0
  \end{aligned}
\end{equation}

Finding $f(0)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (0)^4 - 2(0)^2 + 1 \\
    f(1) & = 1
  \end{aligned}
\end{equation}

**From the above, we know the function has a local max at $(0,1)$.**
  
Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(frac{3}{4})               \qquad  &   f'(x_0 + 1) & = f'(2) \\
    f'(x_0 - \frac{1}{4}) & = 4(\frac{3}{4})^3 - 4(\frac{3}{4})    &   f'(x_0 + 1) & = 4(2)^3 - 4(2) \\
    f'(x_0 - \frac{1}{4}) & = -\frac{21}{16} < 0                   &   f'(x_0 + 1) & = 24 > 0
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (1)^4 - 2(1)^2 + 1 \\
    f(1) & = 0
  \end{aligned}
\end{equation}

**From the above, we know the function has a local min at $(1,0)$.**
**To recap, the function has local minimas at $(-1,0)$, $(1,0)$ and local maxima at $(0,1)$. It has no absolute minima or maxima.**
  
Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    12x^2 - 4 & = 0 \\
    3x^2 - 1 & = 0 \\
    x^2 & = \frac{1}{3} \\
    x & = 
      \left\{
        \begin{array} {11}
          \frac{1}{\sqrt{3}} \\
          -\frac{1}{\sqrt{3}}
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Testing the potential inflection point at $x_0 = -\frac{1}{\sqrt{3}}$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - \frac{2}{\sqrt{3}}) & = f''(-\sqrt{3})   \qquad  &   f''(x_0 + \frac{1}{\sqrt{3}}) & = f''(0) \\
    f''(x_0 - \frac{2}{\sqrt{3}}) & = 12(-\sqrt{3})^2 - 4      &   f''(x_0 + \frac{1}{\sqrt{3}}) & = 12(0)^2 - 4 \\
    f''(x_0 - \frac{2}{\sqrt{3}}) & = 32 > 0                  &   f''(x_0 + \frac{1}{\sqrt{3}}) & = -4 < 0
  \end{aligned}
\end{equation}

Finding $f(-\frac{1}{\sqrt{3})$:
\begin{equation} 
  \begin{aligned}
    f(-\frac{1}{\sqrt{3}}) & = (-\frac{1}{\sqrt{3}})^4 - 2(-\frac{1}{\sqrt{3}})^2 + 1 \\
    f(-\frac{1}{\sqrt{3}}) & = \frac{2}{9}
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from convex to concave at $(-\frac{1}{\sqrt{3}},\frac{2}{9})$, thus $(-\frac{1}{\sqrt{3}},\frac{2}{9})$ is an inflection point.**

Testing the potential inflection point at $x_0 = \frac{1}{\sqrt{3}}$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - \frac{1}{\sqrt{3}}) & = f''(0)   \qquad  &   f''(x_0 + \frac{2}{\sqrt{3}}) & = f''(\sqrt{3}) \\
    f''(x_0 - \frac{1}{\sqrt{3}}) & = 12(0)^2 - 4      &   f''(x_0 + \frac{2}{\sqrt{3}}) & = 12(\sqrt{3})^2 - 4 \\
    f''(x_0 - \frac{1}{\sqrt{3}}) & = -4 < 0           &   f''(x_0 + \frac{2}{\sqrt{3}}) & = 32 > 0
  \end{aligned}
\end{equation}

Finding $f(\frac{1}{\sqrt{3})$:
\begin{equation} 
  \begin{aligned}
    f(\frac{1}{\sqrt{3}}) & = (\frac{1}{\sqrt{3}})^4 - 2(\frac{1}{\sqrt{3}})^2 + 1 \\
    f(\frac{1}{\sqrt{3}}) & = \frac{4}{9}
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(\frac{1}{\sqrt{3}},\frac{4}{9})$, thus $(\frac{1}{\sqrt{3}},\frac{4}{9})$ is also an inflection point.**
  
## g. $y = \ln{\frac{x+1}{x^2+3}}$

We know that $\ln(X)$ is continuous on $(0,\infty)$.

Thus the domain of y is:
\begin{equation} 
  \begin{aligned}
    \left\{
        \begin{array} {11}
          x^2 + 3 > 0 \forall x \in \R \\
          x + 1 > 0 \Leftrightarrow \forall x \in (-1,\infty)
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Finding min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    \frac{d(\ln{\frac{x+1}{x^2+3}})}{dx} & = 0 \\
    \frac{\frac{1}{\frac{x+1}{x^2+3}}.d\frac{x+1}{x^2+3}}{dx} & = 0 \\
    \frac{x^2+3}{x+1}.\Big[(x+1).d(\frac{1}{x^2+3}) + d(x+1).\frac{1}{x^2+3} \Big] & = 0 \\
    \frac{x^2+3}{x+1}.\Big[\frac{-(x+1).d(x^2+3)}{(x^2+3)^2} + \frac{1}{x^2+3} \Big] & = 0 \\
    \frac{x^2+3}{x+1}.\frac{-2x(x+1) + x^2 + 3}{(x^2 + 3)^2} & = 0 \\
    \frac{-2x^2 - 2x + x^2 + 3}{(x^2+3)(x+1)} & = 0 \\
    \frac{-x^2 - 2x + 3}{(x^2+3)(x+1)} & = 0 \\
    -x^2 - 2x + 3 & = 0 \\
    x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
    x & = \frac{-(-2) \pm \sqrt{(-2)^2 - 4(-1)(3)}}{2(-1)} \\
    x & = \frac{2 \pm \sqrt{16}}{-2} \\
    x & = 
      \left\{
        \begin{array} {11}
          1 \\
          -3 \text{  ,not valid as x > -1}
        \end{array}
      \right. 
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = 1$

Graph of the function:
```{r}
curve(log((x+1)/(x^2+3)), 0.0000001,10)
```
Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{2}) & = f'(\frac{1}{2})                       \qquad  &   f'(x_0 + \frac{1}{2}) & = f'(\frac{3}{2}) \\ 
    f'(x_0 - \frac{1}{2}) & = \frac{-(\frac{1}{2})^2 - 2(\frac{1}{2}) + 3}
      {((\frac{1}{2})^2+3)(\frac{1}{2}+1)}                                  &   f'(x_0 + \frac{1}{2}) & = \frac{-(\frac{3}{2})^2 - 2(\frac{3}{2})+                                                                                       3}{((\frac{3}{2})^2+3)(\frac{3}{2}+1)} \\
    f'(x_0 - \frac{1}{2}) & = \frac{14}{39} > 0                             &   f'(x_0 + \frac{1}{2}) & = -\frac{6}{35} < 0 
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = \ln{\frac{1+1}{1+3}} \\
    f(1) & = \ln{\frac{2}{4}} \\
    f(1) & = \ln{\frac{1}{2}} \\
    f(1) & = -\ln{2}
  \end{aligned}
\end{equation}

**From the above, we know the function has an absolute max at $(1,-\ln{2})$.**

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    \frac{d\Big[\frac{-x^2 - 2x + 3}{(x^2 + 3)(x + 1)}\Big]}{dx^2} & = 0 \\
    \frac{d\Big[\frac{-x^2 - 2x + 3}{x^3 + x^2 + 3x + 3}\Big]}{dx^2} & = 0 \\
    \frac{\Big[(-x^2 - 2x + 3).d(\frac{1}{x^3 + x^2 + 3x + 3}) + d(-x^2 - 2x + 3).(\frac{1}{x^3 + x^2 + 3x + 3}) \Big]}{dx^2} & = 0 \\
    \frac{(x^2 + 2x - 3)(3x^2 + 2x + 3)}{(x^3 + x^2 + 3x + 3)^2} - \frac{2x+2}{x^3+x^2+3x+3} & = 0 \\
    \frac{3x^4 + 6x^3 - 9x^2 + 2x^3 + 4x^2 - 6x + 3x^2 + 6x -9 - (2x + 2)(x^3 + x^2 + 3x + 3)}{(x^3 + x^2 + 3x +3)^2} & = 0 \\
    \frac{3x^4 + 8x^3 - 2x^2 - 9 - (2x^4 + 2x^3 + 2x^3 + 2x^2 + 6x^2 + 6x + 6x + 6)}{(x^3 + x^2 + 3x +3)^2} & = 0 \\
    \frac{3x^4 + 8x^3 - 2x^2 - 9 - (2x^4 + 4x^3 + 8x^2 + 12x + 6)}{(x^3 + x^2 + 3x +3)^2} & = 0 \\
    \frac{x^4 + 4x^3 - 10x^2 - 12x - 15}{(x^3 + x^2 + 3x +3)^2} & = 0
  \end{aligned}
\end{equation}

I don't think it's in the scope of this assignment to find analytical roots of a 4th order polynomial equation by hand so here are approximate real roots from R:
```{r}
root <- polyroot(c(-15, -12, -10, 4, 1))
# The equation has 2 non-complex roots:
Re(root)[abs(Im(root)) < 1e-6]
```

Since $(-1,\infty)$ is the domain. The only root is approximately 2.574355.

Testing the potential inflection point at $x_0 = 2.574355$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(1.574355)                    \qquad  &   f''(x_0 + 1) & = f''(3.574355) \\
    f''(x_0 - 1) & =  \frac{(1.574355)^4 + 4(1.574355)^3 - 
      10(1.574355)^2- 12(1.574355) - 15}
      {((1.574355)^3 + (1.574355)^2 + 3(1.574355) + 3)^2}     &   f''(x_0 + 1) & = \frac{(3.574355)^4 + 4(3.574355)^3 - 10(3.574355)^2-                                                                                  12(3.574355) - 15}{((3.574355)^3 + (3.574355)^2 + 3(3.574355) + 3)^2)} \\
    f''(x_0 - 1) & \approx -.185634 < 0                             &   f''(x_0 + 1) & \approx  0.03076888 > 0
  \end{aligned}
\end{equation}

Finding $f(2.574355)$:
\begin{equation} 
  \begin{aligned}
    f(2.574355) & = \ln{\frac{2.574355+1}{(2.574355)^2+3}} \\
    f(2.574355) & \approx -0.9908185 
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(2.574355,-0.9908185)$, thus $(2.574355,-0.9908185)$ is an inflection point.**
  

# **Question 2**