---
title: "assignment03"
author: "Jeff Nguyen"
date: "03/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 03  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**

For continuous functions defined by $y= f(x)$, the point $(x_0,f(x_0))$ is a maxima or minima if $x_0$ is in the domain of the function and $f'(x) = 0$. Thus, for the below, we find and test extrema values $x_0$ for which $f'(x_0) = 0$.


## a. $y = x^2 - 6x + 5$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    2x - 6 & = 0 \\
    x & = 3
  \end{aligned}
\end{equation}

**Thus we have the extrema $x_0 = 3$**  

**Graph of the function:**
```{r}
curve(x^2 - 6*x + 5, -100,100)
```

Testing for min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0-1) & = f'(2)  \qquad &    f'(x_0+1) & = f'(4) \\
    f'(x_0-1) & = 2(2) - 6     &    f'(x_0+1) & = 2(4) - 6 \\
    f'(x_0-1) & = -2 < 0       &    f'(x_0+1) & = 2 > 0
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation}
  \begin{aligned}
    f(3) & = 3^2 - 6(3) + 5 \\
    f(3) & = -4
  \end{aligned}
\end{equation}

**We see that the function is decreasing on $(-\infty,3)$, and increasing on $(3,\infty)$
Thus, the absolute minima of the function is at $(3,-4)$**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    2 & = 0 \text{ (not possible)}
  \end{aligned}
\end{equation}

**Thus the inflection point does not exist for this function.**
  




## b. $y = -x^2 + 6x - 5$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    -2x + 6 & = 0
    x & = 3
  \end{aligned}
\end{equation}

**Thus we have the extrema $x_0 = 3$** 

**Graph of the function:**
```{r}
curve(-x^2 + 6*x - 5, -100,100)
```

Testing for min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0 - 1) & = f'(2)  \qquad &    f'(x_0 + 1) & = f'(4) \\
    f'(x_0 - 1) & = -2(2) + 6    &    f'(x_0 + 1) & = -2(4) + 6 \\
    f'(x_0 - 1) & = 4 > 0        &    f'(x_0 + 1) & = -2 < 0
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation}
  \begin{aligned}
    f(3) & = -3^2 + 6(3) - 5 \\
    f(3) & = 4
  \end{aligned}
\end{equation}

**We see that the function is increasing on $(-\infty,3)$, and decreasing on $(3,\infty)$
Thus, the absolute maxima of the function is at $(3,4)$**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    -2 & = 0 \text{ (not possible)}
  \end{aligned}
\end{equation}

**Thus the inflection point does not exist for this function.**
  






## c. $y = 2x^3 - 15x^2 + 36x + 10$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    6x^2 - 30x + 36 & = 0 \\
    x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
    x & = \frac{-(-30) \pm \sqrt{(-30)^2 - 4(6)(36)}}{2(6)} \\
    x & = \frac{30 \pm \sqrt{36}}{12} \\
    x & = 
      \left\{
        \begin{array} {11}
          3 \\
          2
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Thus we have the potential extremas $x_0 = 3$ and $x_0 = 2$  

**Graph of the function:**
```{r}
curve(2*x^3 - 15*x^2 + 36*x + 10, -100,100)
```

Testing min, max with $x_0 = 3$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(\frac{11}{4})                    \qquad  &   f'(x_0 + 1) & = f'(4) \\
    f'(x_0 - \frac{1}{4}) & = 6(\frac{11}{4})^2 - 30(\frac{11}{4}) + 36   &   f'(x_0 + 1) & = 6(4)^2 - 30(4) + 36 \\
    f'(x_0 - \frac{1}{4}) & = -\frac{9}{8} < 0                            &   f'(x_0 + 1) & = 12 > 0 \\
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation} 
  \begin{aligned}
    f(3) & = 2(3)^3 - 15(3)^2 + 36(3) + 10 \\
    f(3) & = 37
  \end{aligned}
\end{equation}


**From the above, we gather the function is decreasing just before $(3,37)$ and increasing right after $(3,37)$
Thus, the function has a local minima at $(3,37)$**

Testing min, max with $x_0 = 2$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(\frac{7}{4})                    \qquad  &   f'(x_0 + \frac{1}{4}) & = f'(\frac{9}{4}) \\
    f'(x_0 - \frac{1}{4}) & = 6(\frac{7}{4})^2 - 30(\frac{7}{4}) + 36    &   f'(x_0 + \frac{1}{4}) & = 6(\frac{9}{4})^2 - 30(\frac{9}{4}) + 36 \\
    f'(x_0 - \frac{1}{4}) & = \frac{15}{8} > 0                          &   f'(x_0 + \frac{1}{4}) & = -\frac{9}{8} < 0 \\
  \end{aligned}
\end{equation}

Finding $f(2)$:
\begin{equation} 
  \begin{aligned}
    f(2) & = 2(2)^3 - 15(2)^2 + 36(2) + 10 \\
    f(2) & = 38
  \end{aligned}
\end{equation}

**From the above, we gather the function is increasing just before $(2,38)$ and decreasing right after $(2,38)$**
**Thus, the function has a local minima at $(3,37)$**

**The function does not have absolute minima nor maxima.**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    12x - 30 & = 0 \\
    x & = \frac{5}{2}
  \end{aligned}
\end{equation}

Testing the potential inflection point $(\frac{5}{2},f(\frac{5}{2}))$ :
\begin{equation} 
  \begin{aligned}
    f''(x_0 - \frac{1}{2}) & = f''(2)   \qquad  &   f''(x_0 + \frac{1}{2}) & = f''(3) \\
    f''(x_0 - \frac{1}{2}) & = 12(2) - 30       &   f''(x_0 + \frac{1}{2}) & = 12(3) - 30 \\
    f''(x_0 - \frac{1}{2}) & = -6 < 0           &   f''(x_0 + \frac{1}{2}) & = 6 > 0 \\
  \end{aligned}
\end{equation}

Finding $f(\frac{5}{2})$:
\begin{equation} 
  \begin{aligned}
    f(\frac{5}{2}) & = 2(\frac{5}{2})^3 - 15(\frac{5}{2})^2 + 36(\frac{5}{2}) + 10 \\
    f(\frac{5}{2}) & = \frac{75}{2}
  \end{aligned}
\end{equation}

**Thus $(3, \frac{75}{2})$ is an inflection point and is where the function curvature changes from concave to convex.**
  



## d. $y = x^3 -3x^2 +3x$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation} \label {eq_d_first_derivative}
  \begin{aligned}
  f'(x_0) & = 0 \\
  \frac{dy}{dx} & = 0 \\
  3x^2 -6x +3 & = 0 \\
  x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
  x & = \frac{-(-6) \pm \sqrt{(-6)^2 - 4(3)(3)}}{2(3)} \\
  x & = \frac{6 \pm \sqrt{0}}{6} \\
  x & = 1
       
  \end{aligned}
\end{equation}

Thus we have the extremas $x_0 = 1$
Graph of the function:
```{r}
curve(x^3 -3*x^2 +3*x, -100,100)
```

Finding min, max:
\begin{equation} \label {eq_c_minmax}
\begin{split}
  f(x_0) & = f(1)                    
  f(x_0) & = 1^3 - 3(1)^2 + 3(1)     
  f(x_0) & = 1 > 0                   
\end{split}
\end{equation}

There are 2 saddle points but neither are extremas

Finding inflection point:
\begin{equation} \label {eq_c_second_derivative}
\begin{split}
  f''(x_0) & = 0 \\
  \frac{d^2 y}{dx^2} & = 0 \\
  12x - 30 & = 0 \\
  x & = \frac{5}{2}
\end{split}
\end{equation}

We see:
\begin{equation} \label {eq_c1_inflection_point}
\begin{split}
  f''(x_0 + \frac{1}{2}) & =  f''(3) \\
  f''(3) & =  36 - 30\\
  f''(3) & = 6 > 0 \\
\end{split}
\end{equation}

Also:
\begin{equation} \label {eq_c2_inflection_point}
\begin{split}
  f''(x_0 - \frac{1}{2}) & =  f''(2) \\
  f''(2) & = 24 - 30  \\
  f''(2) & = -6 < 0 \\
\end{split}
\end{equation}

Thus $(3, \frac{75}{2})$ is an inflection point and the function is increasing on its domain.