---
title: "assignment03"
author: "Jeff Nguyen"
date: "03/09/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 03  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**

For continuous functions defined by $y= f(x)$, the point $(x_0,f(x_0))$ is a maxima or minima if $x_0$ is in the domain of the function and $f'(x) = 0$. Thus, for the below, we find and test extrema values $x_0$ for which $f'(x_0) = 0$.


## a. $y = x^2 - 6x + 5$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    2x - 6 & = 0 \\
    x & = 3
  \end{aligned}
\end{equation}

**Thus, we have the critical point $x_0 = 3$**  

**Graph of the function:**
```{r}
curve(x^2 - 6*x + 5, -2, 8)
```

Testing for min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0-1) & = f'(2)  \qquad &    f'(x_0+1) & = f'(4) \\
    f'(x_0-1) & = 2(2) - 6     &    f'(x_0+1) & = 2(4) - 6 \\
    f'(x_0-1) & = -2 < 0       &    f'(x_0+1) & = 2 > 0
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation}
  \begin{aligned}
    f(3) & = 3^2 - 6(3) + 5 \\
    f(3) & = -4
  \end{aligned}
\end{equation}

**We see that the function is decreasing on $(-\infty,3)$, and increasing on $(3,\infty)$**
**Thus, the absolute minima of the function is at $(3,-4)$**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    2 & = 0 \text{ (not possible)}
  \end{aligned}
\end{equation}

**Thus the inflection point does not exist for this function.**
  

## b. $y = -x^2 + 6x - 5$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    -2x + 6 & = 0 \\
    x & = 3
  \end{aligned}
\end{equation}

**Thus we have the critical point $x_0 = 3$** 

**Graph of the function:**
```{r}
curve(-x^2 + 6*x - 5, -100,100)
```

Testing for min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0 - 1) & = f'(2)  \qquad &    f'(x_0 + 1) & = f'(4) \\
    f'(x_0 - 1) & = -2(2) + 6    &    f'(x_0 + 1) & = -2(4) + 6 \\
    f'(x_0 - 1) & = 4 > 0        &    f'(x_0 + 1) & = -2 < 0
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation}
  \begin{aligned}
    f(3) & = -3^2 + 6(3) - 5 \\
    f(3) & = 4
  \end{aligned}
\end{equation}

**We see that the function is increasing on $(-\infty,3)$, and decreasing on $(3,\infty)$**
**Thus, the absolute maxima of the function is at $(3,4)$**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    -2 & = 0 \text{ (not possible)}
  \end{aligned}
\end{equation}

**Thus the inflection point does not exist for this function.**
  

## c. $y = 2x^3 - 15x^2 + 36x + 10$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    6x^2 - 30x + 36 & = 0 \\
    x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
    x & = \frac{-(-30) \pm \sqrt{(-30)^2 - 4(6)(36)}}{2(6)} \\
    x & = \frac{30 \pm \sqrt{36}}{12} \\
    x & = 
      \left\{
        \begin{array} {l}
          3 \\
          2
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Thus we have the potential extremas $x_0 = 3$ and $x_0 = 2$  

**Graph of the function:**
```{r}
curve(2*x^3 - 15*x^2 + 36*x + 10, -100,100)
```

Testing min, max with $x_0 = 3$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(\frac{11}{4})                    \qquad  &   f'(x_0 + 1) & = f'(4) \\
    f'(x_0 - \frac{1}{4}) & = 6(\frac{11}{4})^2 - 30(\frac{11}{4}) + 36   &   f'(x_0 + 1) & = 6(4)^2 - 30(4) + 36 \\
    f'(x_0 - \frac{1}{4}) & = -\frac{9}{8} < 0                            &   f'(x_0 + 1) & = 12 > 0 \\
  \end{aligned}
\end{equation}

Finding $f(3)$:
\begin{equation} 
  \begin{aligned}
    f(3) & = 2(3)^3 - 15(3)^2 + 36(3) + 10 \\
    f(3) & = 37
  \end{aligned}
\end{equation}


**From the above, we gather the function is decreasing just before $(3,37)$ and increasing right after $(3,37)$**
**Thus, the function has a local minima at $(3,37)$**

Testing min, max with $x_0 = 2$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(\frac{7}{4})                    \qquad  &   f'(x_0 + \frac{1}{4}) & = f'(\frac{9}{4}) \\
    f'(x_0 - \frac{1}{4}) & = 6(\frac{7}{4})^2 - 30(\frac{7}{4}) + 36    &   f'(x_0 + \frac{1}{4}) & = 6(\frac{9}{4})^2 - 30(\frac{9}{4}) + 36 \\
    f'(x_0 - \frac{1}{4}) & = \frac{15}{8} > 0                          &   f'(x_0 + \frac{1}{4}) & = -\frac{9}{8} < 0 \\
  \end{aligned}
\end{equation}

Finding $f(2)$:
\begin{equation} 
  \begin{aligned}
    f(2) & = 2(2)^3 - 15(2)^2 + 36(2) + 10 \\
    f(2) & = 38
  \end{aligned}
\end{equation}

**From the above, we gather the function is increasing just before $(2,38)$ and decreasing right after $(2,38)$**
**Thus, the function has a local maxima at $(2,38)$**

**The function does not have absolute minima nor maxima.**

Finding inflection point:
\begin{equation}
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    12x - 30 & = 0 \\
    x & = \frac{5}{2}
  \end{aligned}
\end{equation}

Testing the potential inflection point $(\frac{5}{2},f(\frac{5}{2}))$ :
\begin{equation} 
  \begin{aligned}
    f''(x_0 - \frac{1}{2}) & = f''(2)   \qquad  &   f''(x_0 + \frac{1}{2}) & = f''(3) \\
    f''(x_0 - \frac{1}{2}) & = 12(2) - 30       &   f''(x_0 + \frac{1}{2}) & = 12(3) - 30 \\
    f''(x_0 - \frac{1}{2}) & = -6 < 0           &   f''(x_0 + \frac{1}{2}) & = 6 > 0 \\
  \end{aligned}
\end{equation}

Finding $f(\frac{5}{2})$:
\begin{equation} 
  \begin{aligned}
    f(\frac{5}{2}) & = 2(\frac{5}{2})^3 - 15(\frac{5}{2})^2 + 36(\frac{5}{2}) + 10 \\
    f(\frac{5}{2}) & = \frac{75}{2}
  \end{aligned}
\end{equation}

**Thus $(\frac{5}{2}, \frac{75}{2})$ is an inflection point and is where the function curvature changes from concave to convex.**
  



## d. $y = x^3 -3x^2 +3x$

This is a polynomial function, thus, it is continuous everywhere.
We know:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    3x^2 -6x + 3 & = 0 \\
    x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
    x & = \frac{-(-6) \pm \sqrt{(-6)^2 - 4(3)(3)}}{2(3)} \\
    x & = \frac{6 \pm \sqrt{0}}{6} \\
    x & = 1
       
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = 1$
  
Graph of the function:
```{r}
curve(x^3 -3*x^2 +3*x, -100,100)
```


Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(0)       \qquad  &   f'(x_0 + 1) & = f'(2) \\
    f'(x_0 - 1) & = 3(0)^2 - 6(0) + 3   &   f'(x_0 + 1) & = 3(2)^2 - 6(2) + 3 \\
    f'(x_0 - 1) & = 3 > 0               &   f'(x_0 + 1) & = 3 > 0
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = 1^3 - 3(1)^2 + 3(1) \\
    f(1) & = 1
  \end{aligned}
\end{equation}

**From the above, we know the function increasing past $(1,1)$ and there is no local or absolute minima or maxima.**
  

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    6x - 6 & = 0 \\
    x & = 1
  \end{aligned}
\end{equation}

Testing the potential inflection point at $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(0)   \qquad  &   f''(x_0 + 1) & = f''(2) \\
    f''(x_0 - 1) & = 6(0) - 6         &   f''(x_0 + 1) & = 6(2) - 6 \\
    f''(x_0 - 1) & = -6 < 0           &   f''(x_0 + 1) & = 6 > 0
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(1,1)$, thus $(1,1)$ is an inflection point.**
  
## e. $y = (x-1)^3$

This is a polynomial function, thus, it is continuous everywhere.
Expanding:

\begin{equation}
  \begin{aligned}
    f(x) & = (x-1) ^3 \\
         & = (x-1)(x^2 - 2x + 1) \\
         & = x^3 - 2x^2 + x - x^2 + 2x - 1 \\
         & = x^3 - 3x^2 + 3x - 1 \\
  \end{aligned}
\end{equation}

Finding min, max:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    3x^2 - 6x + 3 & = 0 \\
    x^2 - 2x + 1 & = 0 \\
    (x-1)^2 & = 0 \\
    x & = 1
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = 1$
  
Graph of the function:
```{r}
curve(x^3 - 3*x^2 + 3*x - 1, -100,100)
```


Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(0)   \qquad  &   f'(x_0 + 1) & = f'(2) \\
    f'(x_0 - 1) & = (0-1)^2         &   f'(x_0 + 1) & = (2-1)^2 \\
    f'(x_0 - 1) & = 1 > 0           &   f'(x_0 + 1) & = 1 > 0
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (1-1)^3 \\
    f(1) & = 0
  \end{aligned}
\end{equation}

**From the above, we know the function increasing past $(1,0)$ and there is no local or absolute minima or maxima.**
  

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    2x - 2 & = 0 \\
    x & = 1
  \end{aligned}
\end{equation}

Testing the potential inflection point at $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(0)   \qquad  &   f''(x_0 + 1) & = f''(2) \\
    f''(x_0 - 1) & = 2(0) - 2         &   f''(x_0 + 1) & = 2(2) - 2 \\
    f''(x_0 - 1) & = -2 < 0            &   f''(x_0 + 1) & = 2 > 0
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(1,0)$, thus $(1,0)$ is an inflection point.**
  





## f. $y = (x^2 - 1)^2$

This is a polynomial function, thus, it is continuous everywhere.
Expanding:

\begin{equation}
  \begin{aligned}
    f(x) & = (x^2 - 1)^2 \\
         & = x^4 - 2x^2 + 1
  \end{aligned}
\end{equation}

Finding min, max:

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    4x^3 - 4x & = 0 \\
    4x(x^2 - 1) & = 0 \\
    4x(x - 1)(x + 1) & = 0 \\
    x & =
      \left\{
        \begin{array} {l}
          0 \\
          1 \\
          -1
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = -1$, $x_0 = 0$ and $x_0 = 1$
  
Graph of the function:
```{r}
curve(x^4 - 2*x^2 + 1, -2,2)
```


Testing min, max with $x_0 = -1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(-2)   \qquad  &   f'(x_0 + \frac{1}{4}) & = f'(-3/4) \\
    f'(x_0 - 1) & = 4(-2)^3 - 4(-2)  &   f'(x_0 + \frac{1}{4}) & = 4(-3/4)^3 - 4(-3/4) \\
    f'(x_0 - 1) & = -24 < 0          &   f'(x_0 + \frac{1}{4}) & = 21/16 > 0
  \end{aligned}
\end{equation}

Finding $f(-1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (-1)^4 - 2(-1)^2 + 1 \\
    f(1) & = 0
  \end{aligned}
\end{equation}

**From the above, we know the function has a local min at $(-1,0)$.**
  
  
Testing min, max with $x_0 = 0$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(-\frac{1}{4})               \qquad  &   f'(x_0 + \frac{1}{4}) & = f'(1/4) \\
    f'(x_0 - \frac{1}{4}) & = 4(-\frac{1}{4})^3 - 4(-\frac{1}{4})   &   f'(x_0 + \frac{1}{4}) & = 4(1/4)^3 - 4(1/4) \\
    f'(x_0 - \frac{1}{4}) & = \frac{15}{16} > 0                     &   f'(x_0 + \frac{1}{4}) & = -15/16 < 0
  \end{aligned}
\end{equation}

Finding $f(0)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (0)^4 - 2(0)^2 + 1 \\
    f(1) & = 1
  \end{aligned}
\end{equation}

**From the above, we know the function has a local max at $(0,1)$.**
  
Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{4}) & = f'(frac{3}{4})               \qquad  &   f'(x_0 + 1) & = f'(2) \\
    f'(x_0 - \frac{1}{4}) & = 4(\frac{3}{4})^3 - 4(\frac{3}{4})    &   f'(x_0 + 1) & = 4(2)^3 - 4(2) \\
    f'(x_0 - \frac{1}{4}) & = -\frac{21}{16} < 0                   &   f'(x_0 + 1) & = 24 > 0
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = (1)^4 - 2(1)^2 + 1 \\
    f(1) & = 0
  \end{aligned}
\end{equation}

**From the above, we know the function has a local min at $(1,0)$.**
**To recap, the function has local minimas at $(-1,0)$, $(1,0)$ and local maxima at $(0,1)$. It has no absolute minima or maxima.**
  
Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    12x^2 - 4 & = 0 \\
    3x^2 - 1 & = 0 \\
    x^2 & = \frac{1}{3} \\
    x & = 
      \left\{
        \begin{array} {l}
          \frac{1}{\sqrt{3}} \\
          -\frac{1}{\sqrt{3}}
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Testing the potential inflection point at $x_0 = -\frac{1}{\sqrt{3}}$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - \frac{2}{\sqrt{3}}) & = f''(-\sqrt{3})   \qquad  &   f''(x_0 + \frac{1}{\sqrt{3}}) & = f''(0) \\
    f''(x_0 - \frac{2}{\sqrt{3}}) & = 12(-\sqrt{3})^2 - 4      &   f''(x_0 + \frac{1}{\sqrt{3}}) & = 12(0)^2 - 4 \\
    f''(x_0 - \frac{2}{\sqrt{3}}) & = 32 > 0                  &   f''(x_0 + \frac{1}{\sqrt{3}}) & = -4 < 0
  \end{aligned}
\end{equation}

Finding $f(-\frac{1}{\sqrt{3}})$:
\begin{equation} 
  \begin{aligned}
    f(-\frac{1}{\sqrt{3}}) & = (-\frac{1}{\sqrt{3}})^4 - 2(-\frac{1}{\sqrt{3}})^2 + 1 \\
    f(-\frac{1}{\sqrt{3}}) & = \frac{2}{9}
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from convex to concave at $(-\frac{1}{\sqrt{3}},\frac{2}{9})$, thus $(-\frac{1}{\sqrt{3}},\frac{2}{9})$ is an inflection point.**

Testing the potential inflection point at $x_0 = \frac{1}{\sqrt{3}}$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - \frac{1}{\sqrt{3}}) & = f''(0)   \qquad  &   f''(x_0 + \frac{2}{\sqrt{3}}) & = f''(\sqrt{3}) \\
    f''(x_0 - \frac{1}{\sqrt{3}}) & = 12(0)^2 - 4      &   f''(x_0 + \frac{2}{\sqrt{3}}) & = 12(\sqrt{3})^2 - 4 \\
    f''(x_0 - \frac{1}{\sqrt{3}}) & = -4 < 0           &   f''(x_0 + \frac{2}{\sqrt{3}}) & = 32 > 0
  \end{aligned}
\end{equation}

Finding $f(\frac{1}{\sqrt{3}})$:
\begin{equation} 
  \begin{aligned}
    f(\frac{1}{\sqrt{3}}) & = (\frac{1}{\sqrt{3}})^4 - 2(\frac{1}{\sqrt{3}})^2 + 1 \\
    f(\frac{1}{\sqrt{3}}) & = \frac{4}{9}
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(\frac{1}{\sqrt{3}},\frac{4}{9})$, thus $(\frac{1}{\sqrt{3}},\frac{4}{9})$ is also an inflection point.**
  
## g. $y = \ln{\frac{x+1}{x^2+3}}$

We know that $\ln(X)$ is continuous on $(0,\infty)$.

Thus the domain of y is:
\begin{equation} 
  \begin{aligned}
    \left\{
        \begin{array} {l}
          x^2 + 3 > 0 \forall x \in \mathbf{R} \\
          x + 1 > 0 \Leftrightarrow \forall x \in (-1,\infty)
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Finding min, max:
\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    \frac{d(\ln{\frac{x+1}{x^2+3}})}{dx} & = 0 \\
    \frac{\frac{1}{\frac{x+1}{x^2+3}}.d\frac{x+1}{x^2+3}}{dx} & = 0 \\
    \frac{x^2+3}{x+1}.\Big[(x+1).d(\frac{1}{x^2+3}) + d(x+1).\frac{1}{x^2+3} \Big] & = 0 \\
    \frac{x^2+3}{x+1}.\Big[\frac{-(x+1).d(x^2+3)}{(x^2+3)^2} + \frac{1}{x^2+3} \Big] & = 0 \\
    \frac{x^2+3}{x+1}.\frac{-2x(x+1) + x^2 + 3}{(x^2 + 3)^2} & = 0 \\
    \frac{-2x^2 - 2x + x^2 + 3}{(x^2+3)(x+1)} & = 0 \\
    \frac{-x^2 - 2x + 3}{(x^2+3)(x+1)} & = 0 \\
    -x^2 - 2x + 3 & = 0 \\
    x & = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a} \\
    x & = \frac{-(-2) \pm \sqrt{(-2)^2 - 4(-1)(3)}}{2(-1)} \\
    x & = \frac{2 \pm \sqrt{16}}{-2} \\
    x & = 
      \left\{
        \begin{array} {l}
          1 \\
          -3 \text{  ,not valid as x > -1}
        \end{array}
      \right. 
  \end{aligned}
\end{equation}

Thus we have the potential extrema $x_0 = 1$

Graph of the function:
```{r}
curve(log((x+1)/(x^2+3)), 0.0000001,10)
```
Testing min, max with $x_0 = 1$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - \frac{1}{2}) & = f'(\frac{1}{2})                       \qquad  &   f'(x_0 + \frac{1}{2}) & = f'(\frac{3}{2}) \\ 
    f'(x_0 - \frac{1}{2}) & = \frac{-(\frac{1}{2})^2 - 2(\frac{1}{2}) + 3}
      {((\frac{1}{2})^2+3)(\frac{1}{2}+1)}                                  &   f'(x_0 + \frac{1}{2}) & = \frac{-(\frac{3}{2})^2 - 2(\frac{3}{2})+                                                                                       3}{((\frac{3}{2})^2+3)(\frac{3}{2}+1)} \\
    f'(x_0 - \frac{1}{2}) & = \frac{14}{39} > 0                             &   f'(x_0 + \frac{1}{2}) & = -\frac{6}{35} < 0 
  \end{aligned}
\end{equation}

Finding $f(1)$:
\begin{equation} 
  \begin{aligned}
    f(1) & = \ln{\frac{1+1}{1+3}} \\
    f(1) & = \ln{\frac{2}{4}} \\
    f(1) & = \ln{\frac{1}{2}} \\
    f(1) & = -\ln{2}
  \end{aligned}
\end{equation}

**From the above, we know the function has an absolute max at $(1,-\ln{2})$.**

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    \frac{d\Big[\frac{-x^2 - 2x + 3}{(x^2 + 3)(x + 1)}\Big]}{dx^2} & = 0 \\
    \frac{d\Big[\frac{-x^2 - 2x + 3}{x^3 + x^2 + 3x + 3}\Big]}{dx^2} & = 0 \\
    \frac{\Big[(-x^2 - 2x + 3).d(\frac{1}{x^3 + x^2 + 3x + 3}) + d(-x^2 - 2x + 3).(\frac{1}{x^3 + x^2 + 3x + 3}) \Big]}{dx^2} & = 0 \\
    \frac{(x^2 + 2x - 3)(3x^2 + 2x + 3)}{(x^3 + x^2 + 3x + 3)^2} - \frac{2x+2}{x^3+x^2+3x+3} & = 0 \\
    \frac{3x^4 + 6x^3 - 9x^2 + 2x^3 + 4x^2 - 6x + 3x^2 + 6x -9 - (2x + 2)(x^3 + x^2 + 3x + 3)}{(x^3 + x^2 + 3x +3)^2} & = 0 \\
    \frac{3x^4 + 8x^3 - 2x^2 - 9 - (2x^4 + 2x^3 + 2x^3 + 2x^2 + 6x^2 + 6x + 6x + 6)}{(x^3 + x^2 + 3x +3)^2} & = 0 \\
    \frac{3x^4 + 8x^3 - 2x^2 - 9 - (2x^4 + 4x^3 + 8x^2 + 12x + 6)}{(x^3 + x^2 + 3x +3)^2} & = 0 \\
    \frac{x^4 + 4x^3 - 10x^2 - 12x - 15}{(x^3 + x^2 + 3x +3)^2} & = 0 \\
    x^4 + 4x^3 - 10x^2 - 12x - 15 = 0
  \end{aligned}
\end{equation}

Using Ferrari method to solve this 4th degree polynomial equation $ax^4 + bx^3 + cx^2 +dx +e =0$. The 4 roots of this equation are:
\begin{equation}
  \begin{aligned}
    x & = 
      \left\{
        \begin{array} {l}
          -\frac{b}{4a} - S \pm \frac{1}{2}\sqrt{-4S^2 - 2p + \frac{q}{S}} \\
          -\frac{b}{4a} + S \pm \frac{1}{2}\sqrt{-4S^2 - 2p - \frac{q}{S}}
        \end{array}
      \right.
  \end{aligned}
\end{equation}

Where 

\begin{equation}
  \begin{aligned}
    \left\{
        \begin{array} {l}
          p = \frac{8ac - 3b^2}{8a^2} = \frac{8(1)(-10) - 3(4)^2}{8(1)^2} = \frac{-128}{8} = -16\\
          q = \frac{b^3 - 4abc + 8a^2d}{8a^3} = \frac{(4)^3 - 4(1)(4)(-10) + 8(1)^2(-12)}{8(1)^3} = \frac{128}{8} = 16
        \end{array}
      \right.
  \end{aligned}
\end{equation}

where
\begin{equation}
  \begin{aligned}
    \left\{
        \begin{array} {l}
          S = \frac{1}{2}\sqrt{(-\frac{2}{3}p + \frac{1}{3a}(Q + \frac{\Delta_0}{Q}))} \\
          Q = \sqrt[3]{\frac{\Delta_1 + \sqrt{\Delta_1^2 - 4\Delta_0^3}}{2}} = \sqrt[3]{\frac{-19712 + \sqrt{(-19712)^2 - 4(64^3)}}{2}}
        \end{array}
      \right.
  \end{aligned}
\end{equation}

with
\begin{equation}
  \begin{aligned}
    \left\{
        \begin{array} {l}
          \Delta_0 = c^2 - 3bd + 12ae = (-10)^2 - 3(4)(-12) + 12(1)(-15) = 64 \\
          \Delta_1 = 2c^3 - 9bcd + 27b^2e + 27ad^2 - 72ace = 2(-10)^3 - 9(4)(-10)(-12) + 27(4)^2(-15) + 27(1)(-12)^2 - 72(1)(-10)(-15) = -19712
        \end{array}
      \right.
  \end{aligned}
\end{equation}

The approx root of the equation is:
```{r}
root <- polyroot(c(-15, -12, -10, 4, 1))
# The equation has 2 non-complex roots:
Re(root)[abs(Im(root)) < 1e-6]
```

Since $(-1,\infty)$ is the domain. The only root is approximately 2.574355.

Testing the potential inflection point at $x_0 = 2.574355$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(1.574355)                    \qquad  &   f''(x_0 + 1) & = f''(3.574355) \\
    f''(x_0 - 1) & =  \frac{(1.574355)^4 + 4(1.574355)^3 - 
      10(1.574355)^2- 12(1.574355) - 15}
      {((1.574355)^3 + (1.574355)^2 + 3(1.574355) + 3)^2}     &   f''(x_0 + 1) & = \frac{(3.574355)^4 + 4(3.574355)^3 - 10(3.574355)^2-                                                                                  12(3.574355) - 15}{((3.574355)^3 + (3.574355)^2 + 3(3.574355) + 3)^2)} \\
    f''(x_0 - 1) & \approx -.185634 < 0                             &   f''(x_0 + 1) & \approx  0.03076888 > 0
  \end{aligned}
\end{equation}

Finding $f(2.574355)$:
\begin{equation} 
  \begin{aligned}
    f(2.574355) & = \ln{\frac{2.574355+1}{(2.574355)^2+3}} \\
    f(2.574355) & \approx -0.9908185 
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(2.574355,-0.9908185)$, thus $(2.574355,-0.9908185)$ is an inflection point.**
  

# **Question 2**

## a. $y = x^2 - 6x + 5$

The linear approximation at $x_0 = 1$:
\begin{equation}
  \begin{aligned}
    f(x) & \approx f(x_0) + f'(x_0)(x - x_0) \\
         & \approx (1^2 - 6(1) + 5) + [2(1) - 6](x - 1) \\
         & \approx -4(x - 1) \\
         & \approx -4x + 4
  \end{aligned}
\end{equation}
  
## b. $y = x^3 - 3x^2 + 3x$

The linear approximation at $x_0 = 1$:
\begin{equation}
  \begin{aligned}
    f(x) & \approx f(x_0) + f'(x_0)(x - x_0) \\
         & \approx (1^3 - 3(1)^2 + 3) + [3(1)^2 - 6(1) + 3](x - 1) \\
         & \approx 1
  \end{aligned}
\end{equation}
  
The quadratic approximation at $x_0 = 1$:
\begin{equation}
  \begin{aligned}
    f(x) & \approx f(x_0) + f'(x_0)(x - x_0) + \frac{f''(x_0)(x - x_0)^2}{2} \\
         & \approx (1^3 - 3(1)^2 + 3) + [3(1)^2 - 6(1) + 3](x - 1) + \frac{[6(1) - 6](x - 1)^2}{2}  \\
         & \approx 1
  \end{aligned}
\end{equation}
  
## c. $y = (x - 1)^3$

The linear approximation at $x_0 = 1$:
\begin{equation}
  \begin{aligned}
    f(x) & \approx f(x_0) + f'(x_0)(x - x_0) \\
         & \approx (1-1)^3 + [3(1)^2 - 6(1) + 3](x - 1) \\
         & \approx 0
  \end{aligned}
\end{equation}

The quadratic approximation at $x_0 = 1$:
\begin{equation}
  \begin{aligned}
    f(x) & \approx f(x_0) + f'(x_0)(x - x_0) + \frac{f''(x_0)(x - x_0)^2}{2} \\
         & \approx (1-1)^3 + [3(1)^2 - 6(1) + 3](x - 1) + \frac{[2(1) - 2](x - 1)^2}{2}  \\
         & \approx 0
  \end{aligned}
\end{equation}
  

# **Question 3**
The given production function is $Q = 100N - N^2$

This is a polynomial function, thus, it is continuous everywhere.
N >= 0 since N represent labor input.
We know:

\begin{equation}
  \begin{aligned}
    Q'(N_0) & = 0 \\
    \frac{dQ}{dN} & = 0 \\
    -2N + 100 & = 0 \\
    N & = 50
  \end{aligned}
\end{equation}

**Thus we have the critical point $N_0 = 50$**  

**Graph of the function:**
```{r}
curve(-x^2 + 100*x, from = 0, to = 100, xlab = 'N (labor input)', ylab = 'Q (production output)', main = 'Production Function')
```

Testing for min, max:
\begin{equation}
  \begin{aligned}
    Q'(N_0 - 1) & = Q'(49)  \qquad &    Q'(N_0 + 1) & = Q'(51) \\
    Q'(N_0 - 1) & = -2(49) + 100   &    Q'(N_0 + 1) & = -2(51) + 100 \\
    Q'(N_0 - 1) & = 2 > 0          &    Q'(N_0 + 1) & = -2 < 0
  \end{aligned}
\end{equation}

Finding $Q(50)$:
\begin{equation}
  \begin{aligned}
    Q(50) & = 100(50) - (50)^2 \\
    Q(50) & = 2500
  \end{aligned}
\end{equation}

**We see that the function is increasing on $(0,50)$, and decreasing on $(50,\infty)$**
**Thus, the absolute maxima of the function is at $(50,2500)$, i.e.**
**This means $N = 50$ is needed to maximize output.**

# **Question 4**

## a. $q = 100 - 1.6p$, when price is p = 45.00
At $p = 45$: $q = 100 - (1.6)(45) = 28$ 
We know the price elasticity of demand \epsilon_p is given by:

\begin{equation}
  \begin{aligned}
    \epsilon_p & = \frac{dq}{dp}.\frac{p}{q} \\
               & = (-1.6).\frac{45}{28} \\
               & = -\frac{18}{7} \\
               & \approx -2.571429
  \end{aligned}
\end{equation}
  

## b. $q = \frac{100}{p^3}$, when price is p = 20.00
At $p = 20$: $q = \frac{100}{20^3} = \frac{1}{80}$ 
We know the price elasticity of demand \epsilon_p is given by:

\begin{equation}
  \begin{aligned}
    \epsilon_p & = \frac{dq}{dp}.\frac{p}{q} \\
               & = \frac{-300}{p^4}.\frac{20}{\frac{1}{80}} \\
               & = \frac{-300(20)(80)}{20^4} \\
               & = -3
  \end{aligned}
\end{equation}
  
## c. $q = 10p^{-1.8}.y^{.6}$, when price is p = 20.30 and income y = 5800.00
At $p = 20.30$ and $y = 5800$: $q = 10.(20.30)^{-1.8}.(5800)^{.6} \approx 8.027197$ 
We know the price elasticity of demand \epsilon_p is given by:

\begin{equation}
  \begin{aligned}
    \epsilon_p & = \frac{\partial q}{\partial p}.\frac{p}{q} \\
               & = [10.y^{.6}.(-1.8).p^{-2.8}].\frac{20.30}{8.027197} \\
               & = [10.(5800)^{.6}.(-1.8).(20.30)^{-2.8}].\frac{20.30}{8.027197} \\
               & = -1.8
  \end{aligned}
\end{equation}
  
# **Question 5**

Total cost function $TC = 10 + 26q - 3.5q^2 + \frac{1}{3}q^3$

## a. Graph the function:

```{r definition-tc}
# Total Cost
tc <- function(x) 10 + 26*x - 3.5*x^2 + (1/3)*x^3
x <- seq(1,16,.1)
plot(x, tc(x), type = 'l', xlab = 'Output (q)', ylab = 'Total Cost (TC)', main = 'Total Costs as a Function of Output', col = 'black')
```

## b. Average Total Cost:
The average total cost is the total cost divided by quantity of output, i.e.:
$ATC = \frac{TC}{q} = \frac{10}{q} + 26 - 3.5q + \frac{1}{3}q^2$
Graph of the function:
```{r definition-atc}
atc <- function(x) (10/x) + 26 - 3.5*x + (1/3)*x^2
plot(x, atc(x), type = 'l', xlab = 'Output (q)', ylab = 'Average Total Cost (ATC)', main = 'Average Total Costs as a Function of Output', col = 'blue')

```

## c. Average Variable Cost:
The total variable cost is the total cost less the fixed cost, i.e. costs that are not affected by quantity of output.
The average total cost is the total variable cost divided by quantity of output. Thus:
$AVC = \frac{TVC}{q} = \frac{TC - FC}{q} = \frac{26q - 3.5q^2 + \frac{1}{3}q^3}{q} = 26 - 3.5q + \frac{1}{3}q^2$
Graph of the function:
```{r definition-avc}
avc <- function(x) 26 - 3.5*x + (1/3)*x^2
plot(x, atc(x), type = 'l', xlab = 'Output (q)', ylab = 'Average Variable Cost (AVC)', main = 'Average Variable Costs as a Function of Output', col = 'red')
```


## d. Marginal Cost:
The marginal cost is the change in total cost relative to the change in quantity of output.

Thus:
\begin{equation}
  \begin{aligned}
    MC(q) & = \frac{\Delta_{TC}}{\Delta_q} \\
          & = c'(q) \\
          & = \frac{d_TC}{dq} \\
          & = 26 - 7q + q^2
  \end{aligned}
\end{equation}

Graph of the function:
```{r definition-mc}
mc <- function(x) 26 - 7*x + x^2
plot(x, mc(x), type = 'l', xlab = 'Output (q)', ylab = 'Marginal Cost (MC)', main = 'Marginal Costs as a Function of Output', col = 'orange')
```
  

## e. ATC, AVC, MC in one coordinate

Graphs:
```{r}
x <- seq(1,11,.1)
# Average Total Cost curve
plot(x, atc(x), type = "l", xlab = "Output (q)", ylab = "Cost (c)", main = "Costs as a Function of Output", col = "blue")
par(new = TRUE)

# Average Variable Cost curve
plot(x, avc(x), type = "l", xaxt = "n", yaxt = "n", xlab = "", ylab = "", col = "red")
par(new = TRUE)

# Marginal Cost curve
plot(x, mc(x), type = "l", xaxt = "n", yaxt = "n", xlab = "", ylab = "", col = "orange")

# Add legend
legend("top", c("Average Total Cost", "Average Variable Cost", "Marginal Cost"), cex = 0.75, fill = c("blue", "red", "orange"))
```

**Comments:**  
1. When output is low, all ATC, AVC and MC curve are convex and decreasing, i.e. cost per unit of output decreases at small quantity of ouput. ATC falls most sharply as fixed cost is divided among small quantity of output. While AVC is falling due to this initial increase in output, MC is less than AVC.  
2. As AVC curve reaches its minima and starts to rise, ATC curve still continues to fall for some times. During this period, ATC falls at a higher rate than AVC rises. Note than MC starts increases at an accelerated rate and become higher than AVC before AVC reaches its minima.  
3. As output significantly increase, AVC increases sharply, offsetting the fixed cost. Per unit of output, variable cost is proportionally higher than fixed cost. Note that MC intersects AVC at the minima of AVC.
