---
title: "assignment05"
author: "Jeff Nguyen"
date: "18/09/2020"
output: html_document
---

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 05  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**

```{r definition data-question1}
library(quantmod)

# Set start date and end date of data
start_date <- "2014-01-02"
end_date <- "2020-09-18"

# Get data for JPM, FB and the 10 year T-bill (TNX)
getSymbols("JPM", src = "yahoo", from = start_date, to = end_date) # JPM
getSymbols("FB", src = "yahoo", , from = start_date, to = end_date) # FB
getSymbols("^TNX", src = "yahoo", from = start_date, to = end_date) # TNX (10-year T-bill)

# Get adjusted returns data for 01/2014
rJPM <- diff(log(to.monthly(JPM)$JPM.Adjusted))
rFB <- diff(log(to.monthly(FB)$FB.Adjusted))
rTNX <- (to.monthly(TNX)$TNX.Adjusted) / 1200 # Using monthly rate

# Calculate statistics
mean_rJPM <- mean(rJPM, na.rm = TRUE)
mean_rFB <- mean(rFB, na.rm = TRUE)
mean_rTNX <- mean(rTNX, na.rm = TRUE)

sd_rJPM <- sd(rJPM, na.rm = TRUE)
sd_rFB <- sd(rFB, na.rm = TRUE)

```

## a. Coefficient of variation
For JPM:
```{r}
# Coefficient of variation of Adjusted Returns of JPM
cv_rJPM <- sd_rJPM / mean_rJPM
```
\begin{equation}
  \begin{aligned}
    CV_{JPM} & = \frac{\sigma}{\mu}  \\
             & = \frac{`r sd_rJPM`}{`r mean_rJPM`}  \\
             & = `r cv_rJPM`  \\
    \text {where} \\
    \sigma & = \text {Standard deviation of Adjusted Returns} \\
    \mu & = \text {Mean of Adjusted Returns} \\
  \end{aligned}
\end{equation}

For FB:
```{r}
# Coefficient of variation of Adjusted Returns of FB
cv_rFB <- sd_rFB / mean_rFB
```
\begin{equation}
  \begin{aligned}
    CV_{FB} & = \frac{\sigma}{\mu}  \\
            & = \frac{`r sd_rFB`}{`r mean_rFB`}  \\
             & = `r cv_rFB`  \\
    \text {where} \\
    \sigma & = \text {Standard deviation of Adjusted Returns} \\
    \mu & = \text {Mean of Adjusted Returns } \\
  \end{aligned}
\end{equation}

## b. Sharpe Ratio
In this case, each portfolio carry 100% of JPM of FB so weighting is 100% of each stock for each portfolio.

For JPM:
```{r}
# Sharpe Ratio of a 100% JPM portfolio
sharpe_rJPM <- (mean_rJPM - mean_rTNX) / sd_rJPM 
```
\begin{equation}
  \begin{aligned}
    S_{JPM} & = \frac{E(r_p) - r_f}{\sigma_p}  \\
            & = \frac{`r mean_rJPM` - `r mean_rTNX`}{`r sd_rJPM`}  \\
            & = `r sharpe_rJPM` \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_p & = \text {Standard deviation of adjusted returns}
  \end{aligned}
\end{equation}

For FB:
```{r}
# Sharpe Ratio of a 100% JPM portfolio
sharpe_rFB <- (mean_rFB - mean_rTNX) / sd_rFB 
```
\begin{equation}
  \begin{aligned}
    S_{FB} & = \frac{E(r_p) - r_f}{\sigma_p}  \\
           & = \frac{`r mean_rFB` - `r mean_rTNX`}{`r sd_rFB`}  \\
            & = `r sharpe_rFB` \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_p & = \text {Standard deviation of adjusted returns}
  \end{aligned}
\end{equation}

## b. Sortino Ratio
For the purpose of calculating the Sortino ratio, we'll the mean of the Jan 2014 daily risk-free rate as the Minimum Acceptable Returns (MAR).

For JPM:
```{r}
# Calculating downside deviation using lower partial moment of order 2
# Assuming the 10 year T-bill returns as minimum acceptable returns MAR
mar <- mean_rTNX

# Deviation from MAR, this is a data frame, remove NA values
dev_rJPM_mar <- na.omit(rJPM - mar)

# Set positive deviations to be 0 as we only want downside value
devNegative_rJPM_mar <- replace(dev_rJPM_mar, dev_rJPM_mar > 0, 0)

# Calculate the Lower Partial Moment
downsideDev_JPM <- var(devNegative_rJPM_mar)

# Downside deviation
sd_downsideDev_JPM <- sqrt(downsideDev_JPM)

# Sortino Ratio
sortino_rJPM <- (mean_rJPM - mean_rTNX) / sd_downsideDev_JPM 
```
\begin{equation}
  \begin{aligned}
    SortinoRatio_{JPM} & = \frac{r_p - r_f}{\sigma_{downside}}  \\
                       & = \frac{`r mean_rJPM` - `r mean_rTNX`}{`r sd_downsideDev_JPM`}  \\
                       & = `r sortino_rJPM`  \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_{downside} & = \text {Standard deviation of the downside}
  \end{aligned}
\end{equation}

For FB:
```{r}
# Calculating downside deviation using lower partial moment of order 2
# Assuming the 10 year T-bill returns as minimum acceptable returns MAR
mar <- mean_rTNX

# Deviation from MAR, this is a data frame, also remove NA values
dev_rFB_mar <- na.omit(rFB - mar)

# Set positive deviations to be 0 as we only want downside value
devNegative_rFB_mar <- replace(dev_rFB_mar, dev_rFB_mar > 0, 0)

# Calculate the Lower Partial Moment
downsideDev_FB <- var(devNegative_rFB_mar)

# Downside deviation
sd_downsideDev_FB <- sqrt(downsideDev_FB)

# Sortino Ratio
sortino_rFB <- (mean_rFB - mean_rTNX) / sd_downsideDev_FB
```
\begin{equation}
  \begin{aligned}
    SortinoRatio_{JPM} & = \frac{r_p - r_f}{\sigma_{downside}}  \\
                       & = \frac{`r mean_rFB` - `r mean_rFB`}{`r sd_downsideDev_FB`}  \\
                       & = `r sortino_rFB`  \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_{downside} & = \text {Standard deviation of the downside}
  \end{aligned}
\end{equation}
  
In summary:  

Portfolio | Coefficient of Variation | Sharpe Ratio     | Sortino Ratio
---       | ---                      | ---              | ---    
JPM       | `r cv_rJPM`              | `r sharpe_rJPM`  | `r sortino_rJPM`
FB        | `r cv_rFB`               | `r sharpe_rFB`   | `r sortino_rFB`

For the period of Jan 2014:  
In terms of coefficient of variation, JPM shows more deviation from mean compared to FB, i.e. potentially havng higher returns volatility.  
In terms of Sharpe Ratio, FB has better risk-adjusted returns performance compared to JPM.  
In terms of Sortino Ratio, FB also generates better risk-adjusted performance with more weighting on the downside risk.  

# **Question 2**
```{r definition data-question2}

# Set start date and end date of data
start_date <- "2018-01-02"
end_date <- "2020-09-18"

# Get data for JPM, FB and the 10 year T-bill (TNX)
getSymbols("JPM", src = "yahoo", from = start_date, to = end_date) # JPM
getSymbols("FB", src = "yahoo", from = start_date, to = end_date) # FB
getSymbols("^TNX", src = "yahoo", from = start_date, to = end_date) # TNX (10-year T-bill)

# Get adjusted returns data for 01/2014
rJPM <- diff(log(to.monthly(JPM)$JPM.Adjusted))
rFB <- diff(log(to.monthly(FB)$FB.Adjusted))
rTNX <- (to.monthly(TNX)$TNX.Adjusted) / 1200 # Using monthly rate

# Calculate statistics
mean_rJPM <- mean(rJPM, na.rm = TRUE)
mean_rFB <- mean(rFB, na.rm = TRUE)
mean_rTNX <- mean(rTNX, na.rm = TRUE)

sd_rJPM <- sd(rJPM, na.rm = TRUE)
sd_rFB <- sd(rFB, na.rm = TRUE)

```

## a. Coefficient of variation
For JPM:
```{r}
# Coefficient of variation of Adjusted Returns of JPM
cv_rJPM <- sd_rJPM / mean_rJPM
```
\begin{equation}
  \begin{aligned}
    CV_{JPM} & = \frac{\sigma}{\mu}  \\
             & = \frac{`r sd_rJPM`}{`r mean_rJPM`}  \\
             & = `r cv_rJPM`  \\
    \text {where} \\
    \sigma & = \text {Standard deviation of Adjusted Returns} \\
    \mu & = \text {Mean of Adjusted Returns} \\
  \end{aligned}
\end{equation}

For FB:
```{r}
# Coefficient of variation of Adjusted Returns of FB
cv_rFB <- sd_rFB / mean_rFB
```
\begin{equation}
  \begin{aligned}
    CV_{FB} & = \frac{\sigma}{\mu}  \\
            & = \frac{`r sd_rFB`}{`r mean_rFB`}  \\
             & = `r cv_rFB`  \\
    \text {where} \\
    \sigma & = \text {Standard deviation of Adjusted Returns} \\
    \mu & = \text {Mean of Adjusted Returns } \\
  \end{aligned}
\end{equation}

## b. Sharpe Ratio
In this case, each portfolio carry 100% of JPM of FB so weighting is 100% of each stock for each portfolio.

For JPM:
```{r}
# Sharpe Ratio of a 100% JPM portfolio
sharpe_rJPM <- (mean_rJPM - mean_rTNX) / sd_rJPM 
```
\begin{equation}
  \begin{aligned}
    S_{JPM} & = \frac{E(r_p) - r_f}{\sigma_p}  \\
            & = \frac{`r mean_rJPM` - `r mean_rTNX`}{`r sd_rJPM`}  \\
            & = `r sharpe_rJPM` \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_p & = \text {Standard deviation of adjusted returns}
  \end{aligned}
\end{equation}

For FB:
```{r}
# Sharpe Ratio of a 100% JPM portfolio
sharpe_rFB <- (mean_rFB - mean_rTNX) / sd_rFB 
```
\begin{equation}
  \begin{aligned}
    S_{FB} & = \frac{E(r_p) - r_f}{\sigma_p}  \\
           & = \frac{`r mean_rFB` - `r mean_rTNX`}{`r sd_rFB`}  \\
            & = `r sharpe_rFB` \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_p & = \text {Standard deviation of adjusted returns}
  \end{aligned}
\end{equation}

## b. Sortino Ratio
For the purpose of calculating the Sortino ratio, we'll the mean of the Jan 2014 daily risk-free rate as the Minimum Acceptable Returns (MAR).

For JPM:
```{r}
# Calculating downside deviation using lower partial moment of order 2
# Assuming the 10 year T-bill returns as minimum acceptable returns MAR
mar <- mean_rTNX

# Deviation from MAR, this is a data frame, remove NA values
dev_rJPM_mar <- na.omit(rJPM - mar)

# Set positive deviations to be 0 as we only want downside value
devNegative_rJPM_mar <- replace(dev_rJPM_mar, dev_rJPM_mar > 0, 0)

# Calculate the Lower Partial Moment
downsideDev_JPM <- var(devNegative_rJPM_mar)

# Downside deviation
sd_downsideDev_JPM <- sqrt(downsideDev_JPM)

# Sortino Ratio
sortino_rJPM <- (mean_rJPM - mean_rTNX) / sd_downsideDev_JPM 
```
\begin{equation}
  \begin{aligned}
    SortinoRatio_{JPM} & = \frac{r_p - r_f}{\sigma_{downside}}  \\
                       & = \frac{`r mean_rJPM` - `r mean_rTNX`}{`r sd_downsideDev_JPM`}  \\
                       & = `r sortino_rJPM`  \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_{downside} & = \text {Standard deviation of the downside}
  \end{aligned}
\end{equation}

For FB:
```{r}
# Calculating downside deviation using lower partial moment of order 2
# Assuming the 10 year T-bill returns as minimum acceptable returns MAR
mar <- mean_rTNX

# Deviation from MAR, this is a data frame, also remove NA values
dev_rFB_mar <- na.omit(rFB - mar)

# Set positive deviations to be 0 as we only want downside value
devNegative_rFB_mar <- replace(dev_rFB_mar, dev_rFB_mar > 0, 0)

# Calculate the Lower Partial Moment
downsideDev_FB <- var(devNegative_rFB_mar)

# Downside deviation
sd_downsideDev_FB <- sqrt(downsideDev_FB)

# Sortino Ratio
sortino_rFB <- (mean_rFB - mean_rTNX) / sd_downsideDev_FB
```
\begin{equation}
  \begin{aligned}
    SortinoRatio_{JPM} & = \frac{r_p - r_f}{\sigma_{downside}}  \\
                       & = \frac{`r mean_rFB` - `r mean_rFB`}{`r sd_downsideDev_FB`}  \\
                       & = `r sortino_rFB`  \\
    \text {where} \\
    r_p & = \text {Mean of Adjusted Returns} \\
    r_f & = \text {Risk free rate} \\
    \sigma_{downside} & = \text {Standard deviation of the downside}
  \end{aligned}
\end{equation}
  
In summary:  

Portfolio | Coefficient of Variation | Sharpe Ratio     | Sortino Ratio
---       | ---                      | ---              | ---    
JPM       | `r cv_rJPM`              | `r sharpe_rJPM`  | `r sortino_rJPM`
FB        | `r cv_rFB`               | `r sharpe_rFB`   | `r sortino_rFB`

For the period of Jan 02, 2018 to Sep 18, 2020:  
In terms of coefficient of variation, both JPM and FB are highly volatile with JPM showing a significant negative drift from the mean returns while FB shows a positive drift from mean returns. +1 for FB   
In terms of Sharpe Ratio, FB has better risk-adjusted returns performance compared to JPM, which has negative Sharpe. +1 for FB
In terms of Sortino Ratio, FB also generates better risk-adjusted performance with more weighting on the downside risk. JPM also has negative Sortino. +1 for FB

Overall, based on the above statistics, FB is the better investment with better risk-adjusted returns

# **Question 3**

Given statistics
```{r definition-question3}
# Mean returns of portfolio
mean_p <- 5/100

# Standard deviation of returns of portfolio
sd_p <-  2.2/100

# VaR threshold
VaR_threshold <- 5
```


## a. 5% 1 year VaR
Calculating statistics
```{r 1year}
# Set scaling factor based on the period of evaluation
# In this example: {1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'}
scalingFactor <- 1

# Scaling returns
meanScaled_p <- mean_p * scalingFactor

# Scaling standard deviation
sdScaled_p <- sd_p * sqrt(scalingFactor)

# Value at Risk
z_stat <- qnorm(VaR_threshold/100, 0, 1, lower.tail = TRUE)
VaR_1year_p <- meanScaled_p + sdScaled_p * z_stat
```

Value at Risk following the standard normal distribution where the $z_{statistic}$ is the `r VaR_threshold`th percentile of the standard normal distribution.  

\begin{equation}
  \begin{aligned}
    \mu_{scaled} & = \mu * Scaling Factor  \\
                 & = `r mean_p` * `r scalingFactor` \\
                 & = `r meanScaled_p` \\
    \sigma_{scaled} & = \sigma * \sqrt{Scaling Factor}  \\             
                    & = `r sd_p` * \sqrt{`r scalingFactor`} \\
                    & = `r sdScaled_p`  \\
    \text {where} \\
    \mu_{scaled} & = \text {period-scaled expected excess returns} \\
    \mu & = \text {given mean returns} \\
    \sigma_{scaled} & = \text {period-scaled standard deviation of expected excess returns} \\
    \sigma & = \text {given standard deviation returns} \\
    Scaling Factor & = \text {scaled factor based on the period 1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'} \\
  \end{aligned}
\end{equation}

Looking up the $z_{statistic}$ for the `r VaR_threshold`th percentile of the standard normal distribution, we have $z_{statistic} = `r z_stat`$.
Thus, the Value at Risk of the portfolio is:  

\begin{equation}
  \begin{aligned}
    VaR & = \mu_{scaled} + \sigma_{scaled} * z_{statistic}  \\
        & = `r meanScaled_p` + `r sdScaled_p` * `r z_stat`  \\
        & = `r VaR_1year_p`
  \end{aligned}
\end{equation}

## b. 5% 6 months VaR
Calculating statistics
```{r}
# Set scaling factor based on the period of evaluation
# In this example: {1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'}
scalingFactor <- 1/2

# Scaling returns
meanScaled_p <- mean_p * scalingFactor

# Scaling standard deviation
sdScaled_p <- sd_p * sqrt(scalingFactor)

# Value at Risk
z_stat <- qnorm(VaR_threshold/100, 0, 1, lower.tail = TRUE)
VaR_6months_p <- meanScaled_p + sdScaled_p * z_stat
```

Value at Risk following the standard normal distribution where the $z_{statistic}$ is the `r VaR_threshold`th percentile of the standard normal distribution.  

\begin{equation}
  \begin{aligned}
    \mu_{scaled} & = \mu * Scaling Factor  \\
                 & = `r mean_p` * `r scalingFactor` \\
                 & = `r meanScaled_p` \\
    \sigma_{scaled} & = \sigma * \sqrt{Scaling Factor}  \\             
                    & = `r sd_p` * \sqrt{`r scalingFactor`} \\
                    & = `r sdScaled_p`  \\
    \text {where} \\
    \mu_{scaled} & = \text {period-scaled expected excess returns} \\
    \mu & = \text {given mean returns} \\
    \sigma_{scaled} & = \text {period-scaled standard deviation of expected excess returns} \\
    \sigma & = \text {given standard deviation returns} \\
    Scaling Factor & = \text {scaled factor based on the period 1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'} \\
  \end{aligned}
\end{equation}

Looking up the $z_{statistic}$ for the `r VaR_threshold`th percentile of the standard normal distribution, we have $z_{statistic} = `r z_stat`$.
Thus, the Value at Risk of the portfolio is:  

\begin{equation}
  \begin{aligned}
    VaR & = \mu_{scaled} + \sigma_{scaled} * z_{statistic}  \\
        & = `r meanScaled_p` + `r sdScaled_p` * `r z_stat`  \\
        & = `r VaR_6months_p`
  \end{aligned}
\end{equation}

## c. 5% 1 month VaR
Calculating statistics
```{r}
# Set scaling factor based on the period of evaluation
# In this example: {1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'}
scalingFactor <- 1/12

# Scaling returns
meanScaled_p <- mean_p * scalingFactor

# Scaling standard deviation
sdScaled_p <- sd_p * sqrt(scalingFactor)

# Value at Risk
z_stat <- qnorm(VaR_threshold/100, 0, 1, lower.tail = TRUE)
VaR_1month_p <- meanScaled_p + sdScaled_p * z_stat
```

Value at Risk following the standard normal distribution where the $z_{statistic}$ is the `r VaR_threshold`th percentile of the standard normal distribution.  

\begin{equation}
  \begin{aligned}
    \mu_{scaled} & = \mu * Scaling Factor  \\
                 & = `r mean_p` * `r scalingFactor` \\
                 & = `r meanScaled_p` \\
    \sigma_{scaled} & = \sigma * \sqrt{Scaling Factor}  \\             
                    & = `r sd_p` * \sqrt{`r scalingFactor`} \\
                    & = `r sdScaled_p`  \\
    \text {where} \\
    \mu_{scaled} & = \text {period-scaled expected excess returns} \\
    \mu & = \text {given mean returns} \\
    \sigma_{scaled} & = \text {period-scaled standard deviation of expected excess returns} \\
    \sigma & = \text {given standard deviation returns} \\
    Scaling Factor & = \text {scaled factor based on the period 1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'} \\
  \end{aligned}
\end{equation}

Looking up the $z_{statistic}$ for the `r VaR_threshold`th percentile of the standard normal distribution, we have $z_{statistic} = `r z_stat`$.
Thus, the Value at Risk of the portfolio is:  

\begin{equation}
  \begin{aligned}
    VaR & = \mu_{scaled} + \sigma_{scaled} * z_{statistic}  \\
        & = `r meanScaled_p` + `r sdScaled_p` * `r z_stat`  \\
        & = `r VaR_1month_p`
  \end{aligned}
\end{equation}

## d. 5% 1 day VaR
Calculating statistics
```{r}
# Set scaling factor based on the period of evaluation
# In this example: {1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'}
scalingFactor <- 1/250

# Scaling returns
meanScaled_p <- mean_p * scalingFactor

# Scaling standard deviation
sdScaled_p <- sd_p * sqrt(scalingFactor)

# Value at Risk
z_stat <- qnorm(VaR_threshold/100, 0, 1, lower.tail = TRUE)
VaR_1day_p <- meanScaled_p + sdScaled_p * z_stat
```

Value at Risk following the standard normal distribution where the $z_{statistic}$ is the `r VaR_threshold`th percentile of the standard normal distribution.  

\begin{equation}
  \begin{aligned}
    \mu_{scaled} & = \mu * Scaling Factor  \\
                 & = `r mean_p` * `r scalingFactor` \\
                 & = `r meanScaled_p` \\
    \sigma_{scaled} & = \sigma * \sqrt{Scaling Factor}  \\             
                    & = `r sd_p` * \sqrt{`r scalingFactor`} \\
                    & = `r sdScaled_p`  \\
    \text {where} \\
    \mu_{scaled} & = \text {period-scaled expected excess returns} \\
    \mu & = \text {given mean returns} \\
    \sigma_{scaled} & = \text {period-scaled standard deviation of expected excess returns} \\
    \sigma & = \text {given standard deviation returns} \\
    Scaling Factor & = \text {scaled factor based on the period 1: '1 year', 1/2: '6 months', 1/12: '1 month', 1/250: '1 day'} \\
  \end{aligned}
\end{equation}

Looking up the $z_{statistic}$ for the `r VaR_threshold`th percentile of the standard normal distribution, we have $z_{statistic} = `r z_stat`$.
Thus, the Value at Risk of the portfolio is:  

\begin{equation}
  \begin{aligned}
    VaR & = \mu_{scaled} + \sigma_{scaled} * z_{statistic}  \\
        & = `r meanScaled_p` + `r sdScaled_p` * `r z_stat`  \\
        & = `r VaR_1day_p`
  \end{aligned}
\end{equation}

In summary:  

Period  | 1 year          | 6 months          | 1 month           | 1 day
---     | ---             | ---               | ---               | ---       
5% VaR  | `r VaR_1year_p` | `r VaR_6months_p` | `r VaR_1month_p`  | `r VaR_1day_p`

# **Question 4**

```{r definition data-question4}

# Set start date and end date of data
start_date <- "2018-01-02"
end_date <- "2020-09-18"

# Get data for JPM, FB and the 10 year T-bill (TNX)
getSymbols("JPM", src = "yahoo", from = start_date, to = end_date) # JPM
getSymbols("FB", src = "yahoo", from = start_date, to = end_date) # FB
getSymbols("AAPL", src = "yahoo", from = start_date, to = end_date) # AAPL
getSymbols("^TNX", src = "yahoo", from = start_date, to = end_date) # TNX (10-year T-bill)

# Get adjusted returns data for 01/2014
rJPM <- na.omit(diff(log(to.monthly(JPM)$JPM.Adjusted)))
rFB <- na.omit(diff(log(to.monthly(FB)$FB.Adjusted)))
rAAPL <- na.omit(diff(log(to.monthly(AAPL)$AAPL.Adjusted)))
rTNX <- (to.monthly(TNX)$TNX.Adjusted) / 1200 # Using monthly rate

# Calculate statistics
mean_rJPM <- mean(rJPM, na.rm = TRUE)
mean_rFB <- mean(rFB, na.rm = TRUE)
mean_rAAPL <- mean(rAAPL, na.rm = TRUE)
mean_rTNX <- mean(rTNX, na.rm = TRUE)

sd_rJPM <- sd(rJPM, na.rm = TRUE)
sd_rFB <- sd(rFB, na.rm = TRUE)
sd_rAAPL <- sd(rAAPL, na.rm = TRUE)
sd_rTNX <- sd(rTNX, na.rm = TRUE)


cov_rJPM_rJPM <- cov(rJPM, rJPM)
cov_rAAPL_rAAPL <- cov(rAAPL, rAAPL)
cov_rFB_rFB <- cov(rFB, rFB)
cov_rJPM_rFB <- cov(rJPM, rFB)
cov_rJPM_rAAPL <- cov(rJPM, rAAPL)
cov_rFB_rAAPL <- cov(rFB, rAAPL)

cor_rJPM_rJPM <- cor(rJPM, rJPM)
cor_rAAPL_rAAPL <- cor(rAAPL, rAAPL)
cor_rFB_rFB <- cor(rFB, rFB)
cor_rJPM_rFB <- cor(rJPM, rFB)
cor_rJPM_rAAPL <- cor(rJPM, rAAPL)
cor_rFB_rAAPL <- cor(rFB, rAAPL)

```

Parameters for the Markowitz portfolio model are:  
1. Expected Returns  
2. Standard deviation from mean returns  
3. Covariance of one asset returns to another.  

The Covariance and Correlation formula is:
\begin{equation}
  \begin{aligned}
    Cov_{X,Y}  & =  \sum_{i=1}^{n} \frac{(X_i - \overline{X}) * (Y_i - \overline{Y})}{n-1} \\
    Corr_{X,Y} & =  \frac{Cov_{X,Y}}{\sigma_X * \sigma_Y}  \\
    \text {where} \\
    X_i & = \text {the observation value of returns of X} \\
    \overline{X} & = \text {the expected mean returns of X} \\
    Y_i & = \text {the observation value of returns of Y} \\
    \overline{Y} & = \text {the expected mean returns of Y} \\
    n & = \text {number of observations}
    
  \end{aligned}
\end{equation}

Using R, we have the parameters for the Markowitz Portfolio Model:

Stock  | Mean           | Standard Deviation
---    | ---            | ---                      
AAPL   | `r mean_rAAPL` | `r sd_rAAPL` 
JPM    | `r mean_rJPM`  | `r sd_rJPM`
FB     | `r mean_rFB  ` | `r sd_rFB`

And the correlation matrix

Correlation | AAPL                  | JPM                 | FB
---         | ---                   | ---                 | ---                      
AAPL        | `r cor_rAAPL_rAAPL`   | `r cor_rJPM_rAAPL`  | `r cor_rFB_rAAPL` 
JPM         | `r cor_rJPM_rAAPL`    | `r cor_rJPM_rJPM`   | `r cor_rJPM_rFB` 
FB          | `r cor_rFB_rAAPL`     | `r cor_rJPM_rFB`    | `r cor_rFB_rFB` 


And the covariance matrix

Covariance  | AAPL                  | JPM                 | FB
---         | ---                   | ---                 | ---                      
AAPL        | `r cov_rAAPL_rAAPL`   | `r cov_rJPM_rAAPL`  | `r cov_rFB_rAAPL` 
JPM         | `r cov_rJPM_rAAPL`    | `r cov_rJPM_rJPM`   | `r cov_rJPM_rFB` 
FB          | `r cov_rFB_rAAPL`     | `r cov_rJPM_rFB`    | `r cov_rFB_rFB` 

# **Question 5**

Given parameters  

```{r definition-question5}
# Mean Returns
mean_rStock1 <- 10/100
mean_rStock2 <- 12/100
mean_rf <- 5/100

# Variance of returns
var_rStock1 <- 0.025
var_rStock2 <- 0.030

# Standard deviation of returns
sd_rStock1 <- sqrt(var_rStock1)
sd_rStock2 <- sqrt(var_rStock2)

# Covariance of Returns
cov_rStock1_rStock2 <- 0.015

# Correlation of Returns
cor_rStock2_rStock2 <- cov_rStock1_rStock2 / (sd_rStock1 * sd_rStock2)
```


Asset      | Mean Returns      | Variance           | Pair    | \sigma_{1,2}
---        | ---               | ---                | ---     | ---                      
Stock 1    | `r mean_rStock1`  | `r var_rStock1`    | (1,2)   | `r cov_rStock1_rStock2` 
Stock 2    | `r mean_rStock2`  | `r var_rStock2`    |         | 
Risk Free  | `r mean_rf`       |                    |         | 
  
  
Since the investor's objective is to minimize risk, we solve for the global minimum variance combination of the two assets.
Let $x_i$ denotes the weight of the investment in asset i $(i = 1,2)$, and assume all money is invested in i, meaning $\sum {x_i} = x_1 + x_2 = 1$.

\begin{equation}
  \begin{aligned}
    \text {The returns of the portfolio is:} \\
    R_{p,x} & = x_1 * r_1 + x_2 * r_2 \\
    \text {The expected returns on the portfolio is:} \\
    \mu_{p,x} & = E[R_{p,x}] \\
              & = x_1 * \mu_1 + x_2 * \mu_2  \\
    \text {The variance of the portfolio returns is:} \\
    \sigma_{p,x}^2 & = var(R_{p,x})  \\
                   & = x_1 * \sigma_1^2 + x_2 * \sigma_2^2 + 2 * x_1 * x_2 * \sigma_{1,2}
  \end{aligned}
\end{equation}
  
The global minimum variance portfolio $m = (m_1,m_2)$ is the solution of the constrained minimization problem:

\begin{equation}
  \begin{aligned}
    min \sigma_{p,m}^2 & = var(R_{p,m})  \\
                       & = m_1^2 * \sigma_1^2 + m_2^2 * \sigma_2^2 + 2 * m_1 * m_2 * \sigma_{1,2} \\
    \text {s.t. } m_1 + m_2 & = 1 \\
    \text {rewrite: } \\
    min \sigma_{p,m}^2 & = min[m_1^2 * \sigma_1^2 + (1-m_1)^2 * \sigma_2^2 + 2 * m_1 * (1 - m_1) * \sigma_{1,2}] \\
                       & = min[m_1^2 * (\sigma_1^2 + \sigma_2^2 - 2 * \sigma_{1,2}) + m_1 * (2 * \sigma_{1,2} - 2 * \sigma_2^2) + \sigma_2^2]  \\
    \text {plug in: }
    min \sigma_{p,m}^2 & = min[0.025 * m_1^2 - 0.03 * m_1 + 0.03]
  \end{aligned}
\end{equation}

Find the critical point:

\begin{equation}
  \begin{aligned}
    \frac{d\sigma_{p,m}^2}{dm} & = 0 \\
    \frac{d(0.025 * m_1^2 - 0.03 * m_1 + 0.03)}{dm} & = 0 \\
      .05 * m_1 - 0.03 & = 0  \\
    m_1 & = 0.6 = 60\%  \\
    \text {thus, }   \\
    m_2 & = 1 - 0.6 = 0.4 = 40\%
  \end{aligned}
\end{equation}

Graphing the function:  
```{r}

# The Variance function of the portfolio
fVar <- function(m1) var_rStock1 * m1^2 + var_rStock2 * (1 - m1)^2 + 2 * m1 * (1 - m1) * cov_rStock1_rStock2

# Set the weighting
m1 <- .6
m2 <- .4

# Plot of the variance function with respect to w1.
w1 <- seq(0, 1, .05)
plot(fVar, w1, xlab = "Weight of Stock 1 Relative to Portfolio", ylab = "Portfolio Variance", main = "Minimum Variance Portfolio"); abline(v = m1, col = "red")
points(m1, fVar(m1), col='green')
```

We see indeed the minimum is at $m_1 = 0.6$

Thus, the optimum weights of each stocks in the portfolio to satisfy the objective of minimum risk is:  

Asset      | Weight            
---        | ---                                  
Stock 1    | 60\% 
Stock 2    | 40\%

