---
title: "assignment07"
author: "Jeff Nguyen"
date: "17/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 07  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**  

```{r}
a11 <- 15
a12 <- 1
a21 <- 1
a22 <- 2

x1 <- .2
x2 <- .5

detA <- a11*a22 - a12*a21
```
\begin{equation}
  \begin{aligned}
    A & = \begin{pmatrix} `r a11`  & `r a12`  \\ `r a21`  & `r a22`  \\ \end{pmatrix} \\
    X & = \begin{pmatrix} `r x1`   \\  `r x2`     \\        \end{pmatrix}
  \end{aligned}
\end{equation}


## a. Find determinant of A  

\begin{equation}
  \begin{aligned} 
    detA & = \begin{vmatrix} `r a11`  & `r a12`  \\ `r a21`  & `r a22`  \\ \end{vmatrix} \\
         & = `r a11` * `r a22` - `r a12` * `r a21`  \\
         & = `r detA`\\
  \end{aligned}
\end{equation}

## b. Find the inverse of A  

\begin{equation}
  \begin{aligned}
    A^{-1} & = \frac{1}{detA} * \begin{pmatrix} `r a22`  & `r -a12`  \\ `r -a21`  & `r a11`  \\ \end{pmatrix} \\
           & = \frac{1}{`r detA`} * \begin{pmatrix} `r a22`  & `r -a12`  \\ `r -a21`  & `r a11`  \\ \end{pmatrix} \\
           & = \begin{pmatrix} \frac{`r a22`}{`r detA`}  & \frac{`r -a12`}{`r detA`}  \\ \frac{`r -a21`}{`r detA`}  & \frac{`r a11`}{`r detA`}  \\ \end{pmatrix} \\
  \end{aligned}
\end{equation}

## c. Find the trace of A  

\begin{equation}
  \begin{aligned}
    tr(A) & = `r a11` + `r a22`  \\
          & = `r a11 + a22`\\
  \end{aligned}
\end{equation}

## d. Find the quadractic form X'AX  

\begin{equation}
  \begin{aligned}
    x'Ax & = a_{11} * x_1^2 + (a_{12} + a_{21}) *x_1*x_2 + a_{22} * x_2^2  \\
         & = `r a11 * x1^2 + (a12 + a21) *x1*x2 + a22 * x2^2` \\
  \end{aligned}
\end{equation}

## e. Find $x_1:x_2$ that min(X'AX)  

Let $k = \frac{x_1}{x_2}$. We have $x_1 = k * x_2$. Substitute in $x'Ax$:  

\begin{equation}
  \begin{aligned}
    x'Ax & = a_{11} * x_1^2 + (a_{12} + a_{21}) *x_1*x_2 + a_{22} * x_2^2  \\
         & = a_{11} * k^2 * x_2^2 + (a_{12} + a_{21}) *k*x_2^2 + a_{22} * x_2^2  \\
         & = `r a11` * k^2 * x_2^2 + `r a12 + a21` *k*x_2^2 + `r a22` * x_2^2 \\
         & = (`r a11`*k^2 + `r a12 + a21`*k + `r a22`) * x_2^2  \\
  \end{aligned}
\end{equation}

Find the critical point of x'Ax: $z = f(x_1, x_2) = 15*x_1^2+ 2*x_1*x_2 + 2*x_2^2$
The first order condition is: 

\begin{equation}
  \begin{aligned}
    \frac{\partial f}{\partial x_1} &= 0 \\
    30 * x_1 + 2*x_2 &= 0 \\
  \end{aligned}
\end{equation}

\begin{equation}
  \begin{aligned}
    \frac{\partial f}{\partial x_2} &= 0 \\
    4 * x_2 + 2*x_1 &= 0 \\
  \end{aligned}
\end{equation}

Solving the two above equation together yields $x_1 = 0$, $x_2 = 0$ and $z = 0$. Thus the point $(0,0,0)$ is the extrema.

To test for the second order condition, form the Hessian:

\begin{equation}
  \begin{aligned}
    H & = \begin{pmatrix} f_{xx}  & f_{xy}  \\ f_{yx}  & f_{yy}  \\ \end{pmatrix} \\
    H & = \begin{pmatrix} f_{x_1x_1}  & f_{x_1x_2}  \\ f_{x_2x_1}  & f_{x_2x_2}  \\ \end{pmatrix} \\  
    H & = \begin{pmatrix} 30  & 2  \\ 2  & 4  \\ \end{pmatrix} \\
  \end{aligned}
\end{equation}

We can see:

\begin{equation}
  \begin{aligned}
    \begin{vmatrix} 30  \\ \end{vmatrix} \\ > 0 \\
    \begin{vmatrix} 30 & 2 \\ 2 & 4  \\ \end{vmatrix} \\ = 30*4 - 2*2 > 0
  \end{aligned}
\end{equation}

Thus H is positive definite and have a minimum at (0,0,0).

## f. Find $x_1:x_2$ that min(X'AX) s.t. $x_1 + x_2 = 1$  

Similar to e. but adding the constraint $g(x1, x2) = x_1 + x_2 = 1$

The Lagrange becomes:

\begin{equation}
  \begin{aligned}
    L(x_1,x_2,\lambda) & = 15*x_1^2 + 2*x_1*x_2 + 2*x_2^2 + \lambda*(1 - x_1 - x_2)
  \end{aligned}
\end{equation}

Find the critical point of $L(x_1,x_2,\lambda)$
The first order condition is: 

\begin{equation}
  \begin{aligned}
    \frac{\partial L}{\partial x_1} &= 0 \\
    30*x_1 + 2*x_2 - \lambda &= 0 \\
  \end{aligned}
\end{equation}

\begin{equation}
  \begin{aligned}
    \frac{\partial L}{\partial x_2} &= 0 \\
    2*x_1 + 4*x_2 - \lambda &= 0 \\
  \end{aligned}
\end{equation}

Also 

\begin{equation}
  \begin{aligned}
    x_1 + x_2 &= 0 \\
  \end{aligned}
\end{equation}

Solving these yields: $x_1 = \frac{1}{20}$, $x_2 = \frac{19}{20}$ and $\lambda = \frac{271}{70}$

The bordered Hessian matrix is:

\begin{equation}
  \begin{aligned}
    H & = \begin{pmatrix} 
            f_{\lambda \lambda}  & f_{\lambda x_1}  & f_{\lambda x_2 } \\
            f_{x_1 \lambda}  & f_{x_1 x_1}  & f_{x_1 x_2 } \\
            f_{x_2 \lambda}  & f_{x_2 x_1}  & f_{x_2 x_2 }
          \end{pmatrix} \\
    H & = \begin{pmatrix} 
            0  & -1  & -1 \\
            -1  & 30  & 2 \\
            -1  & 2  & 4 \\
          \end{pmatrix} \\
  \end{aligned}
\end{equation}

Thus the min x'Ax happens at \begin{pmatrix} \frac{1}{20}  \\ \frac{19}{20} \end{pmatrix}

## g. Find the eigenvalues of A.  

We have the 2x2 system $x' = A*x$ where 
\begin{equation}
  \begin{aligned}
    A & = \begin{pmatrix} 15  & 1  \\ 1  & 2  \\ \end{pmatrix} \\
  \end{aligned}
\end{equation}

Solve the characteristic equation of this system for the eigenvalues:

\begin{equation}
  \begin{aligned}
    \lambda^2 - tr(A) * \lambda + detA &= 0 \\
    \lambda^2 - 17*\lambda + 29 & = 0 \\
    \lambda &= \frac{17 \pm \sqrt{173}}{2} \\
  \end{aligned}
\end{equation}

## h. Find the eigenvectors of A.  

For $\lambda_1 = \frac{17 + \sqrt{173}}{2}$:  
We need to solve:  

\begin{equation}
  \begin{aligned}
    (A - \lambda_1*I)v & = 0  \\
    \begin{pmatrix} 15 - \frac{17 + \sqrt{173}}{2}  & 1  \\ 1  & 2 - \frac{17 + \sqrt{173}}{2}  \\ \end{pmatrix} * \begin{pmatrix} a_1 \\ a_2                \end{pmatrix} & = \begin{pmatrix} 0 \\ 0 \end{pmatrix} \\
    \begin{pmatrix} \frac{13 - \sqrt{173}}{2}  & 1  \\ 1  & \frac{-13 - \sqrt{173}}{2}  \\ \end{pmatrix} * \begin{pmatrix} a_1 \\ a_2                        \end{pmatrix} & = \begin{pmatrix} 0 \\ 0 \end{pmatrix}  \\
  \end{aligned}
\end{equation}

By inspection, the notrivial solutions to this system and hence the eigenvectors for the eigenvalue $\lambda_1 = \frac{17 + \sqrt{173}}{2}$ are all nonzero scalar multiples of:  

\begin{equation}
  \begin{aligned}
    v_1 & = \begin{pmatrix} \frac{13 + \sqrt{173}}{2}  \\ 1  \\ \end{pmatrix} 
  \end{aligned}
\end{equation}

For $\lambda_2 = \frac{17 - \sqrt{173}}{2}$:  
We need to solve:  

\begin{equation}
  \begin{aligned}
    (A - \lambda_1*I)v & = 0  \\
    \begin{pmatrix} 15 - \frac{17 - \sqrt{173}}{2}  & 1  \\ 1  & 2 - \frac{17 - \sqrt{173}}{2}  \\ \end{pmatrix} * \begin{pmatrix} a_1 \\ a_2                \end{pmatrix} & = \begin{pmatrix} 0 \\ 0 \end{pmatrix} \\
    \begin{pmatrix} \frac{13 + \sqrt{173}}{2}  & 1  \\ 1  & \frac{-13 + \sqrt{173}}{2}  \\ \end{pmatrix} * \begin{pmatrix} a_1 \\ a_2                        \end{pmatrix} & = \begin{pmatrix} 0 \\ 0 \end{pmatrix}  \\
  \end{aligned}
\end{equation}

By inspection, the notrivial solutions to this system and hence the eigenvectors for the eigenvalue $\lambda_1 = \frac{17 + \sqrt{173}}{2}$ are all nonzero scalar multiples of:  

\begin{equation}
  \begin{aligned}
    v_1 & = \begin{pmatrix} \frac{13 - \sqrt{173}}{2}  \\ 1  \\ \end{pmatrix} 
  \end{aligned}
\end{equation}

# **Question 2**  

\begin{equation}
  \begin{aligned}
    A & = \begin{pmatrix} 3 & 0 & 1 \end{pmatrix} \\
    B & = \begin{pmatrix} -1 & 4 & 5 \end{pmatrix} \\
    C & = \begin{pmatrix} 1 & 3 & -1 \\ 2 & 3 & 1 \\ -1 & 1 & 0 \end{pmatrix} \\
  \end{aligned}
\end{equation}

## a. Find $A'$, $C'$  

\begin{equation}
  \begin{aligned}
    A' & = \begin{pmatrix} 3 \\ 0 \\ 1 \end{pmatrix} \\
    C & = \begin{pmatrix} 1 & 2 & -1 \\ 3 & 3 & 1 \\ -1 & 1 & 0 \end{pmatrix} \\
  \end{aligned}
\end{equation}

## b. Find $C^{-1}$  

The matrix of cofactors from C is: 
\begin{equation}
  \begin{aligned}
    \begin{pmatrix} -1 & -1 & 5 \\ -1 & -1 & -4 \\ 6 & -3 & -3 \end{pmatrix} \\
  \end{aligned}
\end{equation}

Thus, the adjoint of C is:

\begin{equation}
  \begin{aligned}
    adj(C) & = \begin{pmatrix} -1 & -1 & 6 \\ -1 & -1 & -3 \\ 5 & -4 & -3 \end{pmatrix} \\
  \end{aligned}
\end{equation}

Assume C is invertible then:  

\begin{equation}
  \begin{aligned}
    C^{-1} &= \frac{1}{detC} * adj(C)
           & = \frac{1}{1*(0-1) -3*(0+1) + (-1)*(2+3)} * \begin{pmatrix} -1 & -1 & 6 \\ -1 & -1 & -3 \\ 5 & -4 & -3 \end{pmatrix} \\
           & = \frac{-1}{9} * \begin{pmatrix} -1 & -1 & 6 \\ -1 & -1 & -3 \\ 5 & -4 & -3 \end{pmatrix} \\
           & = \begin{pmatrix} \frac{1}{9} & \frac{1}{9} & \frac{-2}{3} \\
                               \frac{1}{9} & \frac{1}{9} & \frac{1}{3} \\
                               \frac{-5}{9} & \frac{4}{9} & \frac{1}{3} \\
                \end{pmatrix} \\
  \end{aligned}
\end{equation}

## c. Find AB', A'B, CA', BCA'  

\begin{equation}
  \begin{aligned}
    AB' & = \begin{pmatrix} 3 & 0 & 1 \end{pmatrix} * \begin{pmatrix} -1 \\ 4 \\ 5 \end{pmatrix} \\
        & = \begin{pmatrix} 3*(-1) + 0*(4) + 1 * 5 \end{pmatrix} \\
        & = \begin{pmatrix} 2 \end{pmatrix} \\
  \end{aligned}
\end{equation}

\begin{equation}
  \begin{aligned}
    A'B & = \begin{pmatrix} 3 \\ 0 \\ 1 \end{pmatrix} * \begin{pmatrix} -1 & 4 & 5 \end{pmatrix} \\
        & = \begin{pmatrix} 3*-1 & 3*4 & 3*5 \\ 0*-1 & 0*4 & 0*5 \\ 1*-1 & 1*4 & 1*5 \end{pmatrix} \\
        & = \begin{pmatrix} -3 & 12 & 15 \\ 0 & 0 & 0 \\ -1 & 4 & 5 \end{pmatrix} \\
  \end{aligned}
\end{equation}

\begin{equation}
  \begin{aligned}
    CA' & = \begin{pmatrix} 1 & 3 & -1 \\ 2 & 3 & 1 \\ -1 & 1 & 0 \end{pmatrix} * \begin{pmatrix} 3 \\ 0 \\ 1 \end{pmatrix} \\
        & = \begin{pmatrix} 1*3 + 3*0 + -1*1 \\ 2*3 + 3*0 + 1*1 \\ -1*3 + 1*0 + 0*1 \end{pmatrix} \\
        & = \begin{pmatrix} 2 \\ 7 \\ -3 \end{pmatrix} \\
  \end{aligned}
\end{equation}

\begin{equation}
  \begin{aligned}
    BCA' & = \begin{pmatrix} -1 & 4 & 5 \end{pmatrix} * \begin{pmatrix} 2 \\ 7 \\ 3 \end{pmatrix} \\
         & = \begin{pmatrix} -1*2 + 4*7 + 5*3 \end{pmatrix} \\
         & = \begin{pmatrix} 41 \end{pmatrix} \\
  \end{aligned}
\end{equation}  

## d. Find tr(C) 

\begin{equation}
  \begin{aligned}
    tr(C) & = 1 + 3 + 0 \\
          & = 4
  \end{aligned}
\end{equation}  

## e.Find a vector orthogonal to A  

V is orthogonal to A if V.A = 0. Thus, find value for V that satisfy:

\begin{equation}
  \begin{aligned}
    i*3 + j*0 + k*1 & = 0
  \end{aligned}
\end{equation}  

From observation, we can see there is a V(1,1,-3) satisfy the condition.

## f. Find the eigenvalues of A.  

The characteristic polynomial of C is:  

\begin{equation}
  \begin{aligned}
    det(\lambda I - A) & = \begin{vmatrix} \lambda-1 & -3 & 1 \\ -2 & \lambda-3 & -1 \\ 1 & -1 & \lambda  \end{vmatrix} \\
                       & = \lambda^3 - 4*\lambda^2 - 5*\lambda + 9
  \end{aligned}
\end{equation}

The eigenvalues therefore must satisfy the cubic equation:

\begin{equation}
  \begin{aligned}
    \lambda^3 - 4*\lambda^2 - 5*\lambda + 9 & = 0
    \lambda = 1.099115, -1.757702, 4.658587
  \end{aligned}
\end{equation}

Verify:  
```{r}
C <- matrix(c(1,3,-1,2,3,1,-1,1,0),3,3, byrow=TRUE)
ev <- eigen(C)
ev$values
```
## g. Find the eigenvectors of C.  

Using R, we see the corresponding eigenvectors:  
\begin{equation}
  \begin{aligned}
    \begin{pmatrix} 0.62852346 \\ 0.77713615 \\ 0.03190081 \end{pmatrix} \\
    \begin{pmatrix} 0.6713753 \\ -0.4117461 \\ -0.4117461 \end{pmatrix}  \\
    \begin{pmatrix} -0.6035847 \\ 0.2341098 \\ 0.7621536 \end{pmatrix}  \\
  \end{aligned}
\end{equation}

```{r}
ev$vectors
```

# **Question 3**  

## a. Find the GMV solution, no short sale.

Given parameters  

```{r}
# Mean Returns
mean_rStock1 <- .023
mean_rStock2 <- .021
mean_rf <- .008

# Variance of returns
var_rStock1 <- .0072
var_rStock2 <- .0049

# Standard deviation of returns
sd_rStock1 <- sqrt(var_rStock1)
sd_rStock2 <- sqrt(var_rStock2)

# Covariance of Returns
cov_rStock1_rStock2 <- .0023

# Correlation of Returns
cor_rStock2_rStock2 <- cov_rStock1_rStock2 / (sd_rStock1 * sd_rStock2)
```


Asset      | Mean Returns      | Variance           | Pair    | $\sigma_{1,2}$
---        | ---               | ---                | ---     | ---                      
Stock 1    | `r mean_rStock1`  | `r var_rStock1`    | (1,2)   | `r cov_rStock1_rStock2` 
Stock 2    | `r mean_rStock2`  | `r var_rStock2`    |         | 
Risk Free  | `r mean_rf`       |                    |         | 
  
  
Since the investor's objective is to minimize risk, we solve for the global minimum variance combination of the two assets.
Let $x_i$ denotes the weight of the investment in asset i $(i = 1,2,3)$, and assume all money is invested in i, meaning $\sum {x_i} = x_1 + x_2 = 1$.

\begin{equation}
  \begin{aligned}
    \text {The returns of the portfolio is:} \\
    R_{p,x} & = x_1 * r_1 + x_2 * r_2  \\
    \text {The expected returns on the portfolio is:} \\
    \mu_{p,x} & = E[R_{p,x}] \\
              & = x_1 * \mu_1 + x_2 * \mu_2  \\
    \text {The variance of the portfolio returns is:} \\
    \sigma_{p,x}^2 & = var(R_{p,x})  \\
                   & = x_1^2 * \sigma_1^2 + x_2^2 * \sigma_2^2 + 2 * x_1 * x_2 * \sigma_{1,2}
  \end{aligned}
\end{equation}
  
The global minimum variance portfolio $m = (m_1,m_2)$ is the solution of the constrained minimization problem:

\begin{equation}
  \begin{aligned}
    min \sigma_{p,m}^2 & = var(R_{p,m})  \\
                       & = m_1^2 * \sigma_1^2 + m_2^2 * \sigma_2^2 + 2 * m_1 * m_2 * \sigma_{1,2} \\
    \text {s.t. } m_1 + m_2 & = 1 \\
    \text {rewrite: } \\
    min \sigma_{p,m}^2 & = min[m_1^2 * \sigma_1^2 + (1-m_1)^2 * \sigma_2^2 + 2 * m_1 * (1 - m_1) * \sigma_{1,2}] \\
                       & = min[m_1^2 * (\sigma_1^2 + \sigma_2^2 - 2 * \sigma_{1,2}) + m_1 * (2 * \sigma_{1,2} - 2 * \sigma_2^2) + \sigma_2^2]  \\
    \text {plug in: }
    min \sigma_{p,m}^2 & = min[(`r var_rStock1` + `r var_rStock2` - 2 * `r cov_rStock1_rStock2`) * m_1^2 + (2*`r cov_rStock1_rStock2` - 2*`r var_rStock2`) * m_1 + `r var_rStock2`] \\
    min \sigma_{p,m}^2 & = min[(`r var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2`) * m_1^2 + (`r 2*(cov_rStock1_rStock2 - var_rStock2)`) * m_1 + `r var_rStock2`] \\
  \end{aligned}
\end{equation}

Find the critical point:

\begin{equation}
  \begin{aligned}
    \frac{d\sigma_{p,m}^2}{dm} & = 0 \\
    \frac{d(`r var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2` * m_1^2 + (`r 2*(cov_rStock1_rStock2 - var_rStock2)`) * m_1 + `r var_rStock2`)}{dm} & = 0 \\
      .015* m_1 - .0052 & = 0  \\
    m_1 & = .3467 = 34.67\%  \\
    \text {thus, }   \\
    m_2 & = 1 - 0.3467 = .6533 = 65.33\%
  \end{aligned}
\end{equation}

**Recap:**  

Asset      | Weight            
---        | ---                                  
Stock 1    | `34.67`\% 
Stock 2    | `65.33`\%

Graphing the function:  
```{r}
# The Variance function of the portfolio
fVar <- function(m1) var_rStock1 * m1^2 + var_rStock2 * (1 - m1)^2 + 2 * m1 * (1 - m1) * cov_rStock1_rStock2

# Set the weighting
m1 <- .3467
m2 <- .6533

# Plot of the variance function with respect to w1.
w1 <- seq(0, 1, .05)
plot(fVar, w1, xlab = "Weight of Stock 1 Relative to Portfolio", ylab = "Portfolio Variance", main = "Minimum Variance Portfolio"); abline(v = m1, col = "red")
points(m1, fVar(m1), col='green')

# Plot of the efficient frontier, assume no short sale allowed
w1WithoutShort <- seq(0, 1, .005)
fVar <- function(w1) var_rStock1 * w1^2 + var_rStock2 * (1 - w1)^2 + 2 * w1 * (1 - w1) * cov_rStock1_rStock2
r <- function(w1) mean_rStock1*w1 + mean_rStock2*(1-w1)
riskWithoutShort <- sqrt(fVar(w1WithoutShort))
returnWithoutShort <- r(w1WithoutShort)
plot(riskWithoutShort, returnWithoutShort, type='l', main='Global Minimum Variance (without short sale)', xlab = 'Risk', ylab = 'Return', col = 'green')
wp <- (var_rStock2 - cov_rStock1_rStock2) / (var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2)  # Normalizing weight
Rp <- r(wp)
sigma <- sqrt(fVar(wp))
Rf <- mean_rf
Sharpe <- (Rp-Rf)/sigma
X <- seq(0, 1, .01)
Y <- Rf + Sharpe*X
lines(X, Y)
points(sigma, Rp, col='orange')
```

We see indeed the minimum is at $m_1 = `r m1`$

Thus, the optimum weights of each stocks in the portfolio to satisfy the objective of minimum risk is:  

Asset      | Weight            | Risk            | Return            
---        | ---               | ---             | ---                                          
Stock 1    | `r m1*100`\%      |                 |
Stock 2    | `r m2*100`\%      |                 |
Portfolio  | 100\%             | `r sigma`       | `r Rp`

## **b. Construct the efficient frontier. Assume short sale.**  

```{r}
# Plot of the efficient frontier, assume short sale allowed
w1WithShort <- seq(-2, 2, .1)
riskWithShort <- sqrt(fVar(w1WithShort))
returnWithShort <- r(w1WithShort)
plot(riskWithShort, returnWithShort, type='l', main='Global Minimum Variance (with short sale)', xlab = 'Risk', ylab = 'Return', col = 'red')
wp <- (var_rStock2 - cov_rStock1_rStock2) / (var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2)  # Normalizing weight
Rp <- r(wp)
sigma <- sqrt(fVar(wp))
Rf <- mean_rf
Sharpe <- (Rp-Rf)/sigma
X <- seq(0, 1, .01)
Y <- Rf + Sharpe*X
lines(X, Y)
points(sigma, Rp, col='orange')
```

## c. **Graph the efficient frontier of portfolio with and without short sale together.**

```{r}
# Changed input to display less points
w1WithoutShort <- seq(0, 1, .1)
riskWithoutShort <- sqrt(fVar(w1WithoutShort))
returnWithoutShort <- r(w1WithoutShort)
w1WithShort <- seq(-2, 2, .1)
riskWithShort <- sqrt(fVar(w1WithShort))
returnWithShort <- r(w1WithShort)


plot(riskWithShort, returnWithShort, main='Global Minimum Variance', xlab = 'Risk', ylab = 'Return', col = 'red', pch = 17)
points(riskWithoutShort, returnWithoutShort, col = 'green', pch = 17)
```


## d. **Graph the CAL and find the point of tangency.**  

```{r}
w1 <- .3467
Rp <- r(w1)
sigma <- sqrt(fVar(w1))
CAL_slope <-(Rp - mean_rf) / sigma
CAL <- function(x) {mean_rf + CAL_slope * x}
```

The portfolio returns is:  

\begin{equation}
  \begin{aligned}
    R_p & = w_1 * R_1 + w_2 * R_2 \\
        & = `r Rp` \\
  \end{aligned}
\end{equation}

The portfolio returns variance is:  

\begin{equation}
  \begin{aligned}
    \sigma_p & = w_1 * \sigma_1 + w_2 * \sigma_2 + 2 * w_1 * w_2 * \sigma_{1,2} \\
             & = `r sigma` \\
  \end{aligned}
\end{equation}

The slope of the Capital Allocation Line is:  

\begin{equation}
  \begin{aligned}
    Slope_{CAL} & = \frac{R_p - r_f}{\sqrt{\sigma_p}} \\
              & = `r CAL_slope` \\
  \end{aligned}
\end{equation}

**Thus the Capital Allocation Line equation is $CAL = r_f + Slope_{CAL} * x = `r mean_rf` + `r CAL_slope` * x$.**  

**The tangency point is where the optimum weight is, i.e. $(\sigma_p, Rp)$ or $(`r sigma`, `r Rp`)$**


Graphing 
```{r}
# Plot of the efficient frontier, assume no short sale allowed
plot(riskWithShort, returnWithShort, main='Global Minimum Variance', xlab = 'Risk', ylab = 'Return', col = 'red', pch = 17)
points(riskWithoutShort, returnWithoutShort, col = 'green', pch = 17)
plot.function(CAL, add= TRUE, col = 'blue', lwd = 4)
points(sigma, Rp, col='orange', lwd = 4)
```

# **Question 4**  

## a. Find the GMV solution.  

```{r}
library(matlib)

vcov <- matrix(c(.04, .02, .001, .02, .03, .01, .001, .01, .025), 3, 3, byrow=TRUE)
vcovInverse <- inv(vcov)
vcovInverse
```

Formulating the Markowitz portfolio problem:  

\begin{equation}
  \begin{aligned}
     \text {The investor's objective is:} \\
     max \mu_p & = w' * \mu \quad \text{s.t.} \\
     \sigma_p^2 & = w' * (\sum) * w \quad \text{and} \quad w'*I = 1  \\
     \text {where:} \\
     w & = \quad \text{matrix of asset weights in the portfolio} \\
       & = 
        \begin{pmatrix}
          w_1 \\
          w_2 \\
        \end{pmatrix} \\
     w' & = \quad \text{transpose matrix of asset weights in the portfolio} \\
       & = 
        \begin{pmatrix}
          w_1 & w_2 \\
        \end{pmatrix} \\
     \mu & = \quad \text{matrix of mean returns of asset in the portfolio} \\
         & = 
          \begin{pmatrix}
            \mu_1 \\
            \mu_2 \\
          \end{pmatrix} \\
     \sum & = \quad \text{Variance-covariance matrix of asset returns in the the portfolio} \\
          & = 
            \begin{pmatrix}
            \sigma_1^2     & \sigma_{1,2} \\
            \sigma_{1,2}  & \sigma_2^2  \\
          \end{pmatrix} \\
      w'*I & = \sum_{i=1}^{n} w_n \quad \text{or the sum weights of the asset in the portfolio, I is notation for identity matrix} \\
  \end{aligned}
\end{equation}

Let $\mu_{p,0}$ denotes a target expected return level. Formulate the problem:  

\begin{equation}
  \begin{aligned}
     min \sigma_{p,w}^2 & = w' * (\sum) * w  \quad \text{s.t.} \\
     \mu_p & = w' * \mu = \mu_{p,0}, \quad \text{and} \quad w'*I = 1 \\
  \end{aligned}
\end{equation}

To solve this, form the Lagrangian function:

\begin{equation}
  \begin{aligned}
    L(w, \lambda_1, \lambda_2) & = w'*\sum*w + \lambda_1*(w'*\mu - \mu_{p,0}) + \lambda_2*({w'*I - 1}) \\
  \end{aligned}
\end{equation}
  
Because there are two constraints ($w'*\mu = \mu_{p,0}$ and $w'1 = 1$) there are two Langrange multipliers $\lambda_1$ and $\lambda_2$. The first order condition for a minimum are the linear equations:  

\begin{equation}
  \begin{aligned}
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial w} & = \frac{\partial (\sum * w^2)}{\partial w} + \frac{\partial (\lambda_1*(w'*\mu - \mu_{p,0}))}{\partial w} + \frac{\lambda_2*({w'*I - 1})}{\partial w} = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_1} & = 0 \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_2} & = 0 \\
  \end{aligned}
\end{equation}

Simplify, we have:  

\begin{equation}
  \begin{aligned}
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial w} & = 2*\sum*w + \lambda_1*\mu + \lambda_2*I = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_1} & =  w'*\mu - \mu_{p,0} = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_2} & =  w'*I - 1 = 0  \\
  \end{aligned}
\end{equation}

Rewrite in matrix form:  

\begin{equation}
  \begin{aligned}
    \begin{pmatrix}
            2*\sum    & \mu   & I  \\
            \mu'      & 0     & 0  \\
            I'        & 0     & 0  \\
    \end{pmatrix}
    *
    \begin{pmatrix}
            w   \\
            \lambda_1     \\
            \lambda_2       \\
    \end{pmatrix}
    & =
    \begin{pmatrix}
            0   \\
            \mu_{p,0}     \\
            I       \\
    \end{pmatrix}
  \end{aligned}
\end{equation}

or  

\begin{equation}
  \begin{aligned}
    A * z_w & = b_0 \\
    \text{where}\\
    A & = 
    \begin{pmatrix}
            2*\sum    & \mu   & I  \\
            \mu'      & 0     & 0  \\
            I'        & 0     & 0  \\
    \end{pmatrix} \\
    z_w & = 
    \begin{pmatrix}
            w   \\
            \lambda_1     \\
            \lambda_2       \\
    \end{pmatrix} \\
    b_0 & =
    \begin{pmatrix}
            0   \\
            \mu_{p,0}     \\
            I       \\
    \end{pmatrix}
  \end{aligned}
\end{equation}

The solution for $z_w$ is:  

\begin{equation}
  \begin{aligned}
    z_w & = A^{-1} * b_0
  \end{aligned}
\end{equation}


```{r}
topMatrix <- cbind(2*vcovInverse, rep(1, 3))
bottomVector <- c(rep(1, 3), 0)
AmMatrix <- rbind(topMatrix, bottomVector)
bVector <- c(rep(0, 3), 1)
zmMatrix <- solve(AmMatrix)%*%bVector
mVector <- zmMatrix[1:3,1]
mVector
```

Thus, the optimum weights of each stocks in the portfolio to satisfy the objective of minimum risk is:  

Asset      | Weight                   | 
---        | ---                      | 
Stock A    | `r 0.3885350*100`\%      | 
Stock B    | `r 0.3821656*100`\%      |   
Stock C    | `r 0.2292994*100`\%      |   

## b. Find the GMV solution with constraint.  

```{r}
vcovInverse
mean_rStockA <- .0375
mean_rStockB <- .0420
mean_rStockC <- .0300
mean_rf <- .0225
returnsVector <- rbind(mean_rStockA, mean_rStockB, mean_rStockC)  # Establish returns vector
riskPremiumMatrix <- returnsVector - mean_rf
```
We have the z vector:  

\begin{equation}
  \begin{aligned}
    z & = (\sum)^{-1} * (R - Rf) \\
      & = 
      \begin{pmatrix}
        39.70678 & -29.93280 &  10.38485 \\
        -29.93280 & 61.02627 & -23.21319  \\
        10.38485 & -23.21319  & 48.86988  \\
      \end{pmatrix}
    *
      \begin{pmatrix}
            0.0150    \\
            0.0195  \\
            0.0075  \\
      \end{pmatrix}
      & = 
      \begin{pmatrix}
        0.08979841 \\
        0.56692120 \\
        0.06963958 \\
      \end{pmatrix}
  \end{aligned}
\end{equation}

```{r}
z <- vcovInverse %*% riskPremiumMatrix
```
The lambda value is thus:  

\begin{equation}
  \begin{aligned}
    \lambda & = `r sum(z)`\\
  \end{aligned}
\end{equation}

```{r}
lambda <- sum(z)
w1 <- z[1] / lambda
w2 <- z[2] / lambda
w3 <- z[3] / lambda
```
Therefore, the weight of these stocks are:

\begin{equation}
  \begin{aligned}
    w_1 & = \frac{z_i}{\sum_{i=1}^{n} z_i} \\
        & = \frac{`r z[1]`}{`r lambda`} \\
        & = `r w1` \\
    \text{and} \\
    w_2 & = \frac{z_i}{\sum_{i=1}^{n} z_i} \\
        & = \frac{`r z[2]`}{`r lambda`} \\
        & = `r w2` \\
    \text{and} \\
    w_3 & = \frac{z_i}{\sum_{i=1}^{n} z_i} \\
        & = \frac{`r z[3]`}{`r lambda`} \\
        & = `r w3` \\
  \end{aligned}
\end{equation}

**Recap:**  

Asset      | Weight            
---        | ---                                  
Stock A    | `r w1*100`\% 
Stock B    | `r w2*100`\%
Stock C    | `r w3*100`\%
