---
title: "assignment08"
author: "Jeff Nguyen"
date: "23/10/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 07  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**  

The minimum variance solution is:  

\begin{equation}
  \begin{aligned}
    f(w) &= w^2 * \sigma_1^2 + (1 - w)^2 * \sigma_2^2 + 2 * w * (1-w) * \sigma_12  \\
    \text{where}  \\
    w &= \text{weight of stock 1}  \\
    \sigma_1 &= \text{standard deviation of stock 1's returns}  \\
    \sigma_2 &= \text{standard deviation of stock 2's returns}  \\
    \sigma_{12} &= \text{covariance of stock 1 and 2's returns}  \\
  \end{aligned}
\end{equation}

We know the correlation coefficient $r$ between $r_1$ and $r_2$ to be: $r = \frac{\sigma_{12}}{\sigma_1*\sigma2}$.

Rewrite the variance of the portfolio as:  

\begin{equation}
  \begin{aligned}
    f(w) &= w^2*\sigma_1^2 + (1 - w)^2*\sigma_2^2 + 2 * w * (1-w) * r * \sigma_1 * \sigma_2  \\
  \end{aligned}
\end{equation}

**Since minimum variance is the objective, $r=-1$ yields the lowest $f(w)$, ceteris paribus. Thus the answer is b.**  

# **Question 2**  

```{r}
library(quantmod)

# Set start date and end date of data
start_date <- "2018-01-02"
end_date <- "2020-10-23"

# Get data for JPM, FB and the 10 year T-bill (TNX)
getSymbols("JPM", src = "yahoo", from = start_date, to = end_date)
getSymbols("WMT", src = "yahoo", from = start_date, to = end_date)
getSymbols("AAPL", src = "yahoo", from = start_date, to = end_date)

# Get adjusted returns data for 01/2014
rJPM <- diff(log(to.monthly(JPM)$JPM.Adjusted))
rWMT <- diff(log(to.monthly(WMT)$WMT.Adjusted))
rAAPL <- diff(log(to.monthly(AAPL)$AAPL.Adjusted))

# Calculate statistics
mean_rJPM <- mean(rJPM, na.rm = TRUE)
mean_rWMT <- mean(rWMT, na.rm = TRUE)
mean_rAAPL <- mean(rAAPL, na.rm = TRUE)

sd_rJPM <- sd(rJPM, na.rm = TRUE)
sd_rWMT <- sd(rWMT, na.rm = TRUE)
sd_rAAPL <- sd(rAAPL, na.rm = TRUE)

# Generate monthly returns DataFrame, excluding NA
# Note that in this case, excess returns is equal returns
returnsDF <- data.frame(rJPM, rWMT, rAAPL)[-1,]
excess_returnsDF <- returnsDF
vcovMatrix <- matrix(c(cov(returnsDF)), nrow=3, ncol=3, byrow=TRUE)  # Create the variance-covariance matrix of returns of 3 stocks

# Name the columns of vcovMatrix
assetNames <- c("JPM", "WMT", "AAPL")
dimnames(vcovMatrix) <- list(assetNames, assetNames)

# Average returns, excess returns matrix
avg_returnsDF <- matrix(colMeans(returnsDF, na.rm=TRUE))
avg_excess_returnsDF <- matrix(colMeans(excess_returnsDF, na.rm=TRUE))

# Optimum portfolio
zOptimum <- solve(vcovMatrix, avg_excess_returnsDF)  # z-values
wOptimum <- zOptimum / sum(zOptimum)  # Weights
dimnames(wOptimum) <- list(assetNames, "Weights")

# Optimum Portfolio statistics
rOptimum <- t(wOptimum) %*% avg_returnsDF   # Optimum returns
varOptimum <- t(wOptimum) %*% vcovMatrix %*% wOptimum  # Optimum variance
sdOptimum <- varOptimum^.5
stats_portfolioOptimum <- matrix(c(rOptimum, varOptimum, sdOptimum), nrow=3)  # Create a view of the statistics
dimnames(stats_portfolioOptimum) <- list(c("Returns", "Variance", "Stdev"), "Optimum Portfolio")
```

The variance-covariance matrix is:  
```{r}
vcovMatrix
```

The optimum weights are:
```{r}
wOptimum
```

The returns and risk of the optimum portfolio are:
```{r}
stats_portfolioOptimum
```

# **Question 3**  

\begin{equation}
  \begin{aligned}
    X & = \begin{pmatrix} 2 & 6 & 1 \end{pmatrix} \\
    Z & = \begin{pmatrix} 5 & 3 & 2 \\ 3 & 6 & 1 \\ 2 & 1 & 9 \end{pmatrix} \\
  \end{aligned}
\end{equation}

## a. Show that Z is a symmetric matrix  

Z is symmetrical iff. $Z = Z'$ 

\begin{equation}
  \begin{aligned}
    Z' & = \begin{pmatrix} 5 & 3 & 2 \\ 3 & 6 & 1 \\ 2 & 1 & 9 \end{pmatrix} \\
  \end{aligned}
\end{equation}

**We can see $Z = Z'$. Thus Z is symmetrical.**  

## b. Find inverse of matrix Z.  
```{r}
library(matlib)

zMatrix <- matrix(c(5, 3, 2, 3, 6, 1, 2, 1, 9), 3, 3, byrow=TRUE)
z_invMatrix <- inv(zMatrix)
dimnames(z_invMatrix) <- list(c('','',''), c('','',''))
z_invMatrix

det(zMatrix)
det(z_invMatrix)
```
Thus:
\begin{equation}
  \begin{aligned}
    Z^{-1} & = \begin{pmatrix} 0.30813953 & -0.14534884 & -0.05232558 \\ 
                              -0.14534884 & 0.23837209 & 0.00581395 \\ 
                              -0.05232558 & 0.00581395  & 0.12209302 \end{pmatrix} \\
  \end{aligned}
\end{equation}

## c. Find determinants of Z and Z inverse. Show that they are equal to each other.  

\begin{equation}
  \begin{aligned}
    det(Z) & = 5\begin{vmatrix} 6 & 1 \\ 1 & 9 \end{vmatrix} - 
               3\begin{vmatrix} 3 & 1 \\ 2 & 9 \end{vmatrix} + 
               2\begin{vmatrix} 3 & 6 \\ 2 & 1 \end{vmatrix} \\
           & = 5(6*9 - 1*1) - 3(3*9 - 2*1) + 2(3*1-6*2) \\
           & = `r 5*(6*9 - 1*1) - 3*(3*9 - 2*1) + 2*(3*1-6*2)` \\
    \text{additionally,} \\
    det(Z^{-1}) & = 0.30813953\begin{vmatrix} 0.23837209 & 0.00581395 \\ 0.00581395 & 0.12209302 \end{vmatrix} + 
                    0.14534884\begin{vmatrix} -0.14534884 & 0.00581395 \\  -0.05232558 & 0.12209302 \end{vmatrix} - 
                    0.05232558\begin{vmatrix} -0.14534884 & 0.23837209 \\ -0.05232558 & 0.00581395 \end{vmatrix} \\
           & = 0.30813953*(0.23837209*0.12209302 - 0.00581395*0.00581395) + 
               0.14534884*(-0.14534884*0.12209302 - -0.05232558*0.00581395) - 
               0.05232558*(-0.14534884*0.00581395--0.05232558*0.23837209) \\
           & = `r 0.30813953*(0.23837209*0.12209302 - 0.00581395*0.00581395) + 0.14534884*(-0.14534884*0.12209302 - -0.05232558*0.00581395) -                        0.05232558*(-0.14534884*0.00581395--0.05232558*0.23837209)`
  \end{aligned}
\end{equation}

They are not equal. Not sure what you mean?

## d. Find X’ZX.  
Non comformable multiplication. You are asking to do this multiplication (3x1)*(3x3)*(1*3) which is mathematically impossible.  

## e. Find $Z^{-1}X'$.  
\begin{equation}
  \begin{aligned}
    Z^{-1}X & = \begin{pmatrix} 0.30813953 & -0.14534884 & -0.05232558 \\ 
                               -0.14534884 & 0.23837209 & 0.00581395 \\ 
                               -0.05232558 & 0.00581395  & 0.12209302 \end{pmatrix} * \begin{pmatrix} 2 \\ 6 \\ 1 \end{pmatrix} \\
            & = \begin{pmatrix} 2*0.30813953 + 6*-0.14534884 + 1*-0.05232558 \\
                                2*-0.14534884 + 6*0.23837209 + 1*0.00581395 \\ 
                                2*-0.05232558 + 6*0.00581395 + 1*0.12209302 \end{pmatrix} \\
            & = \begin{pmatrix} `r 2*0.30813953 + 6*-0.14534884 + 1*-0.05232558` \\
                                `r 2*-0.14534884 + 6*0.23837209 + 1*0.00581395` \\ 
                                `r 2*-0.05232558 + 6*0.00581395 + 1*0.12209302` \end{pmatrix} \\               
  \end{aligned}
\end{equation}

## f. Find eigenvalues and eigenvectors of Z using R or Excel.
Eigenvalues using R:  
```{r}
ev <- eigen(zMatrix)
ev$values
```

Eigenvectos:
```{r}
ev$vectors
```

Using R, we see the corresponding eigenvectors:  
\begin{equation}
  \begin{aligned}
    \begin{pmatrix} -0.4840709 \\ -0.4503380 \\ -0.7502473 \end{pmatrix} \\
    \begin{pmatrix} -0.3863934 \\ -0.6592664 \\ 0.6450333 \end{pmatrix}  \\
    \begin{pmatrix} 0.7850958 \\ -0.6021325 \\ -0.1451241 \end{pmatrix}  \\
  \end{aligned}
\end{equation}

# **Question 4**  

Given parameters  

```{r}
# Mean Returns
mean_rAsset1 <- .10
mean_rAsset2 <- .12
mean_rAsset3 <- .07
mean_rf <- .05

# Variance of returns
var_rAsset1 <- .025
var_rAsset2 <- .030
var_rAsset3 <- .004

# Standard deviation of returns
sd_rAsset1 <- sqrt(var_rAsset1)
sd_rAsset2 <- sqrt(var_rAsset2)
sd_rAsset3 <- sqrt(var_rAsset3)

# Covariance of Returns
cov_rAsset1_rAsset2 <- .015
cov_rAsset1_rAsset3 <- -.002
cov_rAsset2_rAsset3 <- .005
```


Asset      | Mean Returns      | Variance           | Pair    | Covariance
---        | ---               | ---                | ---     | ---                      
Asset 1    | `r mean_rAsset1`  | `r var_rAsset1`    | (1,2)   | `r cov_rAsset1_rAsset2` 
Asset 2    | `r mean_rAsset2`  | `r var_rAsset2`    | (2,3)   | `r cov_rAsset2_rAsset3` 
Asset 3    | `r mean_rAsset3`  | `r var_rAsset3`    | (3,1)   | `r cov_rAsset1_rAsset3` 
Risk Free  | `r mean_rf`       |                    |         | 
  
  
Since the investor's objective is to minimize risk, we solve for the global minimum variance combination of the two assets.  
Let $x_i$ denotes the weight of the investment in asset i $(i = 1,2,3)$, and assume all money is invested in i, meaning $\sum {x_i} = x_1 + x_2 + x_3 = 1$.

\begin{equation}
  \begin{aligned}
    \text {The returns of the portfolio is:} \\
    R_{p,x} & = x_1 * r_1 + x_2 * r_2 + x_3 * r_3  \\
    \text {The expected returns on the portfolio is:} \\
    \mu_{p,x} & = E[R_{p,x}] \\
              & = x_1 * \mu_1 + x_2 * \mu_2 + x_3 * \mu_3 \\
    \text {The variance of the portfolio returns is:} \\
    \sigma_{p,x}^2 & = var(R_{p,x})  \\
                   & = x_1^2 * \sigma_1^2 + x_2^2 * \sigma_2^2 + x_3^2 * \sigma_3^2 + 2 * x_1 * x_2 * \sigma_{1,2} + 
                   2 * x_2 * x_3 * \sigma_{2,3} + 2 * x_3 * x_1 * \sigma_{3,1}
  \end{aligned}
\end{equation}

Rewrite using matrix notation for simplicity:  

Formulating the Markowitz portfolio problem:  

\begin{equation}
  \begin{aligned}
     \text {The investor's objective is:} \\
     max \mu_p & = w' * \mu \quad \text{s.t.} \\
     \sigma_p^2 & = w' * (\sum) * w \quad \text{and} \quad w'*I = 1  \\
     \text {where:} \\
     w & = \quad \text{matrix of asset weights in the portfolio} \\
       & = 
        \begin{pmatrix}
          w_1 \\
          w_2 \\
          w_3 \\
        \end{pmatrix} \\
     w' & = \quad \text{transpose matrix of asset weights in the portfolio} \\
       & = 
        \begin{pmatrix}
          w_1 & w_2 & w_3  \\
        \end{pmatrix} \\
     \mu & = \quad \text{matrix of mean returns of asset in the portfolio} \\
         & = 
          \begin{pmatrix}
            \mu_1 \\
            \mu_2 \\
            \mu_3 \\
          \end{pmatrix} \\
     \sum & = \quad \text{Variance-covariance matrix of asset returns in the the portfolio} \\
          & = 
            \begin{pmatrix}
            \sigma_1^2     & \sigma_{1,2}  & \sigma_{3,1} \\
            \sigma_{1,2}  & \sigma_2^2  &  \sigma_{2,3}  \\
            \sigma_{3,1}  &  \sigma_{2,3}  & \sigma_{3}^2  \\
          \end{pmatrix} \\
      w'*I & = \sum_{i=1}^{n} w_n \quad \text{or the sum weights of the asset in the portfolio, I is notation for identity matrix} \\
  \end{aligned}
\end{equation}

Let $\mu_{p,0}$ denotes a target expected return level. Formulate the problem:  

\begin{equation}
  \begin{aligned}
     min \sigma_{p,w}^2 & = w' * (\sum) * w  \quad \text{s.t.} \\
     \mu_p & = w' * \mu = \mu_{p,0}, \quad \text{and} \quad w'*I = 1 \\
  \end{aligned}
\end{equation}

To solve this, form the Lagrangian function:

\begin{equation}
  \begin{aligned}
    L(w, \lambda_1, \lambda_2) & = w'*\sum*w + \lambda_1*(w'*\mu - \mu_{p,0}) + \lambda_2*({w'*I - 1}) \\
  \end{aligned}
\end{equation}
  
Because there are two constraints ($w'*\mu = \mu_{p,0}$ and $w'1 = 1$) there are two Langrange multipliers $\lambda_1$ and $\lambda_2$. The first order condition for a minimum are the linear equations:  

\begin{equation}
  \begin{aligned}
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial w} & = \frac{\partial (\sum * w^2)}{\partial w} + \frac{\partial (\lambda_1*(w'*\mu - \mu_{p,0}))}{\partial w} + \frac{\lambda_2*({w'*I - 1})}{\partial w} = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_1} & = 0 \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_2} & = 0 \\
  \end{aligned}
\end{equation}

Simplify, we have:  

\begin{equation}
  \begin{aligned}
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial w} & = 2*\sum*w + \lambda_1*\mu + \lambda_2*I = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_1} & =  w'*\mu - \mu_{p,0} = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_2} & =  w'*I - 1 = 0  \\
  \end{aligned}
\end{equation}

Rewrite in matrix form:  

\begin{equation}
  \begin{aligned}
    \begin{pmatrix}
            2*\sum    & \mu   & I  \\
            \mu'      & 0     & 0  \\
            I'        & 0     & 0  \\
    \end{pmatrix}
    *
    \begin{pmatrix}
            w   \\
            \lambda_1     \\
            \lambda_2       \\
    \end{pmatrix}
    & =
    \begin{pmatrix}
            0   \\
            \mu_{p,0}     \\
            I       \\
    \end{pmatrix}
  \end{aligned}
\end{equation}

or  

\begin{equation}
  \begin{aligned}
    A * z_w & = b_0 \\
    \text{where}\\
    A & = 
    \begin{pmatrix}
            2*\sum    & \mu   & I  \\
            \mu'      & 0     & 0  \\
            I'        & 0     & 0  \\
    \end{pmatrix} \\
    z_w & = 
    \begin{pmatrix}
            w   \\
            \lambda_1     \\
            \lambda_2       \\
    \end{pmatrix} \\
    b_0 & =
    \begin{pmatrix}
            0   \\
            \mu_{p,0}     \\
            I       \\
    \end{pmatrix}
  \end{aligned}
\end{equation}

The solution for $z_w$ is:  

\begin{equation}
  \begin{aligned}
    z_w & = A^{-1} * b_0
  \end{aligned}
\end{equation}  

Data:  
```{r}
library(matlib)

assetNames <- c("Asset 1", "Asset 2", "Asset 3")
returnsVector <- c(mean_rAsset1, mean_rAsset2, mean_rAsset3)
names(returnsVector) <- assetNames

vcovMatrix <- matrix(c(var_rAsset1, cov_rAsset1_rAsset2, cov_rAsset1_rAsset3,
                       cov_rAsset1_rAsset2, var_rAsset2, cov_rAsset2_rAsset3,
                       cov_rAsset1_rAsset3, cov_rAsset2_rAsset3, var_rAsset3),
                     nrow=3, ncol=3)
dimnames(vcovMatrix) = list(assetNames, assetNames)

vcovInverse <- inv(vcovMatrix)

vcovMatrix
vcovInverse
```

Computations:
```{r}
topMatrix <- cbind(2*vcovInverse, rep(1, 3))
bottomVector <- c(rep(1, 3), 0)
AmMatrix <- rbind(topMatrix, bottomVector)
bVector <- c(rep(0, 3), 1)
zmMatrix <- solve(AmMatrix)%*%bVector
mVector <- zmMatrix[1:3,1]
mVector
```

## a. Find the weights of each asset in the portfolio.  

Thus, the optimum weights of each stocks in the portfolio to satisfy the objective of minimum risk is:  

Asset      | Weight                    | 
---        | ---                       | 
Asset A    | `r 0.40000000*100`\%      | 
Asset B    | `r 0.52631579*100`\%      |   
Asset C    | `r 0.07368421*100`\%      |   

## b. Find the portfolio’s risk and return at the optimum solution.  

The expected returns on this portfolio is:  

```{r}
mean_rPortfolio <- as.numeric(crossprod(mVector, returnsVector))
mean_rPortfolio
```

The risk or standard deviation of this portfolio is:  

```{r}
var_rPortfolio <- as.numeric(t(mVector) %*% vcovMatrix %*% mVector)
sd_rPortfolio <- sqrt(var_rPortfolio)
sd_rPortfolio
```

## c. Write the dual to the problem.  
As above, again:  

Let $\mu_{p,0}$ denotes a target expected return level. Formulate the problem:  

\begin{equation}
  \begin{aligned}
     min \sigma_{p,w}^2 & = w' * (\sum) * w  \quad \text{s.t.} \\
     \mu_p & = w' * \mu = \mu_{p,0}, \quad \text{and} \quad w'*I = 1 \\
  \end{aligned}
\end{equation}

To solve this, form the Lagrangian function:

\begin{equation}
  \begin{aligned}
    L(w, \lambda_1, \lambda_2) & = w'*\sum*w + \lambda_1*(w'*\mu - \mu_{p,0}) + \lambda_2*({w'*I - 1}) \\
  \end{aligned}
\end{equation}
