---
title: "assignment08"
author: "Jeff Nguyen"
date: "23/10/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 07  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**  

The minimum variance solution is:  

\begin{equation}
  \begin{aligned}
    f(w) &= w^2 * \sigma_1^2 + (1 - w)^2 * \sigma_2^2 + 2 * w * (1-w) * \sigma_12  \\
    \text{where}  \\
    w &= \text{weight of stock 1}  \\
    \sigma_1 &= \text{standard deviation of stock 1's returns}  \\
    \sigma_2 &= \text{standard deviation of stock 2's returns}  \\
    \sigma_{12} &= \text{covariance of stock 1 and 2's returns}  \\
  \end{aligned}
\end{equation}

We know the correlation coefficient $r$ between $r_1$ and $r_2$ to be: $r = \frac{\sigma_{12}}{\sigma_1*\sigma2}$.

Rewrite the variance of the portfolio as:  

\begin{equation}
  \begin{aligned}
    f(w) &= w^2*\sigma_1^2 + (1 - w)^2*\sigma_2^2 + 2 * w * (1-w) * r * \sigma_1 * \sigma_2  \\
  \end{aligned}
\end{equation}

**Since minimum variance is the objective, $r=-1$ yields the lowest $f(w)$, ceteris paribus. Thus the answer is b.**  

# **Question 2**  

```{r}
library(quantmod)

# Set start date and end date of data
start_date <- "2018-01-02"
end_date <- "2020-10-23"

# Get data for JPM, FB and the 10 year T-bill (TNX)
getSymbols("JPM", src = "yahoo", from = start_date, to = end_date)
getSymbols("WMT", src = "yahoo", from = start_date, to = end_date)
getSymbols("AAPL", src = "yahoo", from = start_date, to = end_date)

# Get adjusted returns data for 01/2014
rJPM <- diff(log(to.monthly(JPM)$JPM.Adjusted))
rWMT <- diff(log(to.monthly(WMT)$WMT.Adjusted))
rAAPL <- diff(log(to.monthly(AAPL)$AAPL.Adjusted))

# Calculate statistics
mean_rJPM <- mean(rJPM, na.rm = TRUE)
mean_rWMT <- mean(rWMT, na.rm = TRUE)
mean_rAAPL <- mean(rAAPL, na.rm = TRUE)

sd_rJPM <- sd(rJPM, na.rm = TRUE)
sd_rWMT <- sd(rWMT, na.rm = TRUE)
sd_rAAPL <- sd(rAAPL, na.rm = TRUE)

# Generate monthly returns DataFrame, excluding NA
# Note that in this case, excess returns is equal returns
returnsDF <- data.frame(rJPM, rWMT, rAAPL)[-1,]
excess_returnsDF <- returnsDF
vcovMatrix <- matrix(c(cov(returnsDF)), nrow=3, ncol=3, byrow=TRUE)  # Create the variance-covariance matrix of returns of 3 stocks

# Name the columns of vcovMatrix
assetNames <- c("JPM", "WMT", "AAPL")
dimnames(vcovMatrix) <- list(assetNames, assetNames)

# Average returns, excess returns matrix
avg_returnsDF <- matrix(colMeans(returnsDF, na.rm=TRUE))
avg_excess_returnsDF <- matrix(colMeans(excess_returnsDF, na.rm=TRUE))

# Optimum portfolio
zOptimum <- solve(vcovMatrix, avg_excess_returnsDF)  # z-values
wOptimum <- zOptimum / sum(zOptimum)  # Weights
dimnames(wOptimum) <- list(assetNames, "Weights")

# Optimum Portfolio statistics
rOptimum <- t(wOptimum) %*% avg_returnsDF   # Optimum returns
varOptimum <- t(wOptimum) %*% vcovMatrix %*% wOptimum  # Optimum variance
sdOptimum <- varOptimum^.5
stats_portfolioOptimum <- matrix(c(rOptimum, varOptimum, sdOptimum), nrow=3)  # Create a view of the statistics
dimnames(stats_portfolioOptimum) <- list(c("Returns", "Variance", "Stdev"), "Optimum Portfolio")

```

The variance-covariance matrix is:  
```{r}
vcovMatrix
```

The optimum weights are:
```{r}
wOptimum
```

The returns and risk of the optimum portfolio are:
```{r}
stats_portfolioOptimum
```

# **Question 3**  

\begin{equation}
  \begin{aligned}
    X & = \begin{pmatrix} 2 & 6 & 1 \end{pmatrix} \\
    Z & = \begin{pmatrix} 5 & 3 & 2 \\ 3 & 6 & 1 \\ 2 & 1 & 9 \end{pmatrix} \\
  \end{aligned}
\end{equation}

## a. Show that Z is a symmetric matrix  

Z is symmetrical iff. $Z = Z'$ 

\begin{equation}
  \begin{aligned}
    Z' & = \begin{pmatrix} 5 & 3 & 2 \\ 3 & 6 & 1 \\ 2 & 1 & 9 \end{pmatrix} \\
  \end{aligned}
\end{equation}

We can see $Z = Z'$. Thus Z is symmetrical.  

## b. Show that Z is a symmetric matrix  
