---
title: "assignment06"
author: "Jeff Nguyen"
date: "09/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 06  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**  

\begin{equation}
  \begin{aligned}
    Q = 150*N - .025*N^2
  \end{aligned}
\end{equation}

## a. Finding optimum N and Q. No constraint.  
Objective is to maximize Q given N. Thus we find the max of Q. 
Q(N) is a polynomial function, and thus, continuous everywhere.  

**Graph of the function:**
```{r}
Q <- function(N) 150*N - .025*N^2
curve(Q, 0, 6000)
root <- polyroot(c(150, -.05))
N_max <- Re(root)[abs(Im(root)) < 1e-6]
Q_max <- Q(N_max)
points(N_max, Q(N_max), col='red')
```
We know:  
\begin{equation}
  \begin{aligned}
    Q'(N_0) & = 0 \\
    \frac{dQ}{dN} & = 0 \\
    150 - .05*N_{max} & = 0 \\
    N_{max} & = `r N_max`
  \end{aligned}
\end{equation}

**Per graph, we can confirm Q(N) optimum is at $N_{max} = `r N_max`$ and $Q_{max} = `r Q_max`$.**  

## b,c,d. Finding optimum N and Q. Constraint $N \leqslant 250$.  

The problem is to maximize the output $Q$ subject to the constraint that the business can not have more than 250 units of labor $N$.  
To solve the constrained optimizing problem, we form the Lagrangian function.  

**The Lagrangian function is formed by augmenting the constraint together with the Lagrange multiplier to the objective function.** 

\begin{equation}
  \begin{aligned}
    L = 150*N - .025*N^2 + \lambda*(250 - N)
  \end{aligned}
\end{equation}

If the constraint is satisfied, no matter what value has, the second term in the right side of the Lagrangian equation will vanish and we arrive at $L = 150*N - .025*N^2$, that is maximizing $L$ with respect to $N$ is the same as maximizing $Q$, and achieving the objective. Therefore, the trick in solving a constrained optimizing problem is to incorporate the constraint into the problem and ensure that the constraint is satisfied with equality. This is done by treating $\lambda$ as an additional variable and assuming $L$ is a function of $N$ and $\lambda$. That is:

\begin{equation}
  \begin{aligned}
    L(N, \lambda) = 150*N - .025*N^2 + \lambda*(250 - N)
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $N$:
\begin{equation}
  \begin{aligned}
    L'(N_0) & = 0 \\
    \frac{dL}{dN} & = 0 \\
    150 - .05*N_0 - \lambda & = 0 \quad \text{(1)} \\
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $\lambda$:
\begin{equation}
  \begin{aligned}
    L'(\lambda) & = 0 \\
    \frac{dL}{d\lambda} & = 0 \\
    250 - N_0 & = 0 \\ 
    N_0 & = 250 \quad \text{(2)}
  \end{aligned}
\end{equation}

Substitute (2) to (1), we have $\lambda = 137.5 > 0$.   
The Lagrangian multiplier $\lambda$ is positive, implying the constraint is binding.  
```{r}
N_0 <- 250
Q_0 <- Q(N_0)
plot(Q, 0, 3500, xlab = 'N', ylab = 'Q')
abline(v = 250, col = 'red')
points(N_0, Q(N_0), col = 'green')
points(N_max, Q(N_max), col='red')
```

Therefore, the optimum solution to this problem is $N_0 = `r N_0`$ and $Q_0 = `r Q_0`$.  

# **Question 2**  

\begin{equation}
  \begin{aligned}
    Y = X^3 -11*X^2 + 14*X + 80
  \end{aligned}
\end{equation}

```{r}
f <- function(x) x^3 -11*x^2 + 14*x + 80
f_1prime <- function(x) 3*x^2 - 22*x + 14
root <- polyroot(c(14, -22, 3))
x_1prime <- Re(root)[abs(Im(root)) < 1e-6]
x_1prime
```

This is a polynomial function, thus, it is continuous everywhere.  
We know:  

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    3*x^2 - 22*x + 14 & = 0 \\
    x_0 & = `r x_1prime`
  \end{aligned}
\end{equation}


```{r}
x_1prime1 <- 0.7039352
x_1prime2 <- 6.6293981
```
Testing min, max with $x_0 = `r x_1prime1`$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(`r x_1prime1 - 1`)                              \qquad  &   f'(x_0 + 1) & = f'(`r x_1prime1 + 1`) \\
    f'(x_0 - 1) & = 3*(`r x_1prime1 - 1`)^2 - 22*(`r x_1prime1 - 1`) + 14      &   f'(x_0 + 1) & = 3*(`r x_1prime1 + 1`)^2 - 22*(`r x_1prime1 + 1`) + 14 \\
    f'(x_0 - 1) & = `r f_1prime(x_1prime1 - 1)` > 0                            &   f'(x_0 + 1) & = `r f_1prime(x_1prime1 + 1)` < 0
  \end{aligned}
\end{equation}

Finding $f(`r x_1prime1`)$:
\begin{equation} 
  \begin{aligned}
    f(`r x_1prime1`) & = `r x_1prime1`^3 -11*`r x_1prime1`^2 + 14*`r x_1prime1` + 80 \\
    f(`r x_1prime1`) & = `r f(x_1prime1)`
  \end{aligned}
\end{equation}

**From the above, we know the function has a local maxima at $(`r x_1prime1`, `r f(x_1prime1)`)$**  

Testing min, max with $x_0 = `r x_1prime2`$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(`r x_1prime2 - 1`)                              \qquad  &   f'(x_0 + 1) & = f'(`r x_1prime2 + 1`) \\
    f'(x_0 - 1) & = 3*(`r x_1prime2 - 1`)^2 - 22*(`r x_1prime2 - 1`) + 14      &   f'(x_0 + 1) & = 3*(`r x_1prime2 + 1`)^2 - 22*(`r x_1prime2 + 1`) + 14 \\
    f'(x_0 - 1) & = `r f_1prime(x_1prime2 - 1)` < 0                            &   f'(x_0 + 1) & = `r f_1prime(x_1prime2 + 1)` > 0
  \end{aligned}
\end{equation}

Finding $f(`r x_1prime2`)$:
\begin{equation} 
  \begin{aligned}
    f(`r x_1prime2`) & = `r x_1prime2`^3 -11*`r x_1prime2`^2 + 14*`r x_1prime2` + 80 \\
    f(`r x_1prime2`) & = `r f(x_1prime2)`
  \end{aligned}
\end{equation}

**From the above, we know the function has a local minima at $(`r x_1prime2`, `r f(x_1prime2)`)$**

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    6x - 22 & = 0 \\
    x & = \frac{11}{3} \approx 3.666667
  \end{aligned}
\end{equation}

```{r}
x_2prime1 <- 11/3
f_2prime <- function(x) 6*x - 22
```

Testing the potential inflection point at $x_0 = `r x_2prime1`$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(`r x_2prime1 - 1`)   \qquad      &   f''(x_0 + 1) & = f''(`r x_2prime1 + 1`) \\
    f''(x_0 - 1) & = 6*`r x_2prime1 - 1` - 22             &   f''(x_0 + 1) & = 6*`r x_2prime1 + 1` - 22 \\
    f''(x_0 - 1) & = `r f_2prime(x_2prime1 - 1)` < 0      &   f''(x_0 + 1) & = `r f_2prime(x_2prime1 + 1)` > 0
  \end{aligned}
\end{equation}

Finding $f(`r x_2prime1`)$:
\begin{equation} 
  \begin{aligned}
    f(`r x_2prime1`) & = `r x_2prime1`^3 -11*`r x_2prime1`^2 + 14*`r x_2prime1` + 80 \\
    f(`r x_2prime1`) & = `r f(x_2prime1)`
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(`r x_2prime1`,`r f(x_2prime1) `)$, 
thus $(`r x_2prime1`,`r f(x_2prime1) `)$ is an inflection point.**

```{r}
x_1prime1 <- 0.7039352
x_1prime2 <- 6.6293981
x_2prime1 <- 11/3
curve(f, -5, 10)
points(x_1prime1, f(x_1prime1), col = 'red')
points(x_1prime2, f(x_1prime2), col = 'green')
points(x_2prime1, f(x_2prime1), col = 'blue')
```

# **Question 3**  

\begin{equation}
  \begin{aligned}
    Q = 100*N + 10*N^2 - N^3
  \end{aligned}
\end{equation}


**Graph of the function:**
```{r}
Q <- function(N) 100*N + 10*N^2 - N^3
curve(Q, 0, 20)
root <- polyroot(c(100, 20, -3)) 
N_max <- Re(root)[abs(Im(root)) < 1e-6]
N_max <- N_max[which(N_max>0)]
Q_max <- Q(N_max)
points(N_max, Q(N_max), col='red')
```  

Considering the solution with no constraint:

We know:  
\begin{equation}
  \begin{aligned}
    Q'(N_max) & = 0 \\
    \frac{dQ}{dN} & = 0 \\
    100 + 20 * N_{max} - 3*N^2 & = 0 \\
    N_{max} & = `r N_max`
  \end{aligned}
\end{equation}

**Per graph, we can confirm Q(N) optimum is at $N_{max} = `r N_max`$ and $Q_{max} = `r Q(N_max)`$.**  

## a,b. Finding optimum N and Q. Constraint $N \leqslant 15$.  

The problem is to maximize the output $Q$ subject to the constraint that the business can not have more than 15 units of labor $N$.  
To solve the constrained optimizing problem, we form the Lagrangian function.  

**The Lagrangian function is formed by augmenting the constraint together with the Lagrange multiplier to the objective function.** 

\begin{equation}
  \begin{aligned}
    L = 100*N + 10*N^2 - N^3 + \lambda*(15 - N)
  \end{aligned}
\end{equation}

If the constraint is satisfied, no matter what value has, the second term in the right side of the Lagrangian equation will vanish and we arrive at $L = 100*N + 10*N^2 - N^3$, that is maximizing $L$ with respect to $N$ is the same as maximizing $Q$, and achieving the objective. Therefore, the trick in solving a constrained optimizing problem is to incorporate the constraint into the problem and ensure that the constraint is satisfied with equality. This is done by treating $\lambda$ as an additional variable and assuming $L$ is a function of $N$ and $\lambda$. That is:

\begin{equation}
  \begin{aligned}
    L(N, \lambda) = 100*N + 10*N^2 - N^3 + \lambda*(15 - N)
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $N$:
\begin{equation}
  \begin{aligned}
    L'(N_0) & = 0 \\
    \frac{dL}{dN} & = 0 \\
    100- \lambda + 20*N - 3*N^2 & = 0 \quad \text{(1)} \\
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $\lambda$:
\begin{equation}
  \begin{aligned}
    L'(\lambda) & = 0 \\
    \frac{dL}{d\lambda} & = 0 \\
    15 - N_0 & = 0 \\ 
    N_0 & = 15 \quad \text{(2)}
  \end{aligned}
\end{equation}

Substitute (2) to (1), we have $\lambda = -275 < 0$.   
The Lagrangian multiplier $\lambda$ is negative, implying the constraint is non-binding.  
**Therefore, the constraint does not affect the optimum solution, which is still $N_{max} = `r N_max`$ and $Q_{max} = `r Q(N_max)`$.**
```{r}
N_0 <- 15
lambda <- 100 + 20*N_0 - 3*N_0^2 
Q_0 <- Q(N_0)
plot(Q, 0, 20, xlab = 'N', ylab = 'Q')
abline(v = N_0, col = 'green')
points(N_0, Q(N_0), col = 'green')
points(N_max, Q(N_max), col='red')
```  

## c,d. Finding optimum N and Q. Constraint $N \leqslant 8$.  

The problem is to maximize the output $Q$ subject to the constraint that the business can not have more than 8 units of labor $N$.  
To solve the constrained optimizing problem, we form the Lagrangian function.  

**The Lagrangian function is formed by augmenting the constraint together with the Lagrange multiplier to the objective function.** 

\begin{equation}
  \begin{aligned}
    L = 100*N + 10*N^2 - N^3 + \lambda*(8 - N)
  \end{aligned}
\end{equation}

If the constraint is satisfied, no matter what value has, the second term in the right side of the Lagrangian equation will vanish and we arrive at $L = 100*N + 10*N^2 - N^3$, that is maximizing $L$ with respect to $N$ is the same as maximizing $Q$, and achieving the objective. Therefore, the trick in solving a constrained optimizing problem is to incorporate the constraint into the problem and ensure that the constraint is satisfied with equality. This is done by treating $\lambda$ as an additional variable and assuming $L$ is a function of $N$ and $\lambda$. That is:

\begin{equation}
  \begin{aligned}
    L(N, \lambda) = 100*N + 10*N^2 - N^3 + \lambda*(8 - N)
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $N$:
\begin{equation}
  \begin{aligned}
    L'(N_0) & = 0 \\
    \frac{dL}{dN} & = 0 \\
    100- \lambda + 20*N - 3*N^2 & = 0 \quad \text{(1)} \\
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $\lambda$:
\begin{equation}
  \begin{aligned}
    L'(\lambda) & = 0 \\
    \frac{dL}{d\lambda} & = 0 \\
    8 - N_0 & = 0 \\ 
    N_0 & = 8 \quad \text{(2)}
  \end{aligned}
\end{equation}

Substitute (2) to (1), we have $\lambda = 68 > 0$.   
The Lagrangian multiplier $\lambda$ is positive, implying the constraint is binding.  
```{r}
N_0 <- 8
lambda <- 100 + 20*N_0 - 3*N_0^2 
Q_0 <- Q(N_0)
plot(Q, 0, 20, xlab = 'N', ylab = 'Q')
abline(v = N_0, col = 'green')
points(N_0, Q(N_0), col = 'green')
points(N_max, Q(N_max), col='red')
```

**Therefore, the constraint does affect the optimum solution, which is now $N_0 = `r N_0`$ and $Q_0 = `r Q(N_0)`$.**  

# **Question 4**  

## a. Find the GMV solution, no short sale.

Given parameters  

```{r}
# Mean Returns
mean_rStock1 <- .13
mean_rStock2 <- .21
mean_rf <- .08

# Variance of returns
var_rStock1 <- .075
var_rStock2 <- .052

# Standard deviation of returns
sd_rStock1 <- sqrt(var_rStock1)
sd_rStock2 <- sqrt(var_rStock2)

# Covariance of Returns
cov_rStock1_rStock2 <- .018

# Correlation of Returns
cor_rStock2_rStock2 <- cov_rStock1_rStock2 / (sd_rStock1 * sd_rStock2)
```


Asset      | Mean Returns      | Variance           | Pair    | $\sigma_{1,2}$
---        | ---               | ---                | ---     | ---                      
Stock 1    | `r mean_rStock1`  | `r var_rStock1`    | (1,2)   | `r cov_rStock1_rStock2` 
Stock 2    | `r mean_rStock2`  | `r var_rStock2`    |         | 
Risk Free  | `r mean_rf`       |                    |         | 
  
  
Since the investor's objective is to minimize risk, we solve for the global minimum variance combination of the two assets.
Let $x_i$ denotes the weight of the investment in asset i $(i = 1,2)$, and assume all money is invested in i, meaning $\sum {x_i} = x_1 + x_2 = 1$.

\begin{equation}
  \begin{aligned}
    \text {The returns of the portfolio is:} \\
    R_{p,x} & = x_1 * r_1 + x_2 * r_2 \\
    \text {The expected returns on the portfolio is:} \\
    \mu_{p,x} & = E[R_{p,x}] \\
              & = x_1 * \mu_1 + x_2 * \mu_2  \\
    \text {The variance of the portfolio returns is:} \\
    \sigma_{p,x}^2 & = var(R_{p,x})  \\
                   & = x_1 * \sigma_1^2 + x_2 * \sigma_2^2 + 2 * x_1 * x_2 * \sigma_{1,2}
  \end{aligned}
\end{equation}
  
The global minimum variance portfolio $m = (m_1,m_2)$ is the solution of the constrained minimization problem:

\begin{equation}
  \begin{aligned}
    min \sigma_{p,m}^2 & = var(R_{p,m})  \\
                       & = m_1^2 * \sigma_1^2 + m_2^2 * \sigma_2^2 + 2 * m_1 * m_2 * \sigma_{1,2} \\
    \text {s.t. } m_1 + m_2 & = 1 \\
    \text {rewrite: } \\
    min \sigma_{p,m}^2 & = min[m_1^2 * \sigma_1^2 + (1-m_1)^2 * \sigma_2^2 + 2 * m_1 * (1 - m_1) * \sigma_{1,2}] \\
                       & = min[m_1^2 * (\sigma_1^2 + \sigma_2^2 - 2 * \sigma_{1,2}) + m_1 * (2 * \sigma_{1,2} - 2 * \sigma_2^2) + \sigma_2^2]  \\
    \text {plug in: }
    min \sigma_{p,m}^2 & = min[(`r var_rStock1` + `r var_rStock2` - 2 * `r cov_rStock1_rStock2`) * m_1^2 + (2*`r cov_rStock1_rStock2` - 2*`r var_rStock2`) * m_1 + `r var_rStock2`] \\
    min \sigma_{p,m}^2 & = min[(`r var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2`) * m_1^2 + (`r 2*(cov_rStock1_rStock2 - var_rStock2)`) * m_1 + `r var_rStock2`] \\
  \end{aligned}
\end{equation}

Find the critical point:

\begin{equation}
  \begin{aligned}
    \frac{d\sigma_{p,m}^2}{dm} & = 0 \\
    \frac{d(`r var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2` * m_1^2 + (`r 2*(cov_rStock1_rStock2 - var_rStock2)`) * m_1 + `r var_rStock2`)}{dm} & = 0 \\
      .182* m_1 - .068 & = 0  \\
    m_1 & = .3736 = 37.36\%  \\
    \text {thus, }   \\
    m_2 & = 1 - 0.3736 = .6264 = 62.64\%
  \end{aligned}
\end{equation}

Graphing the function:  
```{r}
# The Variance function of the portfolio
fVar <- function(m1) var_rStock1 * m1^2 + var_rStock2 * (1 - m1)^2 + 2 * m1 * (1 - m1) * cov_rStock1_rStock2

# Set the weighting
m1 <- .3736
m2 <- .6264

# Plot of the variance function with respect to w1.
w1 <- seq(0, 1, .05)
plot(fVar, w1, xlab = "Weight of Stock 1 Relative to Portfolio", ylab = "Portfolio Variance", main = "Minimum Variance Portfolio"); abline(v = m1, col = "red")
points(m1, fVar(m1), col='green')

# Plot of the efficient frontier
w1 <- seq(-.5, 1.5, .005)
fVar <- function(w1) var_rStock1 * w1^2 + var_rStock2 * (1 - w1)^2 + 2 * w1 * (1 - w1) * cov_rStock1_rStock2
r <- function(w1) mean_rStock1*w1 + mean_rStock2*(1-w1)
Risk <- sqrt(fVar(w1))
Return <- r(w1)
plot(Risk, Return, type='l', main='Global Minimum Variance (no short sale)', col = 'green')
wp <- (var_rStock2 - cov_rStock1_rStock2) / (var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2)  # Normalizing weight
Rp <- r(wp)
sigma <- sqrt(fVar(wp))
Rf <- mean_rf
Sharpe <- (Rp-Rf)/sigma
X <- seq(0, 1, .01)
Y <- Rf + Sharpe*X
lines(X, Y)
points(sigma, Rp, col='orange')
```

We see indeed the minimum is at $m_1 = `r m1`$

Thus, the optimum weights of each stocks in the portfolio to satisfy the objective of minimum risk is:  

Asset      | Weight            | Risk            | Return            
---        | ---               | ---             | ---                                          
Stock 1    | `r m1*100`\%      |                 |
Stock 2    | `r m2*100`\%      |                 |
Portfolio  | 100\%             | `r sigma`       | `r Rp`

## **b. Construct the efficient frontier. Assume short sale.**
