---
title: "assignment06"
author: "Jeff Nguyen"
date: "09/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, envir=.GlobalEnv)
```

**University of Southern California**  
**Marshall School of Business**  
**FBE 506 Quantitative Method in Finance**

Assignment 06  
Student Name: Ngoc Son (Jeff) Nguyen  
Student ID: 6524885309  


# **Question 1**  

\begin{equation}
  \begin{aligned}
    Q = 150*N - .025*N^2
  \end{aligned}
\end{equation}

## a. Finding optimum N and Q. No constraint.  
Objective is to maximize Q given N. Thus we find the max of Q. 
Q(N) is a polynomial function, and thus, continuous everywhere.  

**Graph of the function:**
```{r}
Q <- function(N) 150*N - .025*N^2
curve(Q, 0, 6000)
root <- polyroot(c(150, -.05))
N_max <- Re(root)[abs(Im(root)) < 1e-6]
Q_max <- Q(N_max)
points(N_max, Q(N_max), col='red')
```
We know:  
\begin{equation}
  \begin{aligned}
    Q'(N_0) & = 0 \\
    \frac{dQ}{dN} & = 0 \\
    150 - .05*N_{max} & = 0 \\
    N_{max} & = `r N_max`
  \end{aligned}
\end{equation}

**Per graph, we can confirm Q(N) optimum is at $N_{max} = `r N_max`$ and $Q_{max} = `r Q_max`$.**  

## b,c,d. Finding optimum N and Q. Constraint $N \leqslant 250$.  

The problem is to maximize the output $Q$ subject to the constraint that the business can not have more than 250 units of labor $N$.  
To solve the constrained optimizing problem, we form the Lagrangian function.  

**The Lagrangian function is formed by augmenting the constraint together with the Lagrange multiplier to the objective function.** 

\begin{equation}
  \begin{aligned}
    L = 150*N - .025*N^2 + \lambda*(250 - N)
  \end{aligned}
\end{equation}

If the constraint is satisfied, no matter what value has, the second term in the right side of the Lagrangian equation will vanish and we arrive at $L = 150*N - .025*N^2$, that is maximizing $L$ with respect to $N$ is the same as maximizing $Q$, and achieving the objective. Therefore, the trick in solving a constrained optimizing problem is to incorporate the constraint into the problem and ensure that the constraint is satisfied with equality. This is done by treating $\lambda$ as an additional variable and assuming $L$ is a function of $N$ and $\lambda$. That is:

\begin{equation}
  \begin{aligned}
    L(N, \lambda) = 150*N - .025*N^2 + \lambda*(250 - N)
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $N$:
\begin{equation}
  \begin{aligned}
    L'(N_0) & = 0 \\
    \frac{dL}{dN} & = 0 \\
    150 - .05*N_0 - \lambda & = 0 \quad \text{(1)} \\
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $\lambda$:
\begin{equation}
  \begin{aligned}
    L'(\lambda) & = 0 \\
    \frac{dL}{d\lambda} & = 0 \\
    250 - N_0 & = 0 \\ 
    N_0 & = 250 \quad \text{(2)}
  \end{aligned}
\end{equation}

Substitute (2) to (1), we have $\lambda = 137.5 > 0$.   
The Lagrangian multiplier $\lambda$ is positive, implying the constraint is binding.  
```{r}
N_0 <- 250
Q_0 <- Q(N_0)
plot(Q, 0, 3500, xlab = 'N', ylab = 'Q')
abline(v = 250, col = 'red')
points(N_0, Q(N_0), col = 'green')
points(N_max, Q(N_max), col='red')
```

Therefore, the optimum solution to this problem is $N_0 = `r N_0`$ and $Q_0 = `r Q_0`$.  

# **Question 2**  

\begin{equation}
  \begin{aligned}
    Y = X^3 -11*X^2 + 14*X + 80
  \end{aligned}
\end{equation}

```{r}
f <- function(x) x^3 -11*x^2 + 14*x + 80
f_1prime <- function(x) 3*x^2 - 22*x + 14
root <- polyroot(c(14, -22, 3))
x_1prime <- Re(root)[abs(Im(root)) < 1e-6]
x_1prime
```

This is a polynomial function, thus, it is continuous everywhere.  
We know:  

\begin{equation}
  \begin{aligned}
    f'(x_0) & = 0 \\
    \frac{dy}{dx} & = 0 \\
    3*x^2 - 22*x + 14 & = 0 \\
    x_0 & = `r x_1prime`
  \end{aligned}
\end{equation}


```{r}
x_1prime1 <- 0.7039352
x_1prime2 <- 6.6293981
```
Testing min, max with $x_0 = `r x_1prime1`$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(`r x_1prime1 - 1`)                              \qquad  &   f'(x_0 + 1) & = f'(`r x_1prime1 + 1`) \\
    f'(x_0 - 1) & = 3*(`r x_1prime1 - 1`)^2 - 22*(`r x_1prime1 - 1`) + 14      &   f'(x_0 + 1) & = 3*(`r x_1prime1 + 1`)^2 - 22*(`r x_1prime1 + 1`) + 14 \\
    f'(x_0 - 1) & = `r f_1prime(x_1prime1 - 1)` > 0                            &   f'(x_0 + 1) & = `r f_1prime(x_1prime1 + 1)` < 0
  \end{aligned}
\end{equation}

Finding $f(`r x_1prime1`)$:
\begin{equation} 
  \begin{aligned}
    f(`r x_1prime1`) & = `r x_1prime1`^3 -11*`r x_1prime1`^2 + 14*`r x_1prime1` + 80 \\
    f(`r x_1prime1`) & = `r f(x_1prime1)`
  \end{aligned}
\end{equation}

**From the above, we know the function has a local maxima at $(`r x_1prime1`, `r f(x_1prime1)`)$**  

Testing min, max with $x_0 = `r x_1prime2`$
\begin{equation} 
  \begin{aligned}
    f'(x_0 - 1) & = f'(`r x_1prime2 - 1`)                              \qquad  &   f'(x_0 + 1) & = f'(`r x_1prime2 + 1`) \\
    f'(x_0 - 1) & = 3*(`r x_1prime2 - 1`)^2 - 22*(`r x_1prime2 - 1`) + 14      &   f'(x_0 + 1) & = 3*(`r x_1prime2 + 1`)^2 - 22*(`r x_1prime2 + 1`) + 14 \\
    f'(x_0 - 1) & = `r f_1prime(x_1prime2 - 1)` < 0                            &   f'(x_0 + 1) & = `r f_1prime(x_1prime2 + 1)` > 0
  \end{aligned}
\end{equation}

Finding $f(`r x_1prime2`)$:
\begin{equation} 
  \begin{aligned}
    f(`r x_1prime2`) & = `r x_1prime2`^3 -11*`r x_1prime2`^2 + 14*`r x_1prime2` + 80 \\
    f(`r x_1prime2`) & = `r f(x_1prime2)`
  \end{aligned}
\end{equation}

**From the above, we know the function has a local minima at $(`r x_1prime2`, `r f(x_1prime2)`)$**

Finding inflection point:
\begin{equation} 
  \begin{aligned}
    f''(x_0) & = 0 \\
    \frac{d^2 y}{dx^2} & = 0 \\
    6x - 22 & = 0 \\
    x & = \frac{11}{3} \approx 3.666667
  \end{aligned}
\end{equation}

```{r}
x_2prime1 <- 11/3
f_2prime <- function(x) 6*x - 22
```

Testing the potential inflection point at $x_0 = `r x_2prime1`$
\begin{equation} 
  \begin{aligned}
    f''(x_0 - 1) & = f''(`r x_2prime1 - 1`)   \qquad      &   f''(x_0 + 1) & = f''(`r x_2prime1 + 1`) \\
    f''(x_0 - 1) & = 6*`r x_2prime1 - 1` - 22             &   f''(x_0 + 1) & = 6*`r x_2prime1 + 1` - 22 \\
    f''(x_0 - 1) & = `r f_2prime(x_2prime1 - 1)` < 0      &   f''(x_0 + 1) & = `r f_2prime(x_2prime1 + 1)` > 0
  \end{aligned}
\end{equation}

Finding $f(`r x_2prime1`)$:
\begin{equation} 
  \begin{aligned}
    f(`r x_2prime1`) & = `r x_2prime1`^3 -11*`r x_2prime1`^2 + 14*`r x_2prime1` + 80 \\
    f(`r x_2prime1`) & = `r f(x_2prime1)`
  \end{aligned}
\end{equation}

**From the test, we see that the function curvature changes from concave to convex at $(`r x_2prime1`,`r f(x_2prime1) `)$, 
thus $(`r x_2prime1`,`r f(x_2prime1) `)$ is an inflection point.**

```{r}
x_1prime1 <- 0.7039352
x_1prime2 <- 6.6293981
x_2prime1 <- 11/3
curve(f, -5, 10)
points(x_1prime1, f(x_1prime1), col = 'red')
points(x_1prime2, f(x_1prime2), col = 'green')
points(x_2prime1, f(x_2prime1), col = 'blue')
```

# **Question 3**  

\begin{equation}
  \begin{aligned}
    Q = 100*N + 10*N^2 - N^3
  \end{aligned}
\end{equation}


**Graph of the function:**
```{r}
Q <- function(N) 100*N + 10*N^2 - N^3
curve(Q, 0, 20)
root <- polyroot(c(100, 20, -3)) 
N_max <- Re(root)[abs(Im(root)) < 1e-6]
N_max <- N_max[which(N_max>0)]
Q_max <- Q(N_max)
points(N_max, Q(N_max), col='red')
```  

Considering the solution with no constraint:

We know:  
\begin{equation}
  \begin{aligned}
    Q'(N_max) & = 0 \\
    \frac{dQ}{dN} & = 0 \\
    100 + 20 * N_{max} - 3*N^2 & = 0 \\
    N_{max} & = `r N_max`
  \end{aligned}
\end{equation}

**Per graph, we can confirm Q(N) optimum is at $N_{max} = `r N_max`$ and $Q_{max} = `r Q(N_max)`$.**  

## a,b. Finding optimum N and Q. Constraint $N \leqslant 15$.  

The problem is to maximize the output $Q$ subject to the constraint that the business can not have more than 15 units of labor $N$.  
To solve the constrained optimizing problem, we form the Lagrangian function.  

**The Lagrangian function is formed by augmenting the constraint together with the Lagrange multiplier to the objective function.** 

\begin{equation}
  \begin{aligned}
    L = 100*N + 10*N^2 - N^3 + \lambda*(15 - N)
  \end{aligned}
\end{equation}

If the constraint is satisfied, no matter what value has, the second term in the right side of the Lagrangian equation will vanish and we arrive at $L = 100*N + 10*N^2 - N^3$, that is maximizing $L$ with respect to $N$ is the same as maximizing $Q$, and achieving the objective. Therefore, the trick in solving a constrained optimizing problem is to incorporate the constraint into the problem and ensure that the constraint is satisfied with equality. This is done by treating $\lambda$ as an additional variable and assuming $L$ is a function of $N$ and $\lambda$. That is:

\begin{equation}
  \begin{aligned}
    L(N, \lambda) = 100*N + 10*N^2 - N^3 + \lambda*(15 - N)
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $N$:
\begin{equation}
  \begin{aligned}
    L'(N_0) & = 0 \\
    \frac{dL}{dN} & = 0 \\
    100- \lambda + 20*N - 3*N^2 & = 0 \quad \text{(1)} \\
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $\lambda$:
\begin{equation}
  \begin{aligned}
    L'(\lambda) & = 0 \\
    \frac{dL}{d\lambda} & = 0 \\
    15 - N_0 & = 0 \\ 
    N_0 & = 15 \quad \text{(2)}
  \end{aligned}
\end{equation}

Substitute (2) to (1), we have $\lambda = -275 < 0$.   
The Lagrangian multiplier $\lambda$ is negative, implying the constraint is non-binding.  
**Therefore, the constraint does not affect the optimum solution, which is still $N_{max} = `r N_max`$ and $Q_{max} = `r Q(N_max)`$.**
```{r}
N_0 <- 15
lambda <- 100 + 20*N_0 - 3*N_0^2 
Q_0 <- Q(N_0)
plot(Q, 0, 20, xlab = 'N', ylab = 'Q')
abline(v = N_0, col = 'green')
points(N_0, Q(N_0), col = 'green')
points(N_max, Q(N_max), col='red')
```  

## c,d. Finding optimum N and Q. Constraint $N \leqslant 8$.  

The problem is to maximize the output $Q$ subject to the constraint that the business can not have more than 8 units of labor $N$.  
To solve the constrained optimizing problem, we form the Lagrangian function.  

**The Lagrangian function is formed by augmenting the constraint together with the Lagrange multiplier to the objective function.** 

\begin{equation}
  \begin{aligned}
    L = 100*N + 10*N^2 - N^3 + \lambda*(8 - N)
  \end{aligned}
\end{equation}

If the constraint is satisfied, no matter what value has, the second term in the right side of the Lagrangian equation will vanish and we arrive at $L = 100*N + 10*N^2 - N^3$, that is maximizing $L$ with respect to $N$ is the same as maximizing $Q$, and achieving the objective. Therefore, the trick in solving a constrained optimizing problem is to incorporate the constraint into the problem and ensure that the constraint is satisfied with equality. This is done by treating $\lambda$ as an additional variable and assuming $L$ is a function of $N$ and $\lambda$. That is:

\begin{equation}
  \begin{aligned}
    L(N, \lambda) = 100*N + 10*N^2 - N^3 + \lambda*(8 - N)
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $N$:
\begin{equation}
  \begin{aligned}
    L'(N_0) & = 0 \\
    \frac{dL}{dN} & = 0 \\
    100- \lambda + 20*N - 3*N^2 & = 0 \quad \text{(1)} \\
  \end{aligned}
\end{equation}

Differentiating $L$ with respect to $\lambda$:
\begin{equation}
  \begin{aligned}
    L'(\lambda) & = 0 \\
    \frac{dL}{d\lambda} & = 0 \\
    8 - N_0 & = 0 \\ 
    N_0 & = 8 \quad \text{(2)}
  \end{aligned}
\end{equation}

Substitute (2) to (1), we have $\lambda = 68 > 0$.   
The Lagrangian multiplier $\lambda$ is positive, implying the constraint is binding.  
```{r}
N_0 <- 8
lambda <- 100 + 20*N_0 - 3*N_0^2 
Q_0 <- Q(N_0)
plot(Q, 0, 20, xlab = 'N', ylab = 'Q')
abline(v = N_0, col = 'green')
points(N_0, Q(N_0), col = 'green')
points(N_max, Q(N_max), col='red')
```

**Therefore, the constraint does affect the optimum solution, which is now $N_0 = `r N_0`$ and $Q_0 = `r Q(N_0)`$.**  

# **Question 4**  

## a. Find the GMV solution, no short sale.

Given parameters  

```{r}
# Mean Returns
mean_rStock1 <- .13
mean_rStock2 <- .21
mean_rf <- .08

# Variance of returns
var_rStock1 <- .075
var_rStock2 <- .052

# Standard deviation of returns
sd_rStock1 <- sqrt(var_rStock1)
sd_rStock2 <- sqrt(var_rStock2)

# Covariance of Returns
cov_rStock1_rStock2 <- .018

# Correlation of Returns
cor_rStock2_rStock2 <- cov_rStock1_rStock2 / (sd_rStock1 * sd_rStock2)
```


Asset      | Mean Returns      | Variance           | Pair    | $\sigma_{1,2}$
---        | ---               | ---                | ---     | ---                      
Stock 1    | `r mean_rStock1`  | `r var_rStock1`    | (1,2)   | `r cov_rStock1_rStock2` 
Stock 2    | `r mean_rStock2`  | `r var_rStock2`    |         | 
Risk Free  | `r mean_rf`       |                    |         | 
  
  
Since the investor's objective is to minimize risk, we solve for the global minimum variance combination of the two assets.
Let $x_i$ denotes the weight of the investment in asset i $(i = 1,2)$, and assume all money is invested in i, meaning $\sum {x_i} = x_1 + x_2 = 1$.

\begin{equation}
  \begin{aligned}
    \text {The returns of the portfolio is:} \\
    R_{p,x} & = x_1 * r_1 + x_2 * r_2 \\
    \text {The expected returns on the portfolio is:} \\
    \mu_{p,x} & = E[R_{p,x}] \\
              & = x_1 * \mu_1 + x_2 * \mu_2  \\
    \text {The variance of the portfolio returns is:} \\
    \sigma_{p,x}^2 & = var(R_{p,x})  \\
                   & = x_1 * \sigma_1^2 + x_2 * \sigma_2^2 + 2 * x_1 * x_2 * \sigma_{1,2}
  \end{aligned}
\end{equation}
  
The global minimum variance portfolio $m = (m_1,m_2)$ is the solution of the constrained minimization problem:

\begin{equation}
  \begin{aligned}
    min \sigma_{p,m}^2 & = var(R_{p,m})  \\
                       & = m_1^2 * \sigma_1^2 + m_2^2 * \sigma_2^2 + 2 * m_1 * m_2 * \sigma_{1,2} \\
    \text {s.t. } m_1 + m_2 & = 1 \\
    \text {rewrite: } \\
    min \sigma_{p,m}^2 & = min[m_1^2 * \sigma_1^2 + (1-m_1)^2 * \sigma_2^2 + 2 * m_1 * (1 - m_1) * \sigma_{1,2}] \\
                       & = min[m_1^2 * (\sigma_1^2 + \sigma_2^2 - 2 * \sigma_{1,2}) + m_1 * (2 * \sigma_{1,2} - 2 * \sigma_2^2) + \sigma_2^2]  \\
    \text {plug in: }
    min \sigma_{p,m}^2 & = min[(`r var_rStock1` + `r var_rStock2` - 2 * `r cov_rStock1_rStock2`) * m_1^2 + (2*`r cov_rStock1_rStock2` - 2*`r var_rStock2`) * m_1 + `r var_rStock2`] \\
    min \sigma_{p,m}^2 & = min[(`r var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2`) * m_1^2 + (`r 2*(cov_rStock1_rStock2 - var_rStock2)`) * m_1 + `r var_rStock2`] \\
  \end{aligned}
\end{equation}

Find the critical point:

\begin{equation}
  \begin{aligned}
    \frac{d\sigma_{p,m}^2}{dm} & = 0 \\
    \frac{d(`r var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2` * m_1^2 + (`r 2*(cov_rStock1_rStock2 - var_rStock2)`) * m_1 + `r var_rStock2`)}{dm} & = 0 \\
      .182* m_1 - .068 & = 0  \\
    m_1 & = .3736 = 37.36\%  \\
    \text {thus, }   \\
    m_2 & = 1 - 0.3736 = .6264 = 62.64\%
  \end{aligned}
\end{equation}

**Recap:**  

Asset      | Weight            
---        | ---                                  
Stock 1    | `37.36`\% 
Stock 2    | `62.64`\%

Graphing the function:  
```{r}
# The Variance function of the portfolio
fVar <- function(m1) var_rStock1 * m1^2 + var_rStock2 * (1 - m1)^2 + 2 * m1 * (1 - m1) * cov_rStock1_rStock2

# Set the weighting
m1 <- .3736
m2 <- .6264

# Plot of the variance function with respect to w1.
w1 <- seq(0, 1, .05)
plot(fVar, w1, xlab = "Weight of Stock 1 Relative to Portfolio", ylab = "Portfolio Variance", main = "Minimum Variance Portfolio"); abline(v = m1, col = "red")
points(m1, fVar(m1), col='green')

# Plot of the efficient frontier, assume no short sale allowed
w1WithoutShort <- seq(0, 1, .005)
fVar <- function(w1) var_rStock1 * w1^2 + var_rStock2 * (1 - w1)^2 + 2 * w1 * (1 - w1) * cov_rStock1_rStock2
r <- function(w1) mean_rStock1*w1 + mean_rStock2*(1-w1)
riskWithoutShort <- sqrt(fVar(w1WithoutShort))
returnWithoutShort <- r(w1WithoutShort)
plot(riskWithoutShort, returnWithoutShort, type='l', main='Global Minimum Variance (without short sale)', xlab = 'Risk', ylab = 'Return', col = 'green')
wp <- (var_rStock2 - cov_rStock1_rStock2) / (var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2)  # Normalizing weight
Rp <- r(wp)
sigma <- sqrt(fVar(wp))
Rf <- mean_rf
Sharpe <- (Rp-Rf)/sigma
X <- seq(0, 1, .01)
Y <- Rf + Sharpe*X
lines(X, Y)
points(sigma, Rp, col='orange')
```

We see indeed the minimum is at $m_1 = `r m1`$

Thus, the optimum weights of each stocks in the portfolio to satisfy the objective of minimum risk is:  

Asset      | Weight            | Risk            | Return            
---        | ---               | ---             | ---                                          
Stock 1    | `r m1*100`\%      |                 |
Stock 2    | `r m2*100`\%      |                 |
Portfolio  | 100\%             | `r sigma`       | `r Rp`

## **b. Construct the efficient frontier. Assume short sale.**  

```{r}
# Plot of the efficient frontier, assume short sale allowed
w1WithShort <- seq(-2, 2, .1)
riskWithShort <- sqrt(fVar(w1WithShort))
returnWithShort <- r(w1WithShort)
plot(riskWithShort, returnWithShort, type='l', main='Global Minimum Variance (with short sale)', xlab = 'Risk', ylab = 'Return', col = 'red')
wp <- (var_rStock2 - cov_rStock1_rStock2) / (var_rStock1 + var_rStock2 - 2 * cov_rStock1_rStock2)  # Normalizing weight
Rp <- r(wp)
sigma <- sqrt(fVar(wp))
Rf <- mean_rf
Sharpe <- (Rp-Rf)/sigma
X <- seq(0, 1, .01)
Y <- Rf + Sharpe*X
lines(X, Y)
points(sigma, Rp, col='orange')
```

## c. **Graph the efficient frontier of portfolio with and without short sale together.**

```{r}
# Changed input to display less points
w1WithoutShort <- seq(0, 1, .1)
riskWithoutShort <- sqrt(fVar(w1WithoutShort))
returnWithoutShort <- r(w1WithoutShort)
w1WithShort <- seq(-2, 2, .1)
riskWithShort <- sqrt(fVar(w1WithShort))
returnWithShort <- r(w1WithShort)


plot(riskWithShort, returnWithShort, main='Global Minimum Variance', xlab = 'Risk', ylab = 'Return', col = 'red', pch = 17)
points(riskWithoutShort, returnWithoutShort, col = 'green', pch = 17)
```

## d. **Find the GMV solution with additional constraint that $R_p > r_f$**  

Not dissimilar to 4a, the investor's objective is to minimize risk with a constrained on expected returns $R_p > r_f$, we solve for the global minimum variance combination of the two assets.  

Let $w_i$ denotes the weight of the investment in asset i $(i = 1,2)$, and assume all money is invested in i, meaning $\sum {w_i} = w_1 + w_2 = 1$.

Formulating the Markowitz portfolio problem:  

\begin{equation}
  \begin{aligned}
     \text {The investor's objective is:} \\
     max \mu_p & = w' * \mu \quad \text{s.t.} \\
     \sigma_p^2 & = w' * (\sum) * w \quad \text{and} \quad w'*I = 1  \\
     \text {where:} \\
     w & = \quad \text{matrix of asset weights in the portfolio} \\
       & = 
        \begin{pmatrix}
          w_1 \\
          w_2 \\
        \end{pmatrix} \\
     w' & = \quad \text{transpose matrix of asset weights in the portfolio} \\
       & = 
        \begin{pmatrix}
          w_1 & w_2 \\
        \end{pmatrix} \\
     \mu & = \quad \text{matrix of mean returns of asset in the portfolio} \\
         & = 
          \begin{pmatrix}
            \mu_1 \\
            \mu_2 \\
          \end{pmatrix} \\
     \sum & = \quad \text{Variance-covariance matrix of asset returns in the the portfolio} \\
          & = 
            \begin{pmatrix}
            \sigma_1     & \sigma_{1,2} \\
            \sigma_{1,2}  & \sigma_2  \\
          \end{pmatrix} \\
      w'*I & = \sum_{i=1}^{n} w_n \quad \text{or the sum weights of the asset in the portfolio, I is notation for identity matrix} \\
  \end{aligned}
\end{equation}

Let $\mu_{p,0}$ denotes a target expected return level. Formulate the problem:  

\begin{equation}
  \begin{aligned}
     min \sigma_{p,w}^2 & = w' * (\sum) * w  \quad \text{s.t.} \\
     \mu_p & = w' * \mu = \mu_{p,0}, \quad \text{and} \quad w'*I = 1 \\
  \end{aligned}
\end{equation}

To solve this, form the Lagrangian function:

\begin{equation}
  \begin{aligned}
    L(w, \lambda_1, \lambda_2) & = w'*\sum*w + \lambda_1*(w'*\mu - \mu_{p,0}) + \lambda_2*({w'*I - 1}) \\
  \end{aligned}
\end{equation}
  
Because there are two constraints ($w'*\mu = \mu_{p,0}$ and $w'1 = 1$) there are two Langrange multipliers $\lambda_1$ and $\lambda_2$. The first order condition for a minimum are the linear equations:  

\begin{equation}
  \begin{aligned}
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial w} & = \frac{\partial (\sum * w^2)}{\partial w} + \frac{\partial (\lambda_1*(w'*\mu - \mu_{p,0}))}{\partial w} + \frac{\lambda_2*({w'*I - 1})}{\partial w} = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_1} & = 0 \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_2} & = 0 \\
  \end{aligned}
\end{equation}

Simplify, we have:  

\begin{equation}
  \begin{aligned}
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial w} & = 2*\sum*w + \lambda_1*\mu + \lambda_2*I = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_1} & =  w'*\mu - \mu_{p,0} = 0  \\
    \frac{\partial L(w, \lambda_1, \lambda_2)}{\partial \lambda_2} & =  w'*I - 1 = 0  \\
  \end{aligned}
\end{equation}

Rewrite in matrix form:  

\begin{equation}
  \begin{aligned}
    \begin{pmatrix}
            2*\sum    & \mu   & I  \\
            \mu'      & 0     & 0  \\
            I'        & 0     & 0  \\
    \end{pmatrix}
    *
    \begin{pmatrix}
            w   \\
            \lambda_1     \\
            \lambda_2       \\
    \end{pmatrix}
    & =
    \begin{pmatrix}
            0   \\
            \mu_{p,0}     \\
            I       \\
    \end{pmatrix}
  \end{aligned}
\end{equation}

or  

\begin{equation}
  \begin{aligned}
    A * z_w & = b_0 \\
    \text{where}\\
    A & = 
    \begin{pmatrix}
            2*\sum    & \mu   & I  \\
            \mu'      & 0     & 0  \\
            I'        & 0     & 0  \\
    \end{pmatrix} \\
    z_w & = 
    \begin{pmatrix}
            w   \\
            \lambda_1     \\
            \lambda_2       \\
    \end{pmatrix} \\
    b_0 & =
    \begin{pmatrix}
            0   \\
            \mu_{p,0}     \\
            I       \\
    \end{pmatrix}
  \end{aligned}
\end{equation}

The solution for $z_w$ is:  

\begin{equation}
  \begin{aligned}
    z_w & = A^{-1} * b_0
  \end{aligned}
\end{equation}

In this case, we have:  

\begin{equation}
  \begin{aligned}
    \text{Hurdle rate:} \quad \mu_{p,0} & = r_f = `r mean_rf` \\
    \text{Returns column vector:} \quad R & = 
      \begin{pmatrix}
            `r mean_rStock1`   \\
            `r mean_rStock2`   \\
      \end{pmatrix} \\
    \text{Variance-Covariance Matrix:} \quad \sum & = 
      \begin{pmatrix}
            `r var_rStock1`           &   `r cov_rStock1_rStock2` \\
            `r cov_rStock1_rStock2`   &   `r var_rStock2` \\
      \end{pmatrix} \\
  \end{aligned}
\end{equation}

```{r}
sigmaMatrix <- matrix(rbind(c(var_rStock1, cov_rStock1_rStock2),c(cov_rStock1_rStock2, var_rStock1)), 2)  # Establish variance, covariance matrix
returnsVector <- rbind(mean_rStock1, mean_rStock2)  # Establish returns vector
```

Find the inverse of the variance-covariance matrix by conducting reduce row echelon form:  

\begin{equation}
  \begin{aligned}
    \text{Inverted Variance-Covariance Matrix:} \quad (\sum)^{-1} & = \\
      \left(\begin{array}{cc|cc} 
        `r var_rStock1`           &   `r cov_rStock1_rStock2` & 1 & 0  \\
        `r cov_rStock1_rStock2`   &   `r var_rStock2`         & 0 & 1
      \end{array}\right)
      \begin{matrix} ~ \\ \xrightarrow{R_2 + (-\frac{.018}{.075})*R_1}  \end{matrix}
      \left(\begin{array}{cc|cc} 
        .075  & .018 & 1 & 0  \\
        0 & .07068  & -.24 & 1
      \end{array}\right)
      \begin{matrix} ~ \\ \xrightarrow{(\frac{1}{.075}))*R_1} \\ \xrightarrow{(\frac{1}{.07068})*R_2}  \end{matrix} \\
      \left(\begin{array}{cc|cc} 
        1  & .24 & 13.33333 & 0  \\
        0 & 1  & -3.395586 & 14.148274
      \end{array}\right)
      \begin{matrix} ~ \\ \xrightarrow{R_1 + (-.24)*R_2}  \end{matrix}
      \left(\begin{array}{cc|cc} 
        1  & 0 & 14.148274 & -3.395586  \\
        0 & 1  & -3.395586 & 14.148274
      \end{array}\right)
  \end{aligned}
\end{equation}

```{r}
inverse_sigmaMatrix <- solve(sigmaMatrix)
riskPremiumMatrix <- returnsVector - mean_rf
```
We have the z vector:  

\begin{equation}
  \begin{aligned}
    z & = (\sum)^{-1} * (R - Rf) \\
      & = 
      \begin{pmatrix}
            14.148274 & -3.395589   \\
            -3.395586 & 14.148274   
      \end{pmatrix}
    *
      \begin{pmatrix}
            .13 - .08    \\
            .21 - .08 
      \end{pmatrix}
      & = 
      \begin{pmatrix}
            `r (14.148274 * .05 + -3.395589 * .13)`    \\
            `r (-3.395586 * .05 + 14.148274 * .13)`
      \end{pmatrix}
  \end{aligned}
\end{equation}

```{r}
z <- inverse_sigmaMatrix %*% riskPremiumMatrix
```
The lambda value is thus:  

\begin{equation}
  \begin{aligned}
    \lambda & = `r sum(z)`\\
  \end{aligned}
\end{equation}

```{r}
lambda <- sum(z)
w1 <- z[1] / lambda
w2 <- z[2] / lambda
```
Therefore, the weight of these stocks are:

\begin{equation}
  \begin{aligned}
    w_1 & = \frac{z_i}{\sum_{i=1}^{n} z_i} \\
        & = \frac{`r z[1]`}{`r lambda`} \\
        & = `r w1` \\
    \text{and} \\
    w_2 & = \frac{z_i}{\sum_{i=1}^{n} z_i} \\
        & = \frac{`r z[2]`}{`r lambda`} \\
        & = `r w2` \\
  \end{aligned}
\end{equation}

**Recap:**  

Asset      | Weight            
---        | ---                                  
Stock 1    | `r w1*100`\% 
Stock 2    | `r w2*100`\%

## e. **Graph the efficient frontier, CAL, and find the tangency point for portfolio in d.**  

```{r}
w1 <- 0.1374269
Rp <- r(w1)
sigma <- sqrt(fVar(w1))
CAL_slope <-(Rp - mean_rf) / sigma
CAL <- function(x) {mean_rf + CAL_slope * x}
```

The portfolio returns is:  

\begin{equation}
  \begin{aligned}
    R_p & = w_1 * R_1 + w_2 * R_2 \\
        & = `r Rp` \\
  \end{aligned}
\end{equation}

The portfolio returns variance is:  

\begin{equation}
  \begin{aligned}
    \sigma_p & = w_1 * \sigma_1 + w_2 * \sigma_2 + 2 * w_1 * w_2 * \sigma_{1,2} \\
             & = `r sigma` \\
  \end{aligned}
\end{equation}

The slope of the Capital Allocation Line is:  

\begin{equation}
  \begin{aligned}
    Slope_{CAL} & = \frac{R_p - r_f}{\sqrt{\sigma_p}} \\
              & = `r CAL_slope` \\
  \end{aligned}
\end{equation}

**Thus the Capital Allocation Line equation is $CAL = r_f + Slope_{CAL} * x = `r mean_rf` + `r CAL_slope` * x$.**  

**The tangency point is where the optimum weight is, i.e. $(\sigma_p, Rp)$ or $(`r sigma`, `r Rp`)$**


Graphing 
```{r}
# Plot of the efficient frontier, assume no short sale allowed
plot(riskWithShort, returnWithShort, main='Global Minimum Variance', xlab = 'Risk', ylab = 'Return', col = 'red', pch = 17)
points(riskWithoutShort, returnWithoutShort, col = 'green', pch = 17)
plot.function(CAL, add= TRUE, col = 'blue', lwd = 4)
points(sigma, Rp, col='orange', lwd = 4)
```

## f. **What will be the expected return to portfolio if the investor is willing to take 25% risk?**  

At 25% risk, the expected return is:  

\begin{equation}
  \begin{aligned}
    E(R_p) & = r_f + Slope_{CAL} * x \\
           & = `r mean_rf` + `r CAL_slope` * .25 \\
           & = `r mean_rf + CAL_slope * .25` \\
           & = `r (mean_rf + CAL_slope * .25) * 100` \%
  \end{aligned}
\end{equation}
